### 2012-08-16 paper/paper.tex
added file for paper

%% Example of a LaTeX source file for a COLING-2012 submission
%% last updated: July 10, 2012
%% Optional instructions for authors within the tex file are provided as comments and start with 'for authors:...'
\documentclass[10pt,a5paper,twoside]{article}
\usepackage{coling2012}
\title{Translating to Shakespeare: A Case Study in Paraphrasing Writing Styles}
%for authors: in case of more than four author names ref. to commented line below 
%\author{$Annie~SMITH^{1, 2}~~~LI~Xiao Dong^{1, 3}$\\$~~~Third~Author^{1, 2}~~~Fourth~Author^{1, 3}~~~ Fifth~Author^{2, 3}$\\
\author{$Author1^{1, 2}~~~Author2^{1, 3}$\\
{\small  	(1) INSTITUTE\_1, address 1\\ 
 		(2) INSTITUTE\_2, address 2\\
		(3) INSTITUTE\_3, address 3\\
  \texttt{author1@institute1, author@institute2} \\ 
}}

\begin{document}
\maketitle
%% The first mandatory ABSTRACT (\abstractEn) section below is for the English language
\abstractEn{  %ABSTRACT}{
We present innitial investigation into the task of paraphrasing writing style.
The plays of William Shakespeare and their \emph{modern} translations are treated
as parallel text which is used to learn paraphrase models targeting the style of Early Modern English employed by Shakespeare.
We demonstrate that existing evaluation metrics developed in the Machine Translation and Paraphrase communities are
innappropriate when generating paraphrases targeting a specific writing style, and
propose a new metric to measure how closely the generated paraphrases match the target
style.  To the best of our knowledge no previous work has investigated the task of
paraphrasing text with the goal of targeting a specific style of writing.
}

\keywordsEn{Paraphrase, Writing Style}

% section 2
\section{Introduction}
% subsection 2.1

\section{Data}

\section{Evaluation Metrics}

\section{Experiments}

\section{Conclusions}

\bibliographystyle{apa}

\bibliography{colingbiblio}
\nocite{TALN2007,LaigneletRioult09,LanglaisPatry07,au1972,cks1981,mb2012}

%%================================================================
\end{document}

### 2012-08-18 paper/paper.tex
added stuff for evaluating style metric

@@
 \usepackage{coling2012}
-\title{Translating to Shakespeare: A Case Study in Paraphrasing Writing Styles}
+%\title{Translating to Shakespeare: A Case Study in Paraphrasing Writing Styles}
+\title{You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles}
 %for authors: in case of more than four author names ref. to commented line below 
@@
 \abstractEn{  %ABSTRACT}{
-We present innitial investigation into the task of paraphrasing writing style.
-The plays of William Shakespeare and their \emph{modern} translations are treated
-as parallel text which is used to learn paraphrase models targeting the style of Early Modern English employed by Shakespeare.
+We present innitial investigation into the task of paraphrasing while targeting a particular writing style.
+The plays of William Shakespeare and their \emph{modern translations} are used as a testbed for evaluating
+paraphrase systems targeting a specific style of writing.
 We demonstrate that existing evaluation metrics developed in the Machine Translation and Paraphrase communities are
-innappropriate when generating paraphrases targeting a specific writing style, and
-propose a new metric to measure how closely the generated paraphrases match the target
+insufficient when the goal is to generate paraphrases targeting a specific style, and
+propose a series of new metrics to measure how closely the generated paraphrases match the target
 style.  To the best of our knowledge no previous work has investigated the task of
@@
 
-% section 2
 \section{Introduction}
-% subsection 2.1
+%The plays of William Shakespeare and their \emph{modern} translations are treated
+%as parallel text which is used to learn paraphrase models targeting the style of Early Modern English employed by Shakespeare.
+
+\begin{itemize}
+  \item Define what we mean by writing styles.
+  \item Define the paraphrasing task and describe previous work.
+  \item Motivate the need for paraphrasing targeting a specific writing style (e.g. students of literature in a specific style, or helping people to understand documents written in an esoteric style).
+   \begin{itemize}
+     \item Mention several domains where paraphrasing into/out of a specific writing style could be beneficial (e.g. technical manuals, legal documents, etc...)
+   \end{itemize}
+  \item Summarize the main contributions.
+\end{itemize}
 
 \section{Data}
+\begin{itemize}
+  \item Motivate the need for a benchmark dataset for evaluating the writing style paraphrase task
+  \item Present Shakespere / Modern translation data as a situation where we have parallel data available (useful for building models \& evaluating automatic evaluation metrics)
+\end{itemize}
 
 \section{Evaluation Metrics}
+\begin{itemize}
+  \item Describe the need for automatic evauation metrics.
+  \item Describe previously used evaluation metrics for paraphrase.
+  \item Highlight problems with previous metrics when targeting a specific writing style.
+  \item Propose new metrics.
+\end{itemize}
 
 \section{Experiments}
+\begin{itemize}
+  \item Experimental setup.
+  \item Present results from human evaluation comparing various systems.
+  \item Analyze correlation between evaluation metrics and human judgements.
+\end{itemize}
+
+\section{Related Work}
+\begin{itemize}
+  \item Kevin Knight's work on poetry generation
+  \item Any work on writing style (e.g. classification)?  Possibly cite work on author attribution...
+  \item work on paraphrase evaluation metrics (David Chen, CCB, etc...)
+\end{itemize}
 
@@
 \bibliography{colingbiblio}
-\nocite{TALN2007,LaigneletRioult09,LanglaisPatry07,au1972,cks1981,mb2012}
 

### 2012-08-18 python/add_scores.py

@@ -1,0 +1,75 @@
+#!/usr/bin/python
+
+import sys
+
+from scipy.stats.stats import pearsonr
+
+from PINC_BLEU import *
+from style_metric import *
+
+_16plays36_bleu_list = []
+_16plays36_pinc_list = []
+_16plays36_csim_list = []
+_16plays36_cmaxent_list = []
+phrase_bleu_list = []
+phrase_pinc_list = []
+phrase_csim_list = []
+phrase_cmaxent_list = []
+
+_16plays36_semantic_list = []
+_16plays36_dissim_list = []
+_16plays36_style_list = []
+phrase_semantic_list = []
+phrase_dissim_list = []
+phrase_style_list = []
+
+sm = StyleMetric('models/Translators/16plays_36LM/data/train_plays_lowercased.modern', 'models/Translators/16plays_36LM/data/train_plays_lowercased.original')
+
+i = 0
+for line in open(sys.argv[1]):
+    line = line.strip()
+    if len(line.split('\t')) < 12 or i == 0:
+        i += 1
+        continue
+    (original, modern, _16plays36, phrase, _16plays36_semantic, _16plays36_dissim, _16plays36_style, _16plays36_overall, phrase_semantic, phrase_dissim, phrase_style, phrase_overall) = line.split('\t')
+    _16plays36_semantic_list.append(float(_16plays36_semantic))
+    _16plays36_dissim_list.append(float(_16plays36_dissim))
+    _16plays36_style_list.append(float(_16plays36_style))
+    phrase_semantic_list.append(float(phrase_semantic))
+    phrase_dissim_list.append(float(phrase_dissim))
+    phrase_style_list.append(float(phrase_style))
+    
+    print "\t".join([str(x) for x in [line, simple_bleu(_16plays36, original), pinc(_16plays36, modern), sm.ScoreSim(_16plays36), sm.ScoreMaxEnt(_16plays36), simple_bleu(phrase, original), pinc(phrase, modern), sm.ScoreSim(phrase), sm.ScoreMaxEnt(phrase)]])
+    _16plays36_bleu_list.append(simple_bleu(_16plays36, original))
+    _16plays36_pinc_list.append(pinc(_16plays36, modern))
+    _16plays36_csim_list.append(sm.ScoreSim(_16plays36))
+    _16plays36_cmaxent_list.append(sm.ScoreMaxEnt(_16plays36))
[…]

### 2012-08-18 python/style_metric.py

@@ -1,0 +1,110 @@
+#!/usr/bin/python
+
+import nltk
+nltk.config_megam('/home/aritter/local/bin/megam')
+
+import sys
+import math
+import random
+
+MAX_NGRAM=6
+
+class StyleMetric:
+    source_vector = {}
+    target_vector = {}
+
+    training = []
+
+    def __init__(self, corpus_source, corpus_target):
+        #Read in Source Corpus
+        nlines = 0
+        for line in open(corpus_source):
+            #TODO: can use more data for training maxent model if more memory is available
+            line = line.strip()
+            words = nltk.word_tokenize(line)
+            sentenceDict = {}
+            for gram in range(1,MAX_NGRAM):
+                for i in range(len(words)-gram+1):
+                    ngram = " ".join(words[i:i+gram])
+                    self.source_vector[ngram] = 1
+                    #self.source_vector[ngram] = self.source_vector.get(ngram, 0) + 1
+                    sentenceDict[ngram] = 1
+                    #sentenceDict[ngram] = sentenceDict.get(ngram, 0) + 1.0
+            self.training.append((sentenceDict, 'source'))
+            nlines += 1
+
+        #Read in Target Corpus
+        nlines = 0
+        for line in open(corpus_target):
+            line = line.strip()
+            words = nltk.word_tokenize(line)
+            sentenceDict = {}
+            for gram in range(1,MAX_NGRAM):
+                for i in range(len(words)-gram+1):
+                    ngram = " ".join(words[i:i+gram])
+                    self.target_vector[ngram] = 1
+                    #self.target_vector[ngram] = self.target_vector.get(ngram, 0) + 1
+                    sentenceDict[ngram] = 1
+                    #sentenceDict[ngram] = sentenceDict.get(ngram, 0) + 1
+            self.training.append((sentenceDict, 'target'))
+            nlines += 1
+
+        #self.training = random.sample(self.training, 100)
+            
+#        for i in range(len(self.training)):
+#            t = {}
+#            for k in self.source_vector.keys() + self.target_vector.keys():
+#                #t[k] = self.training[i][0].get(k, 0.0)
+#                if self.training[i][0].has_key(k):
+#                    t[k] = 1
+#                else:
[…]

### 2012-08-19 eval/eval.sh
added mert moses

@@ -29,6 +29,11 @@ cat ascii.romeojuliet_tokenized_lower_modern.2 | ~/mt/mosesdecoder/moses-cmd/src
 cat ascii.romeojuliet_tokenized_lower_modern.1 | ~/mt/mosesdecoder/moses-cmd/src/moses -f ~/Shakespere/models/Lexicons/phrase2/alan_moses.ini > phrase2.1 2> /dev/null
 cat ascii.romeojuliet_tokenized_lower_modern.2 | ~/mt/mosesdecoder/moses-cmd/src/moses -f ~/Shakespere/models/Lexicons/phrase2/alan_moses.ini > phrase2.2 2> /dev/null
 
+#cat ascii.romeojuliet_tokenized_lower_modern.1 | ~/mt/mosesdecoder/moses-cmd/src/moses -f ~/Shakespere/models/Translators/video_corpus_baseline/model/moses.ini > video_corpus_baseline.1 2> /dev/null
+#cat ascii.romeojuliet_tokenized_lower_modern.2 | ~/mt/mosesdecoder/moses-cmd/src/moses -f ~/Shakespere/models/Translators/video_corpus_baseline/model/moses.ini > video_corpus_baseline.2 2> /dev/null
+cat ascii.romeojuliet_tokenized_lower_modern.1 | ~/mt/mosesdecoder/moses-cmd/src/moses -f ~/Shakespere/models/Translators/video_corpus_baseline/model/moses_mert.ini > video_corpus_baseline.1 2> /dev/null
+cat ascii.romeojuliet_tokenized_lower_modern.2 | ~/mt/mosesdecoder/moses-cmd/src/moses -f ~/Shakespere/models/Translators/video_corpus_baseline/model/moses_mert.ini > video_corpus_baseline.2 2> /dev/null
+
 echo singleword1.1
 ~/mt/mosesdecoder/scripts/generic/multi-bleu.perl ascii.romeojuliet_tokenized_lower_original < singleword1.1
 echo singleword1.2
@@ -48,3 +53,8 @@ echo phrase2.1
 ~/mt/mosesdecoder/scripts/generic/multi-bleu.perl ascii.romeojuliet_tokenized_lower_original < phrase2.1
 echo phrase2.2
 ~/mt/mosesdecoder/scripts/generic/multi-bleu.perl ascii.romeojuliet_tokenized_lower_original < phrase2.2
+
+echo video_corpus_baseline.1
[…]

### 2012-08-19 eval/eval.sh
added output from video corpus baseline

@@ -34,6 +34,12 @@ cat ascii.romeojuliet_tokenized_lower_modern.2 | ~/mt/mosesdecoder/moses-cmd/src
 cat ascii.romeojuliet_tokenized_lower_modern.1 | ~/mt/mosesdecoder/moses-cmd/src/moses -f ~/Shakespere/models/Translators/video_corpus_baseline/model/moses_mert.ini > video_corpus_baseline.1 2> /dev/null
 cat ascii.romeojuliet_tokenized_lower_modern.2 | ~/mt/mosesdecoder/moses-cmd/src/moses -f ~/Shakespere/models/Translators/video_corpus_baseline/model/moses_mert.ini > video_corpus_baseline.2 2> /dev/null
 
+cat ascii.romeojuliet_tokenized_lower_modern.1 | ~/mt/mosesdecoder/moses-cmd/src/moses -f ~/Shakespere/models/Translators/video_corpus_baseline/model/moses_modernLM.ini > video_corpus_baseline_modernLM.1 2> /dev/null
+cat ascii.romeojuliet_tokenized_lower_modern.2 | ~/mt/mosesdecoder/moses-cmd/src/moses -f ~/Shakespere/models/Translators/video_corpus_baseline/model/moses_modernLM.ini > video_corpus_baseline_modernLM.2 2> /dev/null
+
+cat ascii.romeojuliet_tokenized_lower_modern.1 | ~/mt/mosesdecoder/moses-cmd/src/moses -f ~/Shakespere/models/Translators/video_corpus_baseline/model/moses_modernLM_mert.ini > video_corpus_baseline_modernLM_mert.1 2> /dev/null
+cat ascii.romeojuliet_tokenized_lower_modern.2 | ~/mt/mosesdecoder/moses-cmd/src/moses -f ~/Shakespere/models/Translators/video_corpus_baseline/model/moses_modernLM_mert.ini > video_corpus_baseline_modernLM_mert.2 2> /dev/null
+
 echo singleword1.1
 ~/mt/mosesdecoder/scripts/generic/multi-bleu.perl ascii.romeojuliet_tokenized_lower_original < singleword1.1
 echo singleword1.2
@@ -58,3 +64,13 @@ echo video_corpus_baseline.1
 ~/mt/mosesdecoder/scripts/generic/multi-bleu.perl ascii.romeojuliet_tokenized_lower_original < video_corpus_baseline.1
 echo video_corpus_baseline.2
[…]

### 2012-08-19 python/add_scores.py
re-annotated data

@@ -15,6 +15,10 @@ phrase_bleu_list = []
 phrase_pinc_list = []
 phrase_csim_list = []
 phrase_cmaxent_list = []
+video_bleu_list = []
+video_pinc_list = []
+video_csim_list = []
+video_cmaxent_list = []
 
 _16plays36_semantic_list = []
 _16plays36_dissim_list = []
@@ -22,6 +26,9 @@ _16plays36_style_list = []
 phrase_semantic_list = []
 phrase_dissim_list = []
 phrase_style_list = []
+video_semantic_list = []
+video_dissim_list = []
+video_style_list = []
 
 sm = StyleMetric('models/Translators/16plays_36LM/data/train_plays_lowercased.modern', 'models/Translators/16plays_36LM/data/train_plays_lowercased.original')
 
@@ -31,23 +38,32 @@ for line in open(sys.argv[1]):
     if len(line.split('\t')) < 12 or i == 0:
         i += 1
         continue
-    (original, modern, _16plays36, phrase, _16plays36_semantic, _16plays36_dissim, _16plays36_style, _16plays36_overall, phrase_semantic, phrase_dissim, phrase_style, phrase_overall) = line.split('\t')
+    (original, modern, _16plays36, phrase, video, _16plays36_semantic, _16plays36_dissim, _16plays36_style, _16plays36_overall, phrase_semantic, phrase_dissim, phrase_style, phrase_overall, video_semantic, video_dissim, video_style, video_overall) = line.split('\t')
     _16plays36_semantic_list.append(float(_16plays36_semantic))
     _16plays36_dissim_list.append(float(_16plays36_dissim))
     _16plays36_style_list.append(float(_16plays36_style))
     phrase_semantic_list.append(float(phrase_semantic))
     phrase_dissim_list.append(float(phrase_dissim))
     phrase_style_list.append(float(phrase_style))
+    video_semantic_list.append(float(video_semantic))
+    video_dissim_list.append(float(video_dissim))
+    video_style_list.append(float(video_style))
     
[…]

### 2012-08-20 python_wei/crawl_sonnets.py
Added to nltk.classify.megam package, saving/reading maxent models into/from file

@@ -1,0 +1,29 @@
+import re
+import urllib
+import time
+
+url = 'http://nfs.sparknotes.com/sonnets/sonnet_1.html'
+for i in range(2,100000):
+    print url
+    urlobject = urllib.urlopen(url)
+    print urlobject.code
+    if urlobject.code == 404:
+        break
+    lines = urllib.urlopen(url).readlines()
+
+    fOut = open('sonnets/%s_%s' % (url.split('/')[-2], url.split('/')[-1]), 'w')
+    fOut.write("\n".join(lines))
+    fOut.close()
+    time.sleep(1)
+
+    #Get the next URL
+    url = None
+    for line in lines:
+        m = re.match(r'<div class="next"><a href="(.+)">Next Section', line)
+        if m:
+            url = m.group(1)
+            print url
+            break
+
+    if not url:
+        break

### 2012-08-20 python_wei/scrapper_soupparser.py

@@ -1,0 +1,38 @@
+import lxml.html.soupparser as soupparser
+import lxml.html
+import io
+import sys
+import re
+import nltk
+
+from django.utils.encoding import smart_str
+
+file = open(sys.argv[1])
+html = file.read()
+file.close()
+
+tree = soupparser.parse(io.BytesIO(html))
+
+original = ""
+modern = ""
+for t in tree.xpath('//*[name()="div"]'):    
+    if t.text is not None:
+        if 'class' in t.attrib :
+            if t.attrib['class'] == 'original-line' :
+                oline = t.text.replace('\n', ' ')
+                oline = smart_str(re.sub(r'\s+', ' ', oline))
+                original += " " + oline
+
+                
+            elif t.attrib['class'] == 'modern-line' :
+                mline = t.text.replace('\n', ' ')
+                mline = smart_str(re.sub(r'\s+', ' ', mline))
+                modern += " " + mline
+                
+oSentences = nltk.sent_tokenize(original)
+for s in oSentences:
+    print '[O]' + s
+
+mSentences = nltk.sent_tokenize(modern)
+for s in mSentences:
+    print '[M]' + s

### 2012-08-20 python_wei/style_metric.py

@@ -1,0 +1,116 @@
+#!/usr/bin/python
+
+import nltk
+#nltk.config_megam('/home/aritter/local/bin/megam')
+nltk.config_megam('/usr/local/bin/megam')
+
+import sys
+import math
+import random
+
+MAX_NGRAM=6
+
+class StyleMetric:
+    source_vector = {}
+    target_vector = {}
+
+    training = []
+
+    def __init__(self, corpus_source, corpus_target):
+        #Read in Source Corpus
+        nlines = 0
+        for line in open(corpus_source):
+            #TODO: can use more data for training maxent model if more memory is available
+            line = line.strip()
+            words = nltk.word_tokenize(line)
+            sentenceDict = {}
+            for gram in range(1,MAX_NGRAM):
+                for i in range(len(words)-gram+1):
+                    ngram = " ".join(words[i:i+gram])
+                    self.source_vector[ngram] = 1
+                    #self.source_vector[ngram] = self.source_vector.get(ngram, 0) + 1
+                    sentenceDict[ngram] = 1
+                    #sentenceDict[ngram] = sentenceDict.get(ngram, 0) + 1.0
+            self.training.append((sentenceDict, 'source'))
+            nlines += 1
+
+        #Read in Target Corpus
+        nlines = 0
+        for line in open(corpus_target):
+            line = line.strip()
+            words = nltk.word_tokenize(line)
+            sentenceDict = {}
+            for gram in range(1,MAX_NGRAM):
+                for i in range(len(words)-gram+1):
+                    ngram = " ".join(words[i:i+gram])
+                    self.target_vector[ngram] = 1
+                    #self.target_vector[ngram] = self.target_vector.get(ngram, 0) + 1
+                    sentenceDict[ngram] = 1
+                    #sentenceDict[ngram] = sentenceDict.get(ngram, 0) + 1
+            self.training.append((sentenceDict, 'target'))
+            nlines += 1
+
+        #self.training = random.sample(self.training, 100)
+            
+#        for i in range(len(self.training)):
+#            t = {}
+#            for k in self.source_vector.keys() + self.target_vector.keys():
+#                #t[k] = self.training[i][0].get(k, 0.0)
+#                if self.training[i][0].has_key(k):
+#                    t[k] = 1
[…]

### 2012-08-20 scripts/analyze_humanjudgements.pl

@@ -1,0 +1,70 @@
+my $humanfile = "../eval/annotated.tsv";
+
+open (MANFILE, $humanfile) || die "Can't open file $!.";
+my @humanlines = <MANFILE>;
+close(MANFILE);
+
+
+	
+my @scores = (4,3,2,1);
+foreach my $stylescore (@scores) {	
+	foreach my $humanline (@humanlines) {
+		chomp $humanline;
+		my @cols = split(/\t/, $humanline);
+		
+		my $original = $cols[0];
+		my $modern   = $cols[1];
+		my $moseout  = $cols[2];
+		my $dictout  = $cols[3];
+		my $mosesem  = $cols[4];
+		my $mosedis  = $cols[5];
+		my $mosesty  = $cols[6];
+		my $moseall  = $cols[7];
+		my $dictsem  = $cols[8];
+		my $dictdis  = $cols[9];
+		my $dictsty  = $cols[10];
+		my $dictall  = $cols[11];
+		
+		if ($mosesty == $stylescore) {
+			extratoken_analyse($original, $modern, $moseout, $stylescore);	
+		} 
+		
+		if ($dictsty == $stylescore) {
+			extratoken_analyse($original, $modern, $dictout, $stylescore);	
+		} 
+	}
+}
+
+sub extratoken_analyse {
+		my $o = shift;
+		my $m = shift;
+		my $s = shift;
+		my $score = shift;
+		print "[O]".$o."\n";
+		print "[M]".$m."\n";
+		print "[S]".$s."\n";
+		print "[".$score."] ";
+		extratoken ($m, $s);
+		print "\n\n";
+}
+
+sub extratoken {
+
+	my $sysinput  = shift;
+	my $sysoutput = shift;
+	my @sysintokens  = split(/\s/, $sysinput);
+	my @sysouttokens = split(/\s/, $sysoutput);
+	
+	foreach my $outtoken (@sysouttokens) {
+		my $hit = 0;
+		foreach my $intoken (@sysintokens) {
+			if ($outtoken eq $intoken) {
+				$hit = 1;
+			}
+		}
+		if ($hit == 0) {
+			print $outtoken." ";
+		}
+	}
+
+}

### 2012-08-22 python_wei/add_scores_wei.py
Wei's annotation and correlation

@@ -7,93 +7,209 @@ from scipy.stats.stats import pearsonr
 from PINC_BLEU import *
 from style_metric import *
 
-_16plays36_bleu_list = []
-_16plays36_pinc_list = []
-_16plays36_csim_list = []
-_16plays36_cmaxent_list = []
-phrase_bleu_list = []
-phrase_pinc_list = []
-phrase_csim_list = []
-phrase_cmaxent_list = []
-video_bleu_list = []
-video_pinc_list = []
-video_csim_list = []
-video_cmaxent_list = []
 
-_16plays36_semantic_list = []
-_16plays36_dissim_list = []
-_16plays36_style_list = []
-phrase_semantic_list = []
-phrase_dissim_list = []
-phrase_style_list = []
-video_semantic_list = []
-video_dissim_list = []
-video_style_list = []
+def corelation_human_human (filename1, filename2):
 
-sm = StyleMetric('../models/Translators/16plays_36LM/data/train_plays_lowercased.modern', '../models/Translators/16plays_36LM/data/train_plays_lowercased.original')
-
-i = 0
-for line in open(sys.argv[1]):
-    line = line.strip()
-    if len(line.split('\t')) < 12 or i == 0:
-        i += 1
-        continue
-    (original, modern, _16plays36, phrase, video, _16plays36_semantic, _16plays36_dissim, _16plays36_style, _16plays36_overall, phrase_semantic, phrase_dissim, phrase_style, phrase_overall, video_semantic, video_dissim, video_style, video_overall) = line.split('\t')
-    _16plays36_semantic_list.append(float(_16plays36_semantic))
-    _16plays36_dissim_list.append(float(_16plays36_dissim))
-    _16plays36_style_list.append(float(_16plays36_style))
-    phrase_semantic_list.append(float(phrase_semantic))
-    phrase_dissim_list.append(float(phrase_dissim))
-    phrase_style_list.append(float(phrase_style))
-    video_semantic_list.append(float(video_semantic))
-    video_dissim_list.append(float(video_dissim))
-    video_style_list.append(float(video_style))
+    _16plays36_semantic_list_1 = []
+    _16plays36_dissim_list_1 = []
+    _16plays36_style_list_1 = []
+    _16plays36_overall_list_1 = []
+    phrase_semantic_list_1 = []
+    phrase_dissim_list_1 = []
+    phrase_style_list_1 = []
+    phrase_overall_list_1 = []
[…]

### 2012-08-22 python_wei/style_metric.py

@@ -93,7 +93,7 @@ class StyleMetric:
                 #sentence_vector[ngram] = sentence_vector.get(ngram, 0) + 1
         return self.maxEntModel.prob_classify(sentence_vector).prob('target')
         
-    def ScoreDiffMaxEnt(self, sentence1, sentence2)
+    #def ScoreDiffMaxEnt(self, sentence1, sentence2)
 
 
     def CosineSim(self, v1, v2):

### 2012-08-23 paper/paper.tex
some writing progress

@@
 \usepackage{coling2012}
+\usepackage{comment}
 %\title{Translating to Shakespeare: A Case Study in Paraphrasing Writing Styles}
@@
 \abstractEn{  %ABSTRACT}{
-We present innitial investigation into the task of paraphrasing while targeting a particular writing style.
-The plays of William Shakespeare and their \emph{modern translations} are used as a testbed for evaluating
+We present initial investigation into the task of paraphrasing language while targeting a particular writing style.
+The plays of William Shakespeare and their modern translations are used as a testbed for evaluating
 paraphrase systems targeting a specific style of writing.
-We demonstrate that existing evaluation metrics developed in the Machine Translation and Paraphrase communities are
-insufficient when the goal is to generate paraphrases targeting a specific style, and
-propose a series of new metrics to measure how closely the generated paraphrases match the target
-style.  To the best of our knowledge no previous work has investigated the task of
+%We demonstrate that existing evaluation metrics developed in the Machine Translation and Paraphrase communities are
+%insufficient when the goal is to generate paraphrases targeting a specific style, and
+%propose a series of new metrics to measure how closely the generated paraphrases match the target
+%style.  
+We empirically show that even with a relatively small amount of parallel training data available, it is
+possible to learn paraphrase models which capture stylistic phenomenon, and these models outperform
+baselines based on dictionaries and out-of-domain parallel text.
+In addition we present an initial investigation into automatic evaluation metrics for paraphrasing writing style.
+To the best of our knowledge this is the first work to investigate the task of
 paraphrasing text with the goal of targeting a specific style of writing.
@@
 
+Identical meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
+fundamental to many natural language understanding tasks\cite{}, so much previous work has investigated methods for automatic paraphrasing.  Two different
+utterances may be semantically equivelant, however they can also be styalistically quite different.  For example, the same information information about a new product
+is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.
+
+In this paper, we investigate the task of automatic paraphrasing when targeting a specific writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
+We exploit modern translations of 17 plays written to help literature students to better understand Shakespeare.
+These modern translations are used to generate a parallel corpus of Shakespere's style and modern English,
+which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakesperean English.  In addition we develop several
+baseline systems which don't make use of this source of parallel text and instead rely on dictionaries of expressions commonly found in shakesperean english, or parallel monolingual text
+gathered through Amazon's Mechanical Turk \cite{}.
+
+We evaluate these models both through human judgements and standard evaluation metrics from the Machine Translation and paraphrase literature, however no previous work has investigated the ability of automatic metrics
+to capture the notion of writing style.  We propose several new metrics for evaluating the task of paraphrasing while targeting a specific style, and measure correlation with human judgement showing
+promising results for this particular style.
+
+Systems which are capable of automatically paraphrasing literary writing styles could be directly benefical for educational applications, for example helping students to experiment with writing literature in the
+style of authors they are studying.
+Additionally note that out of the 37 surviving plays written by William Shakespeare, only 17 currently have modern translations available; although we have not yet formally evaluated
+paraphrasing in the other direction, this work has the potential to additionally make the other 20 plays more accessable to students of Shakespeare.
+
+\begin{comment}
 \begin{itemize}
@@
 \end{itemize}
+\end{comment}
 
 \section{Data}
+We propose to use Shakespeare's plays and their modern English translations as a testbed the task of paraphrasing targeting a specific writing style.  Having access to parallel text in the target
+style allows us to train statistical models for generating paraphrases, and also perform automatic evaluation using BLEU which requires access to a set of reference translations.  For this purpose
+we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}.
+
 \begin{itemize}
   \item Motivate the need for a benchmark dataset for evaluating the writing style paraphrase task
-  \item Present Shakespere / Modern translation data as a situation where we have parallel data available (useful for building models \& evaluating automatic evaluation metrics)
+  \item Present Shakespeare / Modern translation data as a situation where we have parallel data available (useful for building models \& evaluating automatic evaluation metrics)
 \end{itemize}
@@
 \begin{itemize}
-  \item Describe the need for automatic evauation metrics.
+  \item Describe the need for automatic evaluation metrics.
   \item Describe previously used evaluation metrics for paraphrase.
@@
   \item Present results from human evaluation comparing various systems.
-  \item Analyze correlation between evaluation metrics and human judgements.
+  \item Analyze correlation between evaluation metrics and human judgments.
 \end{itemize}

### 2012-08-23 paper/paper.tex
further progress on writing...

@@
 Identical meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
-fundamental to many natural language understanding tasks\cite{}, so much previous work has investigated methods for automatic paraphrasing.  Two different
-utterances may be semantically equivelant, however they can also be styalistically quite different.  For example, the same information information about a new product
+fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.
+Although two utternaces may be semantically equivelant, they can still be stylistically quite different.  For example, the same information information about a new product
 is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.
@@
 baseline systems which don't make use of this source of parallel text and instead rely on dictionaries of expressions commonly found in shakesperean english, or parallel monolingual text
-gathered through Amazon's Mechanical Turk \cite{}.
+gathered through Amazon's Mechanical Turk \cite{chen11}.
 
-We evaluate these models both through human judgements and standard evaluation metrics from the Machine Translation and paraphrase literature, however no previous work has investigated the ability of automatic metrics
+We evaluate these models both through human judgements and standard evaluation metrics from the Machine Translation and paraphrase literature, however no previous work has investigated the ability of these automatic metrics
 to capture the notion of writing style.  We propose several new metrics for evaluating the task of paraphrasing while targeting a specific style, and measure correlation with human judgement showing
@@
 Additionally note that out of the 37 surviving plays written by William Shakespeare, only 17 currently have modern translations available; although we have not yet formally evaluated
-paraphrasing in the other direction, this work has the potential to additionally make the other 20 plays more accessable to students of Shakespeare.
+paraphrasing in the other direction, this work also has the potential to make the other 20 plays more accessable to students of Shakespeare.
 
@@
 style allows us to train statistical models for generating paraphrases, and also perform automatic evaluation using BLEU which requires access to a set of reference translations.  For this purpose
-we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}.
+we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}, and an additional 8 translations of overlapping plays from \url{http://enotes.com}, giving us
+two reference translations for 8 out of the 17 plays.
+
+After tokenizing and lowercasing, the plays and their modern translations were aligned using Bob Moore's bilingual sentence \cite{Moore02} aligner producing about 21,079 alignments out of 31,718 sentences
+in the Sparknotes data, and 10,365 aligned sentence pairs out of 13,640 sentences in the enotes data.  In addition, we note that the modern translations from each source are qualitatively quite
+different.  The Sparknotes paraphrases tend to differ more significantly from the original texts, whereas the enotes data tends to stick closer to the original text, being much more conservative
+in it's use of paraphrase, although it does include many useful paraphrses which do tend to be qualitatively different from those used in the Sparknotes data.
+%TODO: need examples of differences between the corpora?
+To illustrate these differences empircally, we evaluated a very simple paraphrase system using the standard BLEU evaluation metric which has been shown to be a useful measure of semantic equivelance
+in Parapharse \cite{chen11}.
+These corpus statistics are summarized in table \ref{corpus_stats}.
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{|l|r|r|r|}
+      \hline
+      corpus & initial size & aligned size & No-Change BLEU\\
+      \hline
+      \hline
+      \url{http://nfs.sparknotes.com} & 31,718 & 21,079 & 23.67 \\
+      \hline
+      \url{http://enotes.com} & 13,640 & 10,365 & 49.60 \\
+      \hline
+    \end{tabular}
+  \end{center}
+  \caption{Parallel corpora generated form modern translations of Shakespeare's plays}
+  \label{corpus_stats}
+\end{table}
 
@@
 
-\bibliography{colingbiblio}
+\bibliography{paper.bib}
 

### 2012-08-24 paper/paper.tex
a bit of progress on writing...

@@
 %style.  
-We empirically show that even with a relatively small amount of parallel training data available, it is
+We show that even with a relatively small amount of parallel training data available, it is
 possible to learn paraphrase models which capture stylistic phenomenon, and these models outperform
@@
 fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.
-Although two utternaces may be semantically equivelant, they can still be stylistically quite different.  For example, the same information information about a new product
+Although two utternaces may be semantically equivelant, they can still be stylistically quite different.  For example, the same information
 is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.
 
-In this paper, we investigate the task of automatic paraphrasing when targeting a specific writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
-We exploit modern translations of 17 plays written to help literature students to better understand Shakespeare.
-These modern translations are used to generate a parallel corpus of Shakespere's style and modern English,
+In this paper, we investigate the task of automatic paraphrasing when targeting a writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
+We exploit modern translations of 17 plays written to help students better understand Shakespeare's work.  A parallel corpus is extracted from these modern translations,
 which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakesperean English.  In addition we develop several
-baseline systems which don't make use of this source of parallel text and instead rely on dictionaries of expressions commonly found in shakesperean english, or parallel monolingual text
+baseline systems which don't make use of this source of parallel text and instead rely on dictionaries of expressions commonly found in Shakesperean english, or parallel monolingual text
 gathered through Amazon's Mechanical Turk \cite{chen11}.
@@
 We evaluate these models both through human judgements and standard evaluation metrics from the Machine Translation and paraphrase literature, however no previous work has investigated the ability of these automatic metrics
-to capture the notion of writing style.  We propose several new metrics for evaluating the task of paraphrasing while targeting a specific style, and measure correlation with human judgement showing
-promising results for this particular style.
+to capture the notion of writing style.
+We propose several new metrics for evaluating paraphrases targeting a specific writing style, and measure correlation with human judgements showing  promising, yet
+preliminary results.
 
@@
 Additionally note that out of the 37 surviving plays written by William Shakespeare, only 17 currently have modern translations available; although we have not yet formally evaluated
-paraphrasing in the other direction, this work also has the potential to make the other 20 plays more accessable to students of Shakespeare.
+paraphrasing in the other direction, we believe this work also has the potential to make the other 20 plays more accessable to students of Shakespeare by automatically generating relatively high-quality modern translations.
 
@@
 \section{Data}
-We propose to use Shakespeare's plays and their modern English translations as a testbed the task of paraphrasing targeting a specific writing style.  Having access to parallel text in the target
+We compare 3 different stylisitic paraphrase systems targeting Shakesperean English.  One which leverages parallel corpora of modern translations, another which makes use
+of dictionaries of styalistically representative expressions, and another which leverages out-of-domain monolingual parallel data.
+
+\subsection{Modern Translations}
+We propose to use Shakespeare's plays and their modern English translations as a testbed for the task of paraphrasing while targeting a specific writing style.
+Having access to parallel text in the target
 style allows us to train statistical models for generating paraphrases, and also perform automatic evaluation using BLEU which requires access to a set of reference translations.  For this purpose
@@
 
-After tokenizing and lowercasing, the plays and their modern translations were aligned using Bob Moore's bilingual sentence \cite{Moore02} aligner producing about 21,079 alignments out of 31,718 sentences
-in the Sparknotes data, and 10,365 aligned sentence pairs out of 13,640 sentences in the enotes data.  In addition, we note that the modern translations from each source are qualitatively quite
-different.  The Sparknotes paraphrases tend to differ more significantly from the original texts, whereas the enotes data tends to stick closer to the original text, being much more conservative
-in it's use of paraphrase, although it does include many useful paraphrses which do tend to be qualitatively different from those used in the Sparknotes data.
-%TODO: need examples of differences between the corpora?
-To illustrate these differences empircally, we evaluated a very simple paraphrase system using the standard BLEU evaluation metric which has been shown to be a useful measure of semantic equivelance
-in Parapharse \cite{chen11}.
+After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence \cite{Moore02} aligner, which produced about 21,079 alignments out of 31,718 sentences
+in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the enotes data.  The modern translations from each source are qualitatively quite
+different.  The Sparknotes paraphrases tend to differ significantly from the original text, whereas the enotes translations are much more conservative, making fewer changes.
+To illustrate these differences empirically and provide an initial paraphrase baseline, we computed BLEU scores of the unchanged modern translations against Shakespeare's 
+original text; the Sparknotes paraphrases result in a BLEU score of 23.67, whereas the Enotes paraphrases prouce a much higher BLEU of 49.60 indicating their similarity to the original text.
 These corpus statistics are summarized in table \ref{corpus_stats}.
+
+\subsection{Dictionaries}
+
+\subsection{Out of Domain Monolingual Parallel Data}
 
@@
 
+\begin{comment}
 \begin{itemize}
@@
 \end{itemize}
+\end{comment}
 

### 2012-08-24 paper/paper.tex
more writing progress..

@@
 \section{Data}
+We propose to use Shakespeare's plays as a testbed for the task of paraphrasing while targeting a specific writing style.  Because these plays are some of the
+highest regarded examples of English literature and are also very unique in style, many linguistic resources are available such as parallel corpora
+of modern translations and dictionaries of stylistically representative words and their modern equivelants.
+
 We compare 3 different stylisitic paraphrase systems targeting Shakesperean English.  One which leverages parallel corpora of modern translations, another which makes use
@@
 \subsection{Modern Translations}
-We propose to use Shakespeare's plays and their modern English translations as a testbed for the task of paraphrasing while targeting a specific writing style.
-Having access to parallel text in the target
-style allows us to train statistical models for generating paraphrases, and also perform automatic evaluation using BLEU which requires access to a set of reference translations.  For this purpose
-we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}, and an additional 8 translations of overlapping plays from \url{http://enotes.com}, giving us
-two reference translations for 8 out of the 17 plays.
+Having access to parallel text in the target style allows us to train statistical models for generating paraphrases, and also perform automatic evaluation of semantic adequacy using BLEU, which requires access to a set of reference translations.
+For this purpose we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}, and an additional 8 translations of overlapping plays from \url{http://enotes.com}, giving us two reference translations for 8 out of the 17 plays.
 
-After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence \cite{Moore02} aligner, which produced about 21,079 alignments out of 31,718 sentences
-in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the enotes data.  The modern translations from each source are qualitatively quite
+After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence \cite{Moore02} aligner, which produced about 21,079 alignments out of 31,718 sentences in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the enotes data.
+The modern translations from each source are qualitatively quite
 different.  The Sparknotes paraphrases tend to differ significantly from the original text, whereas the enotes translations are much more conservative, making fewer changes.
@@
 These corpus statistics are summarized in table \ref{corpus_stats}.
-
-\subsection{Dictionaries}
-
-\subsection{Out of Domain Monolingual Parallel Data}
 
@@
 
-\begin{comment}
+\subsection{Baselines}
+Phrase-based translation has been demonstrated to be an effective approach to generating paraphrses \cite{chen11,quirk04}, however this approach does require the existence of
+parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches.
+
+\subsubsection{Dictionary Based Paraphrase}
+Several dictionaries of stylistically representative words of Shakesperean English and their modern equivelants are available on the web.  These dictionaries can be used 
+to define a translation model which is used in combination with a language model as in standard phrase-based MT \cite{knight}.
+
+We gathered a set of 2,386  dictionary entries which were scraped from \url{http:/www.william-shakespeare.info} and semi-automaticaly cleaned.  Example
+dictionary entries are presented in table \ref{dictionary_example}.
+
+{\bf TODO:} need to describe how parameters were learned and combined with LM
+
+\begin{table}
+  \begin{center}
+  \begin{tabular}{|l|l||l|l|}
+    \hline
+    target & source & target & source \\
+    \hline
+    \hline
+    ABATE & shorten & ANIGHT & by night \\
+    \hline
+    CAUTEL & deceit & CHILDING & pregnant \\
+    \hline
+    FOIL & defeat & MORTAL & deadly \\
+    \hline
+  \end{tabular}
+  \end{center}
+  \caption{Exaple dictionary entries}
+  \label{dictionary_example}
+\end{table}
+
+\subsubsection{Out of Domain Monolingual Parallel Data}
+
+\subsection{Initial Comparison}
 \begin{itemize}
-  \item Motivate the need for a benchmark dataset for evaluating the writing style paraphrase task
-  \item Present Shakespeare / Modern translation data as a situation where we have parallel data available (useful for building models \& evaluating automatic evaluation metrics)
+  \item List the various systems we evaluate (e.g. varying LM size, etc...)
+  \item Plot BLEU and PINC scores for the various systems
 \end{itemize}
-\end{comment}
 

### 2012-08-24 paper/paper.tex
minor changes..

@@
 \subsubsection{Out of Domain Monolingual Parallel Data}
+As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
+\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of doimain parallel text, with an in-domain
+language model consisting of Shakespeare's 37 plays.
 
-\subsection{Initial Comparison}
+\subsection{Comparison Using Automatic Evaluation Metrics}
 \begin{itemize}

### 2012-08-25 paper/paper.tex
added figures

@@
 Several dictionaries of stylistically representative words of Shakesperean English and their modern equivelants are available on the web.  These dictionaries can be used 
-to define a translation model which is used in combination with a language model as in standard phrase-based MT \cite{knight}.
+to define a translation model which is used in combination with a language model as in standard phrase-based MT \cite{Koehn00}.
 
@@
 \cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of doimain parallel text, with an in-domain
-language model consisting of Shakespeare's 37 plays.
+language model consisting of Shakespeare's 37 plays.  Although this monolingual parallel data does not include text in the target writing style,
+the in-domain language model does bias the generated sentences towards Shakespeare's writing style.
 
 \subsection{Comparison Using Automatic Evaluation Metrics}
+Figure \ref{bleupinc} compares a variety of sytstems targeting Shakesperean English using previously the previosly proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics.
+
+\begin{figure}
+  \begin{center}
+    \begin{tabular}{cc}
+      \includegraphics[width=2.1in]{figures/bleupinc1.pdf} & \includegraphics[width=2.1in]{figures/bleupinc2.pdf} \\
+    \end{tabular}
+  \end{center}
+  \caption{Various Shakesperean Paraphrase systems compared using BLEU and PINC.}
+  \label{bleupinc}
+\end{figure}
+
 \begin{itemize}

### 2012-08-25 paper/figures/plot.R

@@ -1,0 +1,21 @@
+data = read.csv('bleupinc.csv', sep="\t", header=TRUE)
+data = data[data$corpus == 1,]
+
+pdf('bleupinc1.pdf', width=6, height=6)
+
+plot(data$PINC, data$BLEU, pch=1:dim(data)[1], xlab='PINC', ylab='BLEU')
+title("Corpus 1")
+legend("bottomleft", legend=data$system, pch=1:dim(data)[1])
+
+dev.off()
+
+data = read.csv('bleupinc.csv', sep="\t", header=TRUE)
+data = data[data$corpus == 2,]
+
+pdf('bleupinc2.pdf', width=6, height=6)
+
+plot(data$PINC, data$BLEU, pch=1:dim(data)[1], xlab='PINC', ylab='BLEU')
+title("Corpus 2")
+legend("bottomleft", legend=data$system, pch=1:dim(data)[1])
+
+dev.off()

### 2012-08-25 paper/paper.tex
minor change

@@
 
-\subsection{Comparison Using Automatic Evaluation Metrics}
+\subsection{Comparison Using Existing Automatic Evaluation Metrics}
 Figure \ref{bleupinc} compares a variety of sytstems targeting Shakesperean English using previously the previosly proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics.

### 2012-08-25 paper/paper.tex
some more writing...

@@
 To illustrate these differences empirically and provide an initial paraphrase baseline, we computed BLEU scores of the unchanged modern translations against Shakespeare's 
-original text; the Sparknotes paraphrases result in a BLEU score of 23.67, whereas the Enotes paraphrases prouce a much higher BLEU of 49.60 indicating their similarity to the original text.
+original text; the Sparknotes paraphrases result in a BLEU score of 24.67, whereas the Enotes paraphrases prouce a much higher BLEU of 52.30 indicating their similarity to the original text.
 These corpus statistics are summarized in table \ref{corpus_stats}.
@@
 \subsubsection{Dictionary Based Paraphrase}
+\label{dictionary_baseline}
 Several dictionaries of stylistically representative words of Shakesperean English and their modern equivelants are available on the web.  These dictionaries can be used 
@@
 Figure \ref{bleupinc} compares a variety of sytstems targeting Shakesperean English using previously the previosly proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics.
+A summary of each system is presented in table \ref{systems}.
+Notice that the enotes data is quite similar to the original translations,
+obtaining a BLEU score of 52.3 when compared against the original text.  Our goal is to produce paraphrases which make many changes to the input, therefore
+in the remainder of this paper, we focus our evaluation on the Sparknotes data for evaluation.
+
+Two main trends emerge from figure \ref{bleupinc}.  First, notice that all of the systems which are trained using parallel text achieve higher BLEU scores than the baseline
+of not making any changes to the modern translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making significant changes to the 
+input, it's BLEU is lower than the \emph{no changes} baseline.  Secondly, it seems apparent that the systems whose parameters are learned using Minimum Error Rate training
+tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, but not seeing any BLEU improvements on the test data.  Finally
+we note that using the larger language model seems to yield a slight improvement in BLEU score.
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{|l|p{3in}|}
+      \hline
+      System & Description \\
+      \hline
+      \hline
+      16and7plays\_36LM & Phrase table learned from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, excluding R\&J.
+      Uses default Moses parameters. \\
+      \hline
+      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training instead of using the default Moses parameters.\\
+      \hline
+      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 with modern translations\\
+      \hline
+      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
+      \hline
+      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakesperean language model. a\\
+      \hline
+      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
+      \hline
+      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
+      \hline
+      Dictionary & Dictionary baseline described in section \ref{dictionary_baseline}\\
+      \hline
+    \end{tabular}
+  \end{center}
+  \caption{Descriptions of various systems for Shakesperean Paraphrase.  Romeo and Juliet is held out for testing.}
+  \label{systems}
+\end{table}
 
@@
     \begin{tabular}{cc}
-      \includegraphics[width=2.1in]{figures/bleupinc1.pdf} & \includegraphics[width=2.1in]{figures/bleupinc2.pdf} \\
+      \includegraphics[width=2.4in]{figures/bleupinc1.pdf} & \includegraphics[width=2.4in]{figures/bleupinc2.pdf} \\
     \end{tabular}
@@
 
-\begin{itemize}
-  \item List the various systems we evaluate (e.g. varying LM size, etc...)
-  \item Plot BLEU and PINC scores for the various systems
-\end{itemize}
+Several example paraphrases generated by our system, both from Romeo and Juliet and several Hollywood movies are presented in table \ref{examples}.
+
+\begin{table}
+  \begin{tabular}{|l|l|}
+    \hline
+    Source & Input & Output \\
+    \hline
+    \hline
+    Romeo \& Juliet & & \\
+    Star Wars & & \\
+    \hline
+  \end{tabular}
+\end{table}
 

### 2012-08-25 paper/figures/plot.R

@@ -4,7 +4,7 @@ data = data[data$corpus == 1,]
 pdf('bleupinc1.pdf', width=6, height=6)
 
 plot(data$PINC, data$BLEU, pch=1:dim(data)[1], xlab='PINC', ylab='BLEU')
-title("Corpus 1")
+title("Sparknotes")
 legend("bottomleft", legend=data$system, pch=1:dim(data)[1])
 
 dev.off()
@@ -15,7 +15,7 @@ data = data[data$corpus == 2,]
 pdf('bleupinc2.pdf', width=6, height=6)
 
 plot(data$PINC, data$BLEU, pch=1:dim(data)[1], xlab='PINC', ylab='BLEU')
-title("Corpus 2")
+title("Enotes")
 legend("bottomleft", legend=data$system, pch=1:dim(data)[1])
 
 dev.off()

### 2012-08-25 paper/paper.tex
added some examples

@@
       \hline
-      \url{http://nfs.sparknotes.com} & 31,718 & 21,079 & 23.67 \\
+      \url{http://nfs.sparknotes.com} & 31,718 & 21,079 & 24.67 \\
       \hline
-      \url{http://enotes.com} & 13,640 & 10,365 & 49.60 \\
+      \url{http://enotes.com} & 13,640 & 10,365 & 52.30 \\
       \hline
@@
 \begin{table}
-  \begin{tabular}{|l|l|}
+  \begin{center}
+    \begin{tabular}{|l|l|p{1.4in}|p{1.4in}|}
       \hline
-    Source & Input & Output \\
+      Source & Speaker & Input & Output \\
       \hline
       \hline
-    Romeo \& Juliet & & \\
-    Star Wars & & \\
+      Romeo \& Juliet & Benvolio & he killed your relative , brave mercutio , and then young romeo killed him . & he slew thy kinsman , brave mercutio , and then young romeo kill him . \\
+      \hline
+      Romeo \& Juliet & Romeo & i can read my own fortune in my misery . & i can read mine own fortune in my woes . \\
+      \hline
+      Star Wars & Palpatine & If you will not be turned, you will be destroyed! & if you will not be turn 'd , you will be undone ! \\
+      \hline
+      Star Wars & Luke & Father, please! Help me! & father , i pray you , help me ! \\    
+      \hline
+      The Matrix & Agent Smith & Good bye, Mr. Anderson. & fare you well , good master anderson . \\
+      \hline
+      The Matrix & Morpheus & I'm trying to free your mind, Neo.
+But I can only show you the door.
+You're the one that has to walk through it.
+& i 'll to free your mind , neo.
+but i can but show you the door.
+you 're the one that hath to tread it .
+\\
+      \hline
+      Raiders of the Lost Ark & Belloq & Good afternoon, Dr. Jones. & well met , dr. jones . \\
+      \hline
+      Raiders of the Lost Ark & Jones & I ought to kill you right now. & i should kill thee straight . \\
       \hline
     \end{tabular}
+  \end{center}
+  \caption{Example Shakesperean paraphrases generated by the best overall system.}
 \end{table}

### 2012-08-25 paper/paper.tex
added human judgements bargraph

@@
 
-\section{Evaluation Metrics}
-\begin{itemize}
-  \item Describe the need for automatic evaluation metrics.
-  \item Describe previously used evaluation metrics for paraphrase.
-  \item Highlight problems with previous metrics when targeting a specific writing style.
-  \item Propose new metrics.
-\end{itemize}
+\section{Human Evaluation}
+Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is innitially unclear how well the BLEU and PINC
+automatic evaluation metrics perform when applied to evaluating paraphrases targeting a specific style of writing.  BLEU and PINC have previously
+been shown to have high correlation with human judgements of semantic adequacy and lexical dissimilarity of paraphrase candidates, however no
+previous work has evaluated automatically generated paraphrases which target a specific style of writing \cite{chen11}.
+
+While BLEU is typically used to measure semantic adequacy, it seems reasonable to assume that it may also depend on style, since utterances
+are more likely to contain overlapping ngrams if they are both semantically and stylistically similar.  What BLEU doesn't tell us, however
+is what portion of it's improvements are due to stylistic similarity or semantic equivelance.  For this reason, we were motivated perform
+an evaluation based on human judgements of semantic adequacy, lexical dissimilarity and stylistic similarity.
+
+For this purpose, we randomly sampled 100 lines from Romeo and Juliet, then two of the authors annotated each sentence and it's Shakesperean
+translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overal quality.
+The aggregate results of the human evaluation are displayed in figure \ref{human_judgements}.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=4in]{figures/human_judgements.pdf}
+  \end{center}
+  \caption{Average human judgements evaluating semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality
+    of Shakesperean paraphrase systems} 
+  \label{human_judgements}
+\end{figure}
+
+%Argue why BLEU might capture writing style in addition to semantic adequacy
+%Argue that we really want to seperate these two measures
+%Present initial results from human evaluation (plot? - table?)
+%Plot style vs. equivelance...?
+
+\section{New Metrics Evaluating Writing Style}
 

### 2012-08-25 paper/figures/plot_humanEval.R

@@ -1,0 +1,31 @@
+data = read.csv('../../eval/annotated.csv', sep="\t", header=TRUE)
+data = data[1:99,]
+
+x16plays_36LM_semantic_equiv = data$semantic.equiv
+x16plays_36LM_dissimilarity = data$dissimilarity
+x16plays_36LM_style = data$style
+x16plays_36LM_overall = data$overall
+
+Dictionary_semantic_equiv = data$semantic.equiv.1
+Dictionary_dissimilarity = data$dissimilarity.1
+Dictionary_style = data$style.1
+Dictionary_overall = data$overall.1
+
+video_baseline_semantic_equiv = data$semantic.equiv.2
+video_baseline_dissimilarity = data$dissimilarity.2
+video_baseline_style = data$style.2
+video_baseline_overall = data$overall.2
+
+pdf('human_judgements.pdf', width=6, height=6)
+
+barplot(
+	rbind(
+		c(mean(x16plays_36LM_semantic_equiv), mean(x16plays_36LM_dissimilarity), mean(x16plays_36LM_style), mean(x16plays_36LM_overall)), 
+		c(mean(Dictionary_semantic_equiv), mean(Dictionary_dissimilarity), mean(Dictionary_style), mean(Dictionary_overall)),
+		c(mean(video_baseline_semantic_equiv), mean(video_baseline_dissimilarity), mean(video_baseline_style), mean(video_baseline_overall))),
+	names.arg=c('semantic adequacy', 'dissimilarity', 'style', 'overall'), beside=TRUE)
+title("Average Human Judgements")
+
+legend("topright", legend=c('16plays_36LM', 'Dictionary', 'Video Baseline'), fill=(gray.colors(n=5)))
+
+dev.off()

### 2012-08-25 paper/paper_wei.tex
add a bit into paper about dict-base baseline

--- 2012-08-25 paper/paper.tex
@@
 Identical meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
-fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.
-Although two utternaces may be semantically equivelant, they can still be stylistically quite different.  For example, the same information
+fundamental to many natural language understanding tasks \cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.
+Although two utterances may be semantically equivalent, they can still be stylistically quite different.  For example, the same information
 is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.
@@
 baseline systems which don't make use of this source of parallel text and instead rely on dictionaries of expressions commonly found in Shakesperean english, or parallel monolingual text
-gathered through Amazon's Mechanical Turk \cite{chen11}.
+gathered through crowd sourcing platforms such as Amazon's Mechanical Turk \cite{chen11}.
 
@@
 
-Systems which are capable of automatically paraphrasing literary writing styles could be directly benefical for educational applications, for example helping students to experiment with writing literature in the
+Systems which are capable of automatically paraphrasing literary writing styles could be directly beneficial for educational applications, for example helping students to experiment with writing literature in the
 style of authors they are studying.
 Additionally note that out of the 37 surviving plays written by William Shakespeare, only 17 currently have modern translations available; although we have not yet formally evaluated
-paraphrasing in the other direction, we believe this work also has the potential to make the other 20 plays more accessable to students of Shakespeare by automatically generating relatively high-quality modern translations.
+paraphrasing in the other direction, we believe this work also has the potential to make the other 20 plays more accessible to students of Shakespeare by automatically generating relatively high-quality modern translations.
 
@@
 highest regarded examples of English literature and are also very unique in style, many linguistic resources are available such as parallel corpora
-of modern translations and dictionaries of stylistically representative words and their modern equivelants.
+of modern translations and dictionaries of stylistically representative words and their modern equivalents.
 
-We compare 3 different stylisitic paraphrase systems targeting Shakesperean English.  One which leverages parallel corpora of modern translations, another which makes use
-of dictionaries of styalistically representative expressions, and another which leverages out-of-domain monolingual parallel data.
+We compare 3 different stylistic paraphrase systems targeting Shakesperean English.  One which leverages parallel corpora of modern translations, another which makes use
+of dictionaries of stylistically representative expressions, and another which leverages out-of-domain monolingual parallel data.
 
@@
 
-After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence \cite{Moore02} aligner, which produced about 21,079 alignments out of 31,718 sentences in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the enotes data.
+After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence \cite{Moore02} aligner, which produced about 21,079 alignments out of 31,718 sentences in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the Enotes data.
 The modern translations from each source are qualitatively quite
-different.  The Sparknotes paraphrases tend to differ significantly from the original text, whereas the enotes translations are much more conservative, making fewer changes.
+different.  The Sparknotes paraphrases tend to differ significantly from the original text, whereas the Enotes translations are much more conservative, making fewer changes.
 To illustrate these differences empirically and provide an initial paraphrase baseline, we computed BLEU scores of the unchanged modern translations against Shakespeare's 
@@
 
-\subsection{Baselines}
-Phrase-based translation has been demonstrated to be an effective approach to generating paraphrses \cite{chen11,quirk04}, however this approach does require the existence of
+\subsection{Baselines} po
+Phrase-based translation has been demonstrated to be an effective approach to generating paraphrases \cite{chen11,quirk04}, however this approach does require the existence of
 parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches.
@@
 \label{dictionary_baseline}
-Several dictionaries of stylistically representative words of Shakesperean English and their modern equivelants are available on the web.  These dictionaries can be used 
+Several dictionaries of stylistically representative words of Shakesperean English and their modern equivalents are available on the web.  These dictionaries can be used 
 to define a translation model which is used in combination with a language model as in standard phrase-based MT \cite{Koehn00}.
 
-We gathered a set of 2,386  dictionary entries which were scraped from \url{http:/www.william-shakespeare.info} and semi-automaticaly cleaned.  Example
+We gathered a set of 20,138 dictionary entries which were scraped from \url{http://www.shakespeareswords.com/}, then used heuristic rules to extract 68,709 phrase/word pairs.  Example
 dictionary entries are presented in table \ref{dictionary_example}.
+As described in \cite{Koehn00}, we estimate phrase translation probabilities based on the frequencies of the translation words/phrases in the target language - the Shakespearean English.
+
+For instance, if we look at the modern English (*probably define EME, Shakespearean, modern/ordinary etc ...
+I don't know what words to use) word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations.
+We can obtain the following conditional probabilities for each translation according to the n-gram back off model built on Shakespeare's 36 plays by SRILM toolkit (*ref "SRILM an Extensible Language Modeling Toolkit":
 
@@
   \begin{center}
-  \begin{tabular}{|l|l||l|l|}
+  \begin{tabular}{|l|l|}
     \hline
-    target & source & target & source \\
+    target & source \\
     \hline
     \hline
-    ABATE & shorten & ANIGHT & by night \\
+    CRAVE & beg, entreat, request \\
     \hline
-    CAUTEL & deceit & CHILDING & pregnant \\
+    GAGE & pledge, challenge \\
     \hline
-    FOIL & defeat & MORTAL & deadly \\
+    HAPLY & perhaps, maybe, by chance, with luck \\
     \hline
@@
   \end{center}
-  \caption{Exaple dictionary entries}
+  \caption{Example dictionary entries}
   \label{dictionary_example}
@@
 
+\begin{table}
+  \begin{center}
+  \begin{tabular}{|l|l|||}
+    \hline
+    conditional probability & target & source \\
+    \hline
+    \hline
+    0.0000790755 & PERCHANCE & maybe \\
+    \hline
+    0.00003691883 & PERADVENTURE & maybe \\
+    \hline
+    0.00007524298 & HAPLY & maybe \\
+    \hline
+    0.00007141065 & HAPPILY & maybe \\
+    \hline
+  \end{tabular}
+  \end{center}
+  \caption{Word frequency in target language}
+  \label{word_frequency}
+\end{table}
+
 \subsubsection{Out of Domain Monolingual Parallel Data}
-As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
-\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of doimain parallel text, with an in-domain
-language model consisting of Shakespeare's 37 plays.  Although this monolingual parallel data does not include text in the target writing style,
+As a final baseline we consider a paraphrase system which is trained on out-of-domain parallel data gathered by asking users of Amazon's Mechanical Turk Service 
+\cite{Snow08} to describe videos \cite{chen11}.
+(*Maybe describe a bit more of the strength of Chen et al.'s data?) We combine a phrase table extracted from this out-of-domain parallel text, with an in-domain
+language model consisting of Shakespeare's 37 (*should be 36? hold out) plays.  Although this monolingual parallel data does not include text in the target writing style,
 the in-domain language model does bias the generated sentences towards Shakespeare's writing style.

### 2012-08-25 python/style_metric.py

@@ -3,6 +3,7 @@
 import nltk
 nltk.config_megam('/home/aritter/local/bin/megam')
 
+
 import sys
 import math
 import random

### 2012-08-26 paper/paper.tex
merged changes

@@
 
-We gathered a set of 2,386  dictionary entries which were scraped from \url{http:/www.william-shakespeare.info} and semi-automaticaly cleaned.  Example
+We gathered a set of 20,138 dictionary entries which were scraped from \url{http://www.shakespeareswords.com/}, then used heuristic rules to extract 68,709 phrase/word pairs.  Example
 dictionary entries are presented in table \ref{dictionary_example}.
+As described in \cite{Koehn00}, we estimate phrase translation probabilities based on the frequencies of the translation words/phrases in the target language - the Shakespearean English.
+
+For instance, if we look at the modern English (*probably define EME, Shakespearean, modern/ordinary etc ...
+I don't know what words to use) word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations.
+We can obtain the following conditional probabilities for each translation according to the n-gram back off model built on Shakespeare's 36 plays by SRILM toolkit (*ref "SRILM an Extensible Language Modeling Toolkit":
 
@@
   \label{dictionary_example}
+\end{table}
+
+\begin{table}
+  \begin{center}
+  \begin{tabular}{|l|l|l|}
+    \hline
+    conditional probability & target & source \\
+    \hline
+    \hline
+    0.0000790755 & PERCHANCE & maybe \\
+    \hline
+    0.00003691883 & PERADVENTURE & maybe \\
+    \hline
+    0.00007524298 & HAPLY & maybe \\
+    \hline
+    0.00007141065 & HAPPILY & maybe \\
+    \hline
+  \end{tabular}
+  \end{center}
+  \caption{Word frequency in target language}
+  \label{word_frequency}
 \end{table}

### 2012-08-26 paper/paper.tex
more writing...

@@
 \usepackage{comment}
+\usepackage{amsmath}
 %\title{Translating to Shakespeare: A Case Study in Paraphrasing Writing Styles}
@@
 obtaining a BLEU score of 52.3 when compared against the original text.  Our goal is to produce paraphrases which make many changes to the input, therefore
-in the remainder of this paper, we focus our evaluation on the Sparknotes data for evaluation.
+in the remainder of this paper, we focus on the Sparknotes data for evaluation.
 
@@
 
-\begin{table}
+\begin{table}[ht]
   \begin{center}
@@
 
-\begin{figure}
+\begin{figure}[ht]
   \begin{center}
@@
 
+Based on the human evaluation, it appears that the baseline based on the paraphrase data collected by asking Mechanical Turk users to
+describe videos \cite{chen11} has the highest semantic adequacy, however it is also fairly conservative making few changes to the input.
+The dictionary baseline, and system trained on parallel modern translations make a roughly comparable number of changes to the input
+sentences, but the system trained on modern translations achieves higher semantic adequacy, while being rated higher on style and overall.
+
+These results seem roughly in line with the automatic evalution metrics presented in figure \ref{bleupinc}, however with several important
+differences.  Although the video baseline achieves the highest semantic adequacy in the human evaluation, it's BLEU score
+is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
+Note that the BLEU score of 16plays\_36LM is significantly lower when evaluated on the Enotes data.  This makes sense, because the 
+16 plays come from Sparknotes. This system is not trained on the 7 Enotes plays which, whose modern translations tend
+to be slightly different in style.}
+It would appear that in our case BLEU is conflating semantic adequecy with writing style.  Although the paraphrases produced 
+by the video baseline have high semantic adequacy, their style tends to differ from the reference translations resulting
+in fewer ngram matches, and thus a lower BLEU score.
+
 \begin{figure}
@@
 
-%Argue why BLEU might capture writing style in addition to semantic adequacy
-%Argue that we really want to seperate these two measures
-%Present initial results from human evaluation (plot? - table?)
-%Plot style vs. equivelance...?
+\section{Automatic Metrics Evaluating Writing Style}
+While PINC and BLEU do seem useful for automatically evaluating writing styles, BLEU tends to conflate the notions of
+semantic adequacy with writing style.  When comparing various systems using automatic metrics, however, it would seem useful
+to seperate these two critera.  It would seem desirable for our automatic evaluation metrics to be able to distinguish
+between a system which generates perfect paraphrases which don't match the target style of writing and a system which
+generates sentences in the correct style, but which convey different meaning.
 
-\section{New Metrics Evaluating Writing Style}
+To help address this issue we propse two new automatic evaluation metrics whose goal is to measure the degree to which
+autoamtic paraphrases match the target style.  Both metrics assume existence of large corpora in both the source and
+target style, but do not require access to any parallel text, or human judgements.
 
-\section{Experiments}
-\begin{itemize}
-  \item Experimental setup.
-  \item Present results from human evaluation comparing various systems.
-  \item Analyze correlation between evaluation metrics and human judgments.
-\end{itemize}
+We present a preliminary evalutation of these metrics by measuring their correlation with human judgements, however
+we emphasize that here we are only evaluating these metrics with respect to one specific writing style.  We
+are cautionsly optimistic that these results will generalize across writing styles, however, as they are based entirely
+on ngram statistics.
+
+\subsection{Cosine Similarity Style Metric}
+As a first approach automatic evaluation of writing style, we propose a vector-space model of similarity between the system
+output and a large corpus of text in both the source and target style.  The intuition is that if there is a large ngram
+overlap between the system's output and a large corpus of text in the target style, then the output is more likely to be
+stylistically appropriate.
+
+More concretely, we extract ngrams from both the source and target corpus which are then represented as binary
+vectors $\vec{s}$, and $\vec{t}$; similarly the output sentence is represented using a vector of
+ngrams $\vec{o}$.  
+The proposed metric is the normalized cosine similarity between the source and target corpora:
+\[
+S_{\text{Cosine}}(\vec{o}) = \frac{\frac{\vec{o} \cdot \vec{t}}{\|\vec{o}\| \times \|\vec{t}\|}}{\frac{\vec{o} \cdot \vec{t}}{\|\vec{o}\| \times \|\vec{t}\|} + \frac{\vec{o} \cdot \vec{s}}{\|\vec{o}\| \times \|\vec{s}\|}}
+\]
+
+\subsection{Maximum Entropy Style Metric}
+
+\subsection{Evaluation}
 

### 2012-08-26 paper/figures/plot_humanEval.R

@@ -16,7 +16,7 @@ video_baseline_dissimilarity = data$dissimilarity.2
 video_baseline_style = data$style.2
 video_baseline_overall = data$overall.2
 
-pdf('human_judgements.pdf', width=6, height=6)
+pdf('human_judgements.pdf', width=7, height=7)
 
 barplot(
 	rbind(

### 2012-08-26 paper/paper.tex
some more writing...

@@
 \section{Human Evaluation}
+\label{human_evaluation}
 Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is innitially unclear how well the BLEU and PINC
@@
 
-\subsection{Maximum Entropy Style Metric}
+\subsection{Logistic Regression Style Metric}
+We also consider a Logistic Regression based approach as an alternative to evaluating writing style.  The idea here, is to estimate the probability that each
+sentence belongs to the target style, by using a large source and target training corpus to learn the parameters of a logistic regression model.
+This probability is estimated as follows:
+\[
+%P(\text{style} = \text{target}|\text{output}) \propto \text{exp} \left( \vec{\theta} \cdot \vec{f(\text{output})} \right)
+P(\text{style} = \text{target}|\text{sentence}) = \frac{1}{1 + e^{-\left( \vec{\theta} \cdot \vec{f(\text{sentence})} \right)}}
+\]
+Where $\vec{f(\text{sentence})}$ is a vector of ngrams, and $\vec{\theta}$ is a vector of weights.  
+The parameters, $\vec{\theta}$, are optimized on the source and target corpus, where the assumption is that the target corpus
+is in the target style, whereas the source corpus is not.\footnote{
+  Parameters were optimized using MEGAM \url{http://www.cs.utah.edu/~hal/megam/}.
+}
 
 \subsection{Evaluation}
+We trained both Logistic Regression and Cosine Similarity evaluation metrics using the original Shakespeare plays and modern translations as
+the source and target corpus respectively (holding out Romeo and Juliet), then measured Pearson's Correlation Coefficent between the automatic
+evaluation metrics and human judgements reported in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.
+
+\begin{table}
+  \begin{center}
+  \begin{tabular}{|l|l|r|}
+    \hline
+    & & Pearson's $\rho$ \\
+    \hline
+    \hline
+    semantic adequacy & BLEU & 0.35 \\
+    \hline
+    dissimilarity & PINC & 0.78 \\
+    \hline
+    style & BLEU & 0.07 \\
+    \hline
+    style & PINC & 0.20 \\
+    \hline
+    style & Cosine & 0.37 \\
+    \hline
+    style & Maximum Entropy & 0.47 \\
+    \hline
+  \end{tabular}
+  \end{center}
+  \caption{Correlation between various human judgements and automatic evaluation metrics}
+  \label{correlation}
+\end{table}
+
+As can be seen in table \ref{correlation}, the correlation between semantic adequacy and BLEU appears smaller than that reported in previous work \cite{chen11}.  Presumably this is
+due to the conflation of stylistic differences and semantic adequacy discussed discussed in section \ref{human_evaluation}, however the correlation between BLEU and human style
+judgements seems too low to be of practical use.  PINC has very high correlation with judgments on dissimilarity, however we note that it is also highly correlated with human style
+judgements.  To understand why PINC is highly correlated with human style judgements, notice that because the systems we are evaluating are targeting Shakesperean English, when changes
+are made to the input they are likely to be in the target style.  Although PINC has high correlation with human judgements, it is likely not a useful measure of style in practice,
+because for example a paraphrase system which makes many changes to the input, but targets a completely different style will also get a high PINC score.  
+Both the Cosine and Maximum Entropy style metrics achieve the highest overall correlation with human writing style judgements, with the Maximum Entropy score performing significantly better.
 

### 2012-08-26 paper/paper.tex
more progres...

@@
 
+Finally we note that overall the average automatc metrics seem to agree with agree with human judgements as displayed in figure \ref{style_metrics}.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=4in]{figures/style_metrics.pdf}
+    \end{center}
+    \caption{Overall results from comparing automatic style metrics.  Note that the automatic metrics agree with results from human judgements in figure \ref{human_judgements}.}
+    \label{style_metrics}
+\end{figure}
+
 \section{Related Work}
-\begin{itemize}
-  \item Kevin Knight's work on poetry generation
-  \item Any work on writing style (e.g. classification)?  Possibly cite work on author attribution...
-  \item work on paraphrase evaluation metrics (David Chen, CCB, etc...)
-\end{itemize}
+Although no previous work has investigated paraphrasing modern text into Shakesperean English, or the more general task of paraphrasing while targeting a specific writing
+style, there are several strands of related work.
+
+Perhaps most relevant is recent work generating and translating rhythmic poetry \cite{Greene10}.  This work focused on generating text in an appropriate
+meter (e.g. iambic pentameter) using finate-state transducers.  In contrast our work does not address the issue of meter, however it should be possible to combine our translation
+models with their weighted FSTs to produce Shakesperean paraphrase models which produce output in an appropriate meter.
+
+Much previous work has addressed the task of automatically generating paraphrases \cite{Callison-Burch08,Kok10}.  In addition several authors have previously proposed 
+automatic paraphrase evaluation metrics \cite{Callison-Burch08b,Bangalore00,liu10}.
+We are not aware, however, of any previous work that has addressed the task of generating or evaluating
+paraphrases targeting a specific style of writing.
+
+Finally we highlight related work on authorship classification which can be seen as detecting a specific style of writing \cite{Gamon04,Raghavan10}.
+This work has not specifically addressed the task of automatically generating or evaluating paraphrases in a specific style, however.
 

### 2012-08-26 paper/figures/plot_humanEval.R

@@ -1,5 +1,8 @@
 data = read.csv('../../eval/annotated.csv', sep="\t", header=TRUE)
-data = data[1:99,]
+data2 = read.csv('../../eval/annotated_wei.csv', sep="\t", header=TRUE)
+data  = data[1:99,]
+data2 = data2[1:99,]
+data = rbind(data, data2)
 
 x16plays_36LM_semantic_equiv = data$semantic.equiv
 x16plays_36LM_dissimilarity = data$dissimilarity

### 2012-08-26 paper/figures/plot_style.R

@@ -1,0 +1,22 @@
+#16plays36:
+#average-csim	0.512979241631
+#average-cmaxent	0.701862536235
+#phrase2:
+#average-csim	0.491599098577
+#average-cmaxent	0.50375691204
+#video2:
+#average-csim	0.480059827357
+#average-cmaxent	0.456308085791
+
+pdf('style_metrics.pdf', width=7, height=7)
+
+barplot(rbind(
+	c(0.512979241631, 0.491599098577, 0.480059827357),
+	c(0.701862536235, 0.50375691204, 0.456308085791)),
+	names.arg=c('16plays36LM', 'Dictionary', 'Video Baseline'), beside=TRUE)
+
+title("Average Style Metrics")
+
+legend("topright", legend=c('Cosine Similarity', 'Maximum Entropy'), fill=(gray.colors(n=2)))
+
+dev.off()

### 2012-08-26 python/add_scores.py

@@ -66,6 +66,9 @@ for line in open(sys.argv[1]):
     video_cmaxent_list.append(sm.ScoreMaxEnt(video))
     i += 1
 
+def mean(values):
+    return sum(values, 0.0) / len(values)
+
 print "16plays36:"
 print "sematnic-bleu\t" + str(pearsonr(_16plays36_semantic_list, _16plays36_bleu_list))
 print "dissim-pinc\t" + str(pearsonr(_16plays36_dissim_list, _16plays36_pinc_list))
@@ -73,6 +76,8 @@ print "style-bleu\t" + str(pearsonr(_16plays36_style_list, _16plays36_bleu_list)
 print "style-pinc\t" + str(pearsonr(_16plays36_style_list, _16plays36_pinc_list))
 print "style-csim\t" + str(pearsonr(_16plays36_style_list, _16plays36_csim_list))
 print "style-cmaxent\t" + str(pearsonr(_16plays36_style_list, _16plays36_cmaxent_list))
+print "average-csim\t" + str(mean(_16plays36_csim_list))
+print "average-cmaxent\t" + str(mean(_16plays36_cmaxent_list))
 
 print "phrase2:"
 print "semantic-bleu\t" + str(pearsonr(phrase_semantic_list, phrase_bleu_list))
@@ -81,6 +86,8 @@ print "style-bleu\t" + str(pearsonr(phrase_style_list, phrase_bleu_list))
 print "style-pinc\t" + str(pearsonr(phrase_style_list, phrase_pinc_list))
 print "style-csim\t" + str(pearsonr(phrase_style_list, phrase_csim_list))
 print "style-cmaxent\t" + str(pearsonr(phrase_style_list, phrase_cmaxent_list))
+print "average-csim\t" + str(mean(phrase_csim_list))
+print "average-cmaxent\t" + str(mean(phrase_cmaxent_list))
 
 print "video2:"
 print "semantic-bleu\t" + str(pearsonr(video_semantic_list, video_bleu_list))
@@ -89,6 +96,8 @@ print "style-bleu\t" + str(pearsonr(video_style_list, video_bleu_list))
 print "style-pinc\t" + str(pearsonr(video_style_list, video_pinc_list))
 print "style-csim\t" + str(pearsonr(video_style_list, video_csim_list))
 print "style-cmaxent\t" + str(pearsonr(video_style_list, video_cmaxent_list))
+print "average-csim\t" + str(mean(video_csim_list))
[…]

### 2012-08-26 paper/figures/plot_humanEval.R
minor changes

@@ -29,6 +29,6 @@ barplot(
 	names.arg=c('semantic adequacy', 'dissimilarity', 'style', 'overall'), beside=TRUE)
 title("Average Human Judgements")
 
-legend("topright", legend=c('16plays_36LM', 'Dictionary', 'Video Baseline'), fill=(gray.colors(n=5)))
+legend("topright", legend=c('16plays_36LM', 'Dictionary', 'Video Baseline'), fill=(gray.colors(n=3)))
 
 dev.off()

### 2012-08-26 paper/paper.tex
further progres...

@@
 which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakesperean English.  In addition we develop several
-baseline systems which don't make use of this source of parallel text and instead rely on dictionaries of expressions commonly found in Shakesperean english, or parallel monolingual text
-gathered through Amazon's Mechanical Turk \cite{chen11}.
+baseline systems which do not make use of this source of parallel text and instead rely on manually compiled dictionaries of expressions commonly found in Shakesperean english, or out of
+domain parallel monolingual text gathered through Amazon's Mechanical Turk \cite{chen11}.
 
-We evaluate these models both through human judgements and standard evaluation metrics from the Machine Translation and paraphrase literature, however no previous work has investigated the ability of these automatic metrics
-to capture the notion of writing style.
-We propose several new metrics for evaluating paraphrases targeting a specific writing style, and measure correlation with human judgements showing  promising, yet
+We evaluate these models both through human judgements and standard evaluation metrics from the Machine Translation and paraphrase literature, however no previous work has investigated the ability of automatic
+evaluation metrics to capture the notion of writing style.
+We propose several new metrics for evaluating paraphrases targeting a specific writing style, and measure correlation with human judgements showing  promising
 preliminary results.
 
-Systems which are capable of automatically paraphrasing literary writing styles could be directly benefical for educational applications, for example helping students to experiment with writing literature in the
-style of authors they are studying.
-Additionally note that out of the 37 surviving plays written by William Shakespeare, only 17 currently have modern translations available; although we have not yet formally evaluated
-paraphrasing in the other direction, we believe this work also has the potential to make the other 20 plays more accessable to students of Shakespeare by automatically generating relatively high-quality modern translations.
+Systems which are capable of automatically paraphrasing literary writing styles could be directly benefical for educational applications.
+For example, a system which generates paraphrases targeting a specific style
+of writing could help students to experiment with writing literature in that style.
+In addition, out of the 37 surviving plays written by William Shakespeare only 17 currently have modern translations available.  Though we have not yet formally evaluated
+paraphrasing Shakespeare's plays into modern English, we believe it should be possible to make the other 20 plays more accessable to students of Shakespeare by automatically 
+generating high-quality modern translations.
 
@@
 
-\section{Data}
+\section{Shakesperean Paraphrasing}
 We propose to use Shakespeare's plays as a testbed for the task of paraphrasing while targeting a specific writing style.  Because these plays are some of the
@@
 \end{table}
+
+We apply a typical phrase-based Statistical Machine Translation pipeline, performing
+word alignment on the data described in table \ref{corpus_stats} using GIZA++ \cite{Och03}, then extracting phrase pairs and performing decoding using Moses \cite{Koehn07}.
 
@@
       \hline
-      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training instead of using the default Moses parameters.\\
+      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT} instead of using the default Moses parameters.\\
       \hline
@@
 
-\begin{figure}[ht]
+\begin{figure}
   \begin{center}
@@
   \end{center}
-  \caption{Various Shakesperean Paraphrase systems compared using BLEU and PINC.}
+  \caption{Various Shakesperean Paraphrase systems compared using BLEU and PINC.  A brief description of each system is presented in table \ref{systems}.}
   \label{bleupinc}
@@
 
-Several example paraphrases generated by our system, both from Romeo and Juliet and several Hollywood movies are presented in table \ref{examples}.
-
-\begin{table}
+\begin{table}[ht]
   \begin{center}
@@
 
+Several example paraphrases generated by our system, both from Romeo and Juliet and several Hollywood movies are presented in table \ref{examples}.
+
 \section{Human Evaluation}
@@
 
-Based on the human evaluation, it appears that the baseline based on the paraphrase data collected by asking Mechanical Turk users to
-describe videos \cite{chen11} has the highest semantic adequacy, however it is also fairly conservative making few changes to the input.
+Based on the human evaluation, it appears that the baseline combining paraphrases collected from mechanical turk \cite{chen11} with
+a Shakesperean language model has the highest semantic adequacy, however it is also fairly conservative making few changes to the input.
 The dictionary baseline, and system trained on parallel modern translations make a roughly comparable number of changes to the input
@@
 to be slightly different in style.}
-It would appear that in our case BLEU is conflating semantic adequecy with writing style.  Although the paraphrases produced 
+It would appear that in this case BLEU is conflating semantic adequecy with writing style.  Although the paraphrases produced 
 by the video baseline have high semantic adequacy, their style tends to differ from the reference translations resulting
@@
   \begin{center}
-    \includegraphics[width=4in]{figures/human_judgements.pdf}
+    \includegraphics[width=5in]{figures/human_judgements.pdf}
   \end{center}
@@
 \section{Automatic Metrics Evaluating Writing Style}
-While PINC and BLEU do seem useful for automatically evaluating writing styles, BLEU tends to conflate the notions of
+While PINC and BLEU do seem useful for automatically evaluating paraphrases targeting a  writing style, BLEU tends to conflate the notions of
 semantic adequacy with writing style.  When comparing various systems using automatic metrics, however, it would seem useful
@@
   \begin{center}
-    \includegraphics[width=4in]{figures/style_metrics.pdf}
+    \includegraphics[width=5in]{figures/style_metrics.pdf}
     \end{center}
@@
 
-Much previous work has addressed the task of automatically generating paraphrases \cite{Callison-Burch08,Kok10}.  In addition several authors have previously proposed 
-automatic paraphrase evaluation metrics \cite{Callison-Burch08b,Bangalore00,liu10}.
+Much previous work has addressed the task of automatically generating paraphrases \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05,Callison-Burch08,Kok10}.
+In addition several authors have previously proposed
+automatic paraphrase evaluation metrics \cite{chen11,Callison-Burch08b,Bangalore00,liu10}.
 We are not aware, however, of any previous work that has addressed the task of generating or evaluating
@@
 \section{Conclusions}
+We have presented initial investigation into the task of automatic paraphrasing while targeting a specific style of writing.  We proposed Shakespere's plays and their
+modern translations as a tesbed for this task, and developed a series of paraphrase systems targeting Shakesperean English.  We showed that while existing evaluation
+metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivelance with writing style giving an incomplete picture of which systems
+perform better according to each of these critera.
+
+To address the problems we have demonstrated with previous evaluation metrics applied to this task, we have introduced two new metrics for evaluating writing style.
+We measured correlation between automatic metrics and human judgements in the context of paraphrasing writing style, and showed
+that our new metrics have better correlation with human judgements than existing metrics in the context of our data.
+While this evaluation is limited to one specific style of writing, we are optimistic that these or similar metrics will also perform well when
+evaluating other writing styles.
+
+Future work could include automatically translating the remaining 20 of Shakespeare's plays into modern English, which could be benefical to students
+of Shakespere's plays and also to future human translators.
 

### 2012-08-26 paper/figures/plot_humanEval.R

@@ -19,7 +19,7 @@ video_baseline_dissimilarity = data$dissimilarity.2
 video_baseline_style = data$style.2
 video_baseline_overall = data$overall.2
 
-pdf('human_judgements.pdf', width=7, height=7)
+pdf('human_judgements.pdf', width=8, height=5)
 
 barplot(
 	rbind(

### 2012-08-26 paper/figures/plot_style.R

@@ -8,7 +8,7 @@
 #average-csim	0.480059827357
 #average-cmaxent	0.456308085791
 
-pdf('style_metrics.pdf', width=7, height=7)
+pdf('style_metrics.pdf', width=8, height=5)
 
 barplot(rbind(
 	c(0.512979241631, 0.491599098577, 0.480059827357),

### 2012-08-27 paper/paper_wei.tex
fixed the table
Finished the description of dict-based baseline. Note that two tables are also modified.

--- 2012-08-25 paper/paper.tex
@@
 
+We apply a typical phrase-based Statistical Machine Translation pipeline, performing
+word alignment on the data described in table \ref{corpus_stats} using GIZA++ \cite{Och03}, then extracting phrase pairs and performing decoding using Moses \cite{Koehn07}.
+
 \subsection{Baselines}
@@
 
-We gathered a set of 2,386  dictionary entries which were scraped from \url{http:/www.william-shakespeare.info} and semi-automaticaly cleaned.  Example
+We gathered a set of 20,138 dictionary entries which were scraped from \url{http://www.shakespeareswords.com/}, then used heuristic rules to extract 68,709 phrase/word pairs.  Example
 dictionary entries are presented in table \ref{dictionary_example}.
+As described in \cite{Koehn00}, we estimate phrase translation probabilities based on the frequencies of the translation words/phrases in the target language - the Shakespearean English.
 
-{\bf TODO:} need to describe how parameters were learned and combined with LM
+For instance, if we look at the modern English (*probably define EME, Shakespearean, modern/ordinary etc ...
+I don't know what words to use) word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations.
+We can obtain the following conditional probabilities for each translation according to the n-gram back off model built on Shakespeare's 36 plays by SRILM toolkit (*ref "SRILM an Extensible Language Modeling Toolkit") \ref{word_frequency}:
+
+So we can estimate that p(PERCHANGE|maybe) = 0.0000790755 / 0.00026264791 = 0.30107035689, and so forth.
+This method allows us to estimate reasonable translation probabilities in the phrase table.
+Together with language model consisting of Shakespeare's 36 plays (hold out R&J), we can then choose the most likely translations according to the context.
+
+(*Note that I also changed this table below)
 
@@
     \hline
-    ABATE & shorten & ANIGHT & by night \\
+    ABATE & shorten & AYE & always \\
     \hline
-    CAUTEL & deceit & CHILDING & pregnant \\
+    CAUTEL & deceit & GLASS & mirror \\
     \hline
-    FOIL & defeat & MORTAL & deadly \\
+    SUP & have supper & VOICE & vote \\
     \hline
@@
 
+(*Note that I also changed this table below)
+
+\begin{table}
+  \begin{center}
+  \begin{tabular}{|l|l|l|}
+    \hline
+    conditional probability & target & source \\
+    \hline
+    \hline
+    0.0000790755 & PERCHANCE & maybe \\
+    \hline
+    0.00003691883 & PERADVENTURE & maybe \\
+    \hline
+    0.00007524298 & HAPLY & maybe \\
+    \hline
+    0.00007141065 & HAPPILY & maybe \\
+    \hline
+    \hline
+    total 0.00026264791 & & \\
+    \hline
+  \end{tabular}
+  \end{center}
+  \caption{Word frequency in target language}
+  \label{word_frequency}
+\end{table}
+
 \subsubsection{Out of Domain Monolingual Parallel Data}
@@
 \cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of doimain parallel text, with an in-domain
-language model consisting of Shakespeare's 37 plays.  Although this monolingual parallel data does not include text in the target writing style,
+language model consisting of Shakespeare's 37 plays (*should be 36?).  Although this monolingual parallel data does not include text in the target writing style,
 the in-domain language model does bias the generated sentences towards Shakespeare's writing style.
@@
   \caption{Example Shakesperean paraphrases generated by the best overall system.}
+  \label{examples}
 \end{table}
 
+Several example paraphrases generated by our system, both from Romeo and Juliet and several Hollywood movies are presented in table \ref{examples}.
+
 \section{Human Evaluation}
+\label{human_evaluation}
 Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is innitially unclear how well the BLEU and PINC
@@
 translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overal quality.
-The aggregate results of the human evaluation are displayed in figure \ref{human_judgements}.
+The aggregate results of the human evaluation are displayed in figure \ref{human_judgements}.  Agreement between annotators
+measured using Pearson's $\rho$ is displayed in table \ref{annotator_agreement}.
+
+Based on the human evaluation, it appears that the baseline combining paraphrases collected from mechanical turk \cite{chen11} with
+a Shakesperean language model has the highest semantic adequacy, however it is also fairly conservative making few changes to the input.
+The dictionary baseline, and system trained on parallel modern translations make a roughly comparable number of changes to the input
+sentences, but the system trained on modern translations achieves higher semantic adequacy, while being rated higher on style and overall.
+
+These results seem roughly in line with the automatic evalution metrics presented in figure \ref{bleupinc}, however with several important
+differences.  Although the video baseline achieves the highest semantic adequacy in the human evaluation, it's BLEU score
+is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
+Note that the BLEU score of 16plays\_36LM is significantly lower when evaluated on the Enotes data.  This makes sense, because the 
+16 plays come from Sparknotes. This system is not trained on the 7 Enotes plays which, whose modern translations tend
+to be slightly different in style.}
+It would appear that in this case BLEU is conflating semantic adequecy with writing style.  Although the paraphrases produced 
+by the video baseline have high semantic adequacy, their style tends to differ from the reference translations resulting
+in fewer ngram matches, and thus a lower BLEU score.
+
+\begin{table}[ht]
+  \begin{center}
+    \begin{tabular}{|l|l|l|l|}
+      \hline
+      Semantic Adequacy & Lexical Dissimilarity & Style & Overall \\
+      \hline
+      \hline
+      0.73 & 0.82 & 0.64 & 0.62 \\
+      \hline
+    \end{tabular}
+  \end{center}
+  \caption{Agreement between annotators measured using Pearson's $\rho$.}
+  \label{annotator_agreement}
+\end{table}
 
@@
 
-%Argue why BLEU might capture writing style in addition to semantic adequacy
-%Argue that we really want to seperate these two measures
-%Present initial results from human evaluation (plot? - table?)
-%Plot style vs. equivelance...?
+\section{Automatic Metrics Evaluating Writing Style}
+While PINC and BLEU do seem useful for automatically evaluating paraphrases targeting a  writing style, BLEU tends to conflate the notions of
+semantic adequacy with writing style.  When comparing various systems using automatic metrics, however, it would seem useful
+to seperate these two critera.  It would seem desirable for our automatic evaluation metrics to be able to distinguish
+between a system which generates perfect paraphrases which don't match the target style of writing and a system which
+generates sentences in the correct style, but which convey different meaning.
 
-\section{New Metrics Evaluating Writing Style}
+To help address this issue we propse two new automatic evaluation metrics whose goal is to measure the degree to which
+autoamtic paraphrases match the target style.  Both metrics assume existence of large corpora in both the source and
+target style, but do not require access to any parallel text, or human judgements.
 
-\section{Experiments}
-\begin{itemize}
-  \item Experimental setup.
-  \item Present results from human evaluation comparing various systems.
-  \item Analyze correlation between evaluation metrics and human judgments.
-\end{itemize}
+We present a preliminary evalutation of these metrics by measuring their correlation with human judgements, however
+we emphasize that here we are only evaluating these metrics with respect to one specific writing style.  We
+are cautionsly optimistic that these results will generalize across writing styles, however, as they are based entirely
+on ngram statistics.
+
+\subsection{Cosine Similarity Style Metric}
+As a first approach automatic evaluation of writing style, we propose a vector-space model of similarity between the system
+output and a large corpus of text in both the source and target style.  The intuition is that if there is a large ngram
+overlap between the system's output and a large corpus of text in the target style, then the output is more likely to be
+stylistically appropriate.
+
+More concretely, we extract ngrams from both the source and target corpus which are then represented as binary
+vectors $\vec{s}$, and $\vec{t}$; similarly the output sentence is represented using a vector of
+ngrams $\vec{o}$.  
+The proposed metric is the normalized cosine similarity between the source and target corpora:
+\[
+S_{\text{Cosine}}(\vec{o}) = \frac{\frac{\vec{o} \cdot \vec{t}}{\|\vec{o}\| \times \|\vec{t}\|}}{\frac{\vec{o} \cdot \vec{t}}{\|\vec{o}\| \times \|\vec{t}\|} + \frac{\vec{o} \cdot \vec{s}}{\|\vec{o}\| \times \|\vec{s}\|}}
+\]
+
+\subsection{Logistic Regression Style Metric}
+We also consider a Logistic Regression based approach as an alternative to evaluating writing style.  The idea here, is to estimate the probability that each
+sentence belongs to the target style, by using a large source and target training corpus to learn the parameters of a logistic regression model.
+This probability is estimated as follows:
+\[
+%P(\text{style} = \text{target}|\text{output}) \propto \text{exp} \left( \vec{\theta} \cdot \vec{f(\text{output})} \right)
+P(\text{style} = \text{target}|\text{sentence}) = \frac{1}{1 + e^{-\left( \vec{\theta} \cdot \vec{f(\text{sentence})} \right)}}
+\]
+Where $\vec{f(\text{sentence})}$ is a vector of ngrams, and $\vec{\theta}$ is a vector of weights.  
+The parameters, $\vec{\theta}$, are optimized on the source and target corpus, where the assumption is that the target corpus
+is in the target style, whereas the source corpus is not.\footnote{
+  Parameters were optimized using MEGAM \url{http://www.cs.utah.edu/~hal/megam/}.
+}
+
+\subsection{Evaluation}
+We trained both Logistic Regression and Cosine Similarity evaluation metrics using the original Shakespeare plays and modern translations as
+the source and target corpus respectively (holding out Romeo and Juliet), then measured Pearson's Correlation Coefficent between the automatic
+evaluation metrics and human judgements reported in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.
+
+\begin{table}
+  \begin{center}
+  \begin{tabular}{|l|l|r|}
+    \hline
+    & & Pearson's $\rho$ \\
+    \hline
+    \hline
+    semantic adequacy & BLEU & 0.35 \\
+    \hline
+    dissimilarity & PINC & 0.78 \\
+    \hline
+    style & BLEU & 0.07 \\
+    \hline
+    style & PINC & 0.20 \\
+    \hline
+    style & Cosine & 0.37 \\
+    \hline
+    style & Maximum Entropy & 0.47 \\
+    \hline
+  \end{tabular}
+  \end{center}
+  \caption{Correlation between various human judgements and automatic evaluation metrics}
+  \label{correlation}
+\end{table}
+
+As can be seen in table \ref{correlation}, the correlation between semantic adequacy and BLEU appears smaller than that reported in previous work \cite{chen11}.  Presumably this is
+due to the conflation of stylistic differences and semantic adequacy discussed discussed in section \ref{human_evaluation}, however the correlation between BLEU and human style
+judgements seems too low to be of practical use.  PINC has very high correlation with judgments on dissimilarity, however we note that it is also highly correlated with human style
+judgements.  To understand why PINC is highly correlated with human style judgements, notice that because the systems we are evaluating are targeting Shakesperean English, when changes
+are made to the input they are likely to be in the target style.  Although PINC has high correlation with human judgements, it is likely not a useful measure of style in practice,
+because for example a paraphrase system which makes many changes to the input, but targets a completely different style will also get a high PINC score.  
+Both the Cosine and Maximum Entropy style metrics achieve the highest overall correlation with human writing style judgements, with the Maximum Entropy score performing significantly better.
+
+Finally we note that overall the average automatc metrics seem to agree with agree with human judgements as displayed in figure \ref{style_metrics}.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=5in]{figures/style_metrics.pdf}
+    \end{center}
+    \caption{Overall results from comparing automatic style metrics.  Note that the automatic metrics agree with results from human judgements in figure \ref{human_judgements}.}
+    \label{style_metrics}
+\end{figure}
 
 \section{Related Work}
-\begin{itemize}
-  \item Kevin Knight's work on poetry generation
-  \item Any work on writing style (e.g. classification)?  Possibly cite work on author attribution...
-  \item work on paraphrase evaluation metrics (David Chen, CCB, etc...)
-\end{itemize}
+Although no previous work has investigated paraphrasing modern text into Shakesperean English, or the more general task of paraphrasing while targeting a specific writing
+style, there are several strands of related work.
+
+Perhaps most relevant is recent work generating and translating rhythmic poetry \cite{Greene10}.  This work focused on generating text in an appropriate
+meter (e.g. iambic pentameter) using finate-state transducers.  In contrast our work does not address the issue of meter, however it should be possible to combine our translation
+models with their weighted FSTs to produce Shakesperean paraphrase models which produce output in an appropriate meter.
+
+Much previous work has addressed the task of automatically generating paraphrases \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05,Callison-Burch08,Kok10}.
+In addition several authors have previously proposed
+automatic paraphrase evaluation metrics \cite{chen11,Callison-Burch08b,Bangalore00,liu10}.
+We are not aware, however, of any previous work that has addressed the task of generating or evaluating
+paraphrases targeting a specific style of writing.
+
+Finally we highlight related work on authorship classification which can be seen as detecting a specific style of writing \cite{Gamon04,Raghavan10}.
+This work has not specifically addressed the task of automatically generating or evaluating paraphrases in a specific style, however.
 
 \section{Conclusions}
+We have presented initial investigation into the task of automatic paraphrasing while targeting a specific style of writing.  We proposed Shakespere's plays and their
+modern translations as a tesbed for this task, and developed a series of paraphrase systems targeting Shakesperean English.  We showed that while existing evaluation
+metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivelance with writing style giving an incomplete picture of which systems
+perform better according to each of these critera.
+
+To address the problems we have demonstrated with previous evaluation metrics applied to this task, we have introduced two new metrics for evaluating writing style.
+We measured correlation between automatic metrics and human judgements in the context of paraphrasing writing style, and showed
+that our new metrics have better correlation with human judgements than existing metrics in the context of our data.
+While this evaluation is limited to one specific style of writing, we are optimistic that these or similar metrics will also perform well when
+evaluating other writing styles.
+
+Future work could include automatically translating the remaining 20 of Shakespeare's plays into modern English, which could be benefical to students
+of Shakespere's plays and also to future human translators.
 

### 2012-08-27 paper/paper.tex
minor changes
minor changes...

@@
 
-We gathered a set of 20,138 dictionary entries which were scraped from \url{http://www.shakespeareswords.com/}, then used heuristic rules to extract 68,709 phrase/word pairs.  Example
-dictionary entries are presented in table \ref{dictionary_example}.
+%We gathered a set of 20,138 dictionary entries which were scraped from \url{http://www.shakespeareswords.com/}, then used heuristic rules to extract 68,709 phrase/word pairs.  Example
+%dictionary entries are presented in table \ref{dictionary_example}.
 As described in \cite{Koehn00}, we estimate phrase translation probabilities based on the frequencies of the translation words/phrases in the target language - the Shakespearean English.
 
-For instance, if we look at the modern English (*probably define EME, Shakespearean, modern/ordinary etc ...
-I don't know what words to use) word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations.
-We can obtain the following conditional probabilities for each translation according to the n-gram back off model built on Shakespeare's 36 plays by SRILM toolkit (*ref "SRILM an Extensible Language Modeling Toolkit":
+We scraped a set of 68,709 phrase/word pairs from \url{http://www.shakespeareswords.com/}.  
+Example dictionary entries are presented in table \ref{dictionary_example}.
 
-{\bf TODO:} need to describe how parameters were learned and combined with LM
+%As described in \cite{Koehn00}, we estimate phrase translation probabilities based on the frequencies of the translation words/phrases in the target language - the Shakespearean English. 
+As described in \cite{Koehn00}, we estimate phrase translation probabilities based on the frequencies of the translation words/phrases in the target language (Shakespearean English).
+For instance, if we look at the modern English word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations. 
+We obtained the conditional probabilities for each translation according to the n-gram back off model built on Shakespeare's 
+36 plays by SRILM toolkit \cite{Stolcke02} \ref{word_frequency}, 
+normalizing the probabilities for each source phrase, for example $p(\text{PERCHANGE}|\text{maybe}) = \frac{0.0000790755}{0.00026264791} = 0.30107035689$. 
+This method allows us to estimate reasonable translation probabilities for use in a phrase table, which is used in combination 
+with a language model consisting of Shakespeare's 36 plays (holding out Romeo and Juliet), which are then be fed into the Moses decoder
+\cite{Koehn07}.
 
@@
     \hline
-    conditional probability & target & source \\
+    Smoothed Probability Estimate & target & source \\
     \hline
@@
     \hline
+    \hline
+    total 0.00026264791 & & \\
+    \hline
   \end{tabular}
   \end{center}
-  \caption{Word frequency in target language}
+  \caption{Example ngram probabilities in target language}
   \label{word_frequency}
@@
   \caption{Example Shakesperean paraphrases generated by the best overall system.}
+  \label{examples}
 \end{table}
@@
 translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overal quality.
-The aggregate results of the human evaluation are displayed in figure \ref{human_judgements}.
+The aggregate results of the human evaluation are displayed in figure \ref{human_judgements}.  Agreement between annotators
+measured using Pearson's $\rho$ is displayed in table \ref{annotator_agreement}.
 
@@
 in fewer ngram matches, and thus a lower BLEU score.
+
+\begin{table}[ht]
+  \begin{center}
+    \begin{tabular}{|l|l|l|l|}
+      \hline
+      Semantic Adequacy & Lexical Dissimilarity & Style & Overall \\
+      \hline
+      \hline
+      0.73 & 0.82 & 0.64 & 0.62 \\
+      \hline
+    \end{tabular}
+  \end{center}
+  \caption{Agreement between annotators measured using Pearson's $\rho$.}
+  \label{annotator_agreement}
+\end{table}
 

### 2012-08-27 paper/paper.tex
some polishing

@@
 fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.
-Although two utternaces may be semantically equivelant, they can still be stylistically quite different.  For example, the same information
+
+Although two utternaces might be semantically equivelant, they can still be stylistically quite different.  For example, the same information
 is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.
+
+Systems capable of paraphrasing text targeting to a specific writing style could be useful for a variety of applications.  For example, they could:
+\begin{enumerate}
+  \item Help authors of technical documents to adhere to appropriate stylistic guidelines.  
+  \item Enable average people to better understand information in legal documents by translating ``leaglese'' into ordinary English.  
+  \item Benefit educational applications:
+    \begin{enumerate}
+    \item Students studying a specific style of writing may benefit from access to \emph{modern english} versions of works by authors they are studying.
+    \item Automatic paraphrases could help students to experiment with writing in the style of the authors whose works they are reading.
+    \end{enumerate}
+\end{enumerate}
 
@@
 evaluation metrics to capture the notion of writing style.  
-We propose several new metrics for evaluating paraphrases targeting a specific writing style, and measure correlation with human judgements showing  promising
+We show that previously proposed automatic evaluation metrics do not give us a complete picture of a system's performance when the task is to generate paraphrases
+targeting a specific style of writing.  We propose several new metrics for evaluating paraphrases targeting a specific style, and measure correlation with human judgements showing promising
 preliminary results.
 
-Systems which are capable of automatically paraphrasing literary writing styles could be directly benefical for educational applications.
-For example, a system which generates paraphrases targeting a specific style
-of writing could help students to experiment with writing literature in that style.
-In addition, out of the 37 surviving plays written by William Shakespeare only 17 currently have modern translations available.  Though we have not yet formally evaluated
-paraphrasing Shakespeare's plays into modern English, we believe it should be possible to make the other 20 plays more accessable to students of Shakespeare by automatically 
-generating high-quality modern translations.
-
-\begin{comment}
-\begin{itemize}
-  \item Define what we mean by writing styles.
-  \item Define the paraphrasing task and describe previous work.
-  \item Motivate the need for paraphrasing targeting a specific writing style (e.g. students of literature in a specific style, or helping people to understand documents written in an esoteric style).
-   \begin{itemize}
-     \item Mention several domains where paraphrasing into/out of a specific writing style could be beneficial (e.g. technical manuals, legal documents, etc...)
-   \end{itemize}
-  \item Summarize the main contributions.
-\end{itemize}
-\end{comment}
+Systems which are capable of automatically paraphrasing literary writing styles could be directly benefical for educational applications.  For example, our systems which generate paraphrases targeting
+a Shakesperean English could help students to experiment with writing literature in this style.
+In addition, out of the 37 surviving plays written by William Shakespeare modern translations are currently only available for 17.  Though we have not yet formally evaluated
+paraphrasing Shakespeare's plays into modern English, we believe it should be possible to help make the other 20 plays more accessable to students of Shakespeare by automatically 
+generating modern translations.
 
@@
 
-After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence \cite{Moore02} aligner, which produced about 21,079 alignments out of 31,718 sentences in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the enotes data.
+After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence aligner \cite{Moore02}, which produced about 21,079 alignments out of 31,718 sentences in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the enotes data.
 The modern translations from each source are qualitatively quite
@@
 To illustrate these differences empirically and provide an initial paraphrase baseline, we computed BLEU scores of the unchanged modern translations against Shakespeare's 
-original text; the Sparknotes paraphrases result in a BLEU score of 24.67, whereas the Enotes paraphrases prouce a much higher BLEU of 52.30 indicating their similarity to the original text.
+original text; the Sparknotes paraphrases result in a BLEU score of 24.67, whereas the Enotes paraphrases prouce a much higher BLEU of 52.30 indicating their strong similarity to the original plays.
 These corpus statistics are summarized in table \ref{corpus_stats}.
@@
 
-We apply a typical phrase-based Statistical Machine Translation pipeline, performing
+To generate paraphrases, we apply a typical phrase-based Statistical Machine Translation pipeline, performing
 word alignment on the data described in table \ref{corpus_stats} using GIZA++ \cite{Och03}, then extracting phrase pairs and performing decoding using Moses \cite{Koehn07}.
@@
 This method allows us to estimate reasonable translation probabilities for use in a phrase table, which is used in combination 
-with a language model consisting of Shakespeare's 36 plays (holding out Romeo and Juliet), which are then be fed into the Moses decoder
+with a language model consisting of Shakespeare's 36 plays (holding out Romeo and Juliet), which are then fed into the Moses decoder
 \cite{Koehn07}.
@@
 \cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of doimain parallel text, with an in-domain
-language model consisting of Shakespeare's 37 plays.  Although this monolingual parallel data does not include text in the target writing style,
-the in-domain language model does bias the generated sentences towards Shakespeare's writing style.
+language model consisting of Shakespeare's 36 plays (holding out Romeo and Juliet for testing), applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
+Although this monolingual parallel data does not include text in the target writing style,
+the in-domain language model does bias the system's output towards Shakespeare's style of writing.
 
 \subsection{Comparison Using Existing Automatic Evaluation Metrics}
-Figure \ref{bleupinc} compares a variety of sytstems targeting Shakesperean English using previously the previosly proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics.
-A summary of each system is presented in table \ref{systems}.
-Notice that the enotes data is quite similar to the original translations,
-obtaining a BLEU score of 52.3 when compared against the original text.  Our goal is to produce paraphrases which make many changes to the input, therefore
+Figure \ref{bleupinc} compares a variety of sytstems targeting Shakesperean English using the previosly proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics which
+have been demonstrated to correlate with human judgements on semantic adequacy and lexical dissimilarity with the input.
+A description of each of the systems compared in this experiment is presented in table \ref{systems}.  Notice that the Enotes paraphrases are quite similar to the original text,
+obtaining a BLEU score of 52.3 when compared directly to the original lines from Shakespeare's plays.
+Because our goal is to produce paraphrases which make more dramatic stylistic changes to the input,
 in the remainder of this paper, we focus on the Sparknotes data for evaluation.
 
-Two main trends emerge from figure \ref{bleupinc}.  First, notice that all of the systems which are trained using parallel text achieve higher BLEU scores than the baseline
-of not making any changes to the modern translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making significant changes to the 
-input, it's BLEU is lower than the \emph{no changes} baseline.  Secondly, it seems apparent that the systems whose parameters are learned using Minimum Error Rate training
-tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, but not seeing any BLEU improvements on the test data.  Finally
+\subsubsection{Discussion}
+Two main trends emerge from Figure \ref{bleupinc}.  First, notice that all of the systems which are trained using parallel text achieve higher BLEU scores than the baseline
+of not making any changes to the modern translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making a significant number of changes to the 
+input, it's BLEU is lower than the \emph{no changes} baseline.  Secondly, it seems apparent that the systems whose parameters are learned using Minimum Error Rate Training \cite{MERT}
+tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, however also not seeing any BLEU improvements on the test data.  Finally
 we note that using the larger language model seems to yield a slight improvement in BLEU score.
+
+\subsection{Examples}
+Several example paraphrases of lines from Romeo and Juliet and a few Hollywood movies, generated by the top performing system according to BLEU and PINC, are presented in table \ref{examples}.
 
@@
 
-Several example paraphrases generated by our system, both from Romeo and Juliet and several Hollywood movies are presented in table \ref{examples}.
-
 \section{Human Evaluation}
@@
 a Shakesperean language model has the highest semantic adequacy, however it is also fairly conservative making few changes to the input.
-The dictionary baseline, and system trained on parallel modern translations make a roughly comparable number of changes to the input
-sentences, but the system trained on modern translations achieves higher semantic adequacy, while being rated higher on style and overall.
 
-These results seem roughly in line with the automatic evalution metrics presented in figure \ref{bleupinc}, however with several important
-differences.  Although the video baseline achieves the highest semantic adequacy in the human evaluation, it's BLEU score
+The dictionary baseline, and paraphrase system trained on parallel modern translations are roughly comparable when it comes to 
+the number of changes made to the input, however the system trained on modern translations achieves higher semantic adequacy, while also being rated higher on style and overall.
+
+These results are roughly in line with the automatic evalution metrics presented in figure \ref{bleupinc}, however we see several important
+trends which are not aparent based on the automatic evaluation metrics.
+
+Although the video baseline achieves the highest semantic adequacy in the human evaluation, it's BLEU score
 is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
@@
 It would appear that in this case BLEU is conflating semantic adequecy with writing style.  Although the paraphrases produced 
-by the video baseline have high semantic adequacy, their style tends to differ from the reference translations resulting
+by the video baseline have high semantic adequacy, their style tends to differ substantially from the reference translations resulting
 in fewer ngram matches, and thus a lower BLEU score.
@@
 While PINC and BLEU do seem useful for automatically evaluating paraphrases targeting a  writing style, BLEU tends to conflate the notions of
-semantic adequacy with writing style.  When comparing various systems using automatic metrics, however, it would seem useful
-to seperate these two critera.  It would seem desirable for our automatic evaluation metrics to be able to distinguish
+semantic adequacy with writing style.  When comparing various systems using automatic metrics, it would seem useful
+to seperate effects based on these two critera.  We would like our automatic evaluation metrics to be able to distinguish
 between a system which generates perfect paraphrases which don't match the target style of writing and a system which
@@
 We present a preliminary evalutation of these metrics by measuring their correlation with human judgements, however
-we emphasize that here we are only evaluating these metrics with respect to one specific writing style.  We
-are cautionsly optimistic that these results will generalize across writing styles, however, as they are based entirely
+we emphasize that we are only evaluating these metrics with respect to one specific style of writing.  We
+are cautionsly optimistic that our results will generalize across writing styles, however, as they are based entirely
 on ngram statistics.
@@
 \subsection{Logistic Regression Style Metric}
-We also consider a Logistic Regression based approach as an alternative to evaluating writing style.  The idea here, is to estimate the probability that each
-sentence belongs to the target style, by using a large source and target training corpus to learn the parameters of a logistic regression model.
-This probability is estimated as follows:
+We also consider a Logistic Regression based approach as an alternative to the Cosine-Similarity based style metric.  Here the idea is to estimate the probability that each
+sentence belongs to the target style based on the ngrams it contains, using large corpora of in and out-of domain sentences to learn  parameters of a logistic regression model.
+
+The probability a sentence belongs to the target style is estimated as follows:
 \[
@@
 Where $\vec{f(\text{sentence})}$ is a vector of ngrams, and $\vec{\theta}$ is a vector of weights.
+
 The parameters, $\vec{\theta}$, are optimized on the source and target corpus, where the assumption is that the target corpus
@@
 As can be seen in table \ref{correlation}, the correlation between semantic adequacy and BLEU appears smaller than that reported in previous work \cite{chen11}.  Presumably this is
-due to the conflation of stylistic differences and semantic adequacy discussed discussed in section \ref{human_evaluation}, however the correlation between BLEU and human style
-judgements seems too low to be of practical use.  PINC has very high correlation with judgments on dissimilarity, however we note that it is also highly correlated with human style
-judgements.  To understand why PINC is highly correlated with human style judgements, notice that because the systems we are evaluating are targeting Shakesperean English, when changes
-are made to the input they are likely to be in the target style.  Although PINC has high correlation with human judgements, it is likely not a useful measure of style in practice,
-because for example a paraphrase system which makes many changes to the input, but targets a completely different style will also get a high PINC score.  
-Both the Cosine and Maximum Entropy style metrics achieve the highest overall correlation with human writing style judgements, with the Maximum Entropy score performing significantly better.
+due to the conflation of stylistic differences and semantic adequacy discussed discussed in section \ref{human_evaluation}, however it also appears 
+that the correlation between BLEU and human style judgements is too low to be of practical use for evaluating style.
 
-Finally we note that overall the average automatc metrics seem to agree with agree with human judgements as displayed in figure \ref{style_metrics}.
+PINC, on the other hand has high correlation with judgments on dissimilarity, and is also moderately correlated with human style
+judgements.  We believe PINC has some correlation with writing style, because the systems we are evaluating all target Shakesperean English, 
+so whenever changes are made to the input, they are likely to make it similar to the target style.
+Although PINC has relatively high correlation with human judgements, it is likely not a very useful measure of writing style in practice.
+For example, consider a paraphrase system which makes many changes to the input and thus gets a high PINC score, but targets a completely different writing style.
+
+Both the Cosine and Maximum Entropy style metrics achieve the highest overall correlation with human writing style judgements, with the Maximum Entropy style score performing significantly better.
+
+Finally we note that overall the automatc metrics tend to agree with agree with human judgements as displayed in figure \ref{style_metrics}.
 
@@
 Although no previous work has investigated paraphrasing modern text into Shakesperean English, or the more general task of paraphrasing while targeting a specific writing
-style, there are several strands of related work.
+style, we highlight several strands of related work.
 
-Perhaps most relevant is recent work generating and translating rhythmic poetry \cite{Greene10}.  This work focused on generating text in an appropriate
-meter (e.g. iambic pentameter) using finate-state transducers.  In contrast our work does not address the issue of meter, however it should be possible to combine our translation
-models with their weighted FSTs to produce Shakesperean paraphrase models which produce output in an appropriate meter.
+Perhaps most relevant is recent work generating and translating rhythmic poetry \cite{Greene10}.  This work focuses on automatically generating text in an appropriate
+meter (e.g. iambic pentameter) using finate-state transducers, however doesn't address the issue of paraphrase.  
+While our work does not address the issue of meter, it should be possible to combine our translation
+models with their weighted Finate State Transducers to produce Shakesperean paraphrase models which produce output in an appropriate meter.
 
@@
 In addition several authors have previously proposed
-automatic paraphrase evaluation metrics \cite{chen11,Callison-Burch08b,Bangalore00,liu10}.
+automatic paraphrase evaluation metrics \cite{chen11,Callison-Burch08b,Bangalore00,liu10} for paraphrase.
 We are not aware, however, of any previous work that has addressed the task of generating or evaluating
@@
 Finally we highlight related work on authorship classification which can be seen as detecting a specific style of writing \cite{Gamon04,Raghavan10}.
-This work has not specifically addressed the task of automatically generating or evaluating paraphrases in a specific style, however.
+This work has not specifically addressed the task of automatically generating or evaluating paraphrases in a specific style.
 

### 2012-08-27 paper/paper.tex
spell checked

@@
 
-Although two utternaces might be semantically equivelant, they can still be stylistically quite different.  For example, the same information
+Although two utterances might be semantically equivalent, they can still be stylistically quite different.  For example, the same information
 is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.
@@
   \item Help authors of technical documents to adhere to appropriate stylistic guidelines.  
-  \item Enable average people to better understand information in legal documents by translating ``leaglese'' into ordinary English.  
+  \item Enable average people to better understand information in legal documents by translating ``legalese'' into ordinary English.  
   \item Benefit educational applications:
     \begin{enumerate}
-    \item Students studying a specific style of writing may benefit from access to \emph{modern english} versions of works by authors they are studying.
+    \item Students studying a specific style of writing may benefit from access to \emph{modern English} versions of works by authors they are studying.
     \item Automatic paraphrases could help students to experiment with writing in the style of the authors whose works they are reading.
@@
 We exploit modern translations of 17 plays written to help students better understand Shakespeare's work.  A parallel corpus is extracted from these modern translations,
-which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakesperean English.  In addition we develop several
-baseline systems which do not make use of this source of parallel text and instead rely on manually compiled dictionaries of expressions commonly found in Shakesperean english, or out of
+which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakespearean English.  In addition we develop several
+baseline systems which do not make use of this source of parallel text and instead rely on manually compiled dictionaries of expressions commonly found in Shakespearean English, or out of
 domain parallel monolingual text gathered through Amazon's Mechanical Turk \cite{chen11}.
 
-We evaluate these models both through human judgements and standard evaluation metrics from the Machine Translation and paraphrase literature, however no previous work has investigated the ability of automatic
+We evaluate these models both through human judgments and standard evaluation metrics from the Machine Translation and paraphrase literature, however no previous work has investigated the ability of automatic
 evaluation metrics to capture the notion of writing style.  
 We show that previously proposed automatic evaluation metrics do not give us a complete picture of a system's performance when the task is to generate paraphrases
-targeting a specific style of writing.  We propose several new metrics for evaluating paraphrases targeting a specific style, and measure correlation with human judgements showing promising
+targeting a specific style of writing.  We propose several new metrics for evaluating paraphrases targeting a specific style, and measure correlation with human judgments showing promising
 preliminary results.
 
-Systems which are capable of automatically paraphrasing literary writing styles could be directly benefical for educational applications.  For example, our systems which generate paraphrases targeting
-a Shakesperean English could help students to experiment with writing literature in this style.
+Systems which are capable of automatically paraphrasing literary writing styles could be directly beneficial for educational applications.
+For example, our systems which generate paraphrases targeting
+a Shakespearean English could help students to experiment with writing literature in this style.
 In addition, out of the 37 surviving plays written by William Shakespeare modern translations are currently only available for 17.  Though we have not yet formally evaluated
-paraphrasing Shakespeare's plays into modern English, we believe it should be possible to help make the other 20 plays more accessable to students of Shakespeare by automatically 
+paraphrasing Shakespeare's plays into modern English, we believe it should be possible to help make the other 20 plays more accessible to students of Shakespeare by automatically 
 generating modern translations.
 
-\section{Shakesperean Paraphrasing}
+\section{Shakespearean Paraphrasing}
 We propose to use Shakespeare's plays as a testbed for the task of paraphrasing while targeting a specific writing style.  Because these plays are some of the
 highest regarded examples of English literature and are also very unique in style, many linguistic resources are available such as parallel corpora
-of modern translations and dictionaries of stylistically representative words and their modern equivelants.
+of modern translations and dictionaries of stylistically representative words and their modern equivalents.
 
-We compare 3 different stylisitic paraphrase systems targeting Shakesperean English.  One which leverages parallel corpora of modern translations, another which makes use
-of dictionaries of styalistically representative expressions, and another which leverages out-of-domain monolingual parallel data.
+We compare 3 different stylistic paraphrase systems targeting Shakespearean English.  One which leverages parallel corpora of modern translations, another which makes use
+of dictionaries of stylistically representative expressions, and another which leverages out-of-domain monolingual parallel data.
 
@@
 
-After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence aligner \cite{Moore02}, which produced about 21,079 alignments out of 31,718 sentences in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the enotes data.
+After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence aligner \cite{Moore02}, which produced about 21,079 alignments out of 31,718 sentences in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the Enotes data.
 The modern translations from each source are qualitatively quite
-different.  The Sparknotes paraphrases tend to differ significantly from the original text, whereas the enotes translations are much more conservative, making fewer changes.
+different.  The Sparknotes paraphrases tend to differ significantly from the original text, whereas the Enotes translations are much more conservative, making fewer changes.
 To illustrate these differences empirically and provide an initial paraphrase baseline, we computed BLEU scores of the unchanged modern translations against Shakespeare's 
-original text; the Sparknotes paraphrases result in a BLEU score of 24.67, whereas the Enotes paraphrases prouce a much higher BLEU of 52.30 indicating their strong similarity to the original plays.
+original text; the Sparknotes paraphrases result in a BLEU score of 24.67, whereas the Enotes paraphrases produce a much higher BLEU of 52.30 indicating their strong similarity to the original plays.
 These corpus statistics are summarized in table \ref{corpus_stats}.
@@
 \subsection{Baselines}
-Phrase-based translation has been demonstrated to be an effective approach to generating paraphrses \cite{chen11,quirk04}, however this approach does require the existence of
+Phrase-based translation has been demonstrated to be an effective approach to generating paraphrases \cite{chen11,quirk04}, however this approach does require the existence of
 parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches.
@@
 \label{dictionary_baseline}
-Several dictionaries of stylistically representative words of Shakesperean English and their modern equivelants are available on the web.  These dictionaries can be used 
+Several dictionaries of stylistically representative words of Shakespearean English and their modern equivalents are available on the web.  These dictionaries can be used 
 to define a translation model which is used in combination with a language model as in standard phrase-based MT \cite{Koehn00}.
@@
 As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
-\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of doimain parallel text, with an in-domain
+\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of domain parallel text, with an in-domain
 language model consisting of Shakespeare's 36 plays (holding out Romeo and Juliet for testing), applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
@@
 \subsection{Comparison Using Existing Automatic Evaluation Metrics}
-Figure \ref{bleupinc} compares a variety of sytstems targeting Shakesperean English using the previosly proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics which
-have been demonstrated to correlate with human judgements on semantic adequacy and lexical dissimilarity with the input.
+Figure \ref{bleupinc} compares a variety of systems targeting Shakespearean English using the previously proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics which
+have been demonstrated to correlate with human judgments on semantic adequacy and lexical dissimilarity with the input.
 A description of each of the systems compared in this experiment is presented in table \ref{systems}.  Notice that the Enotes paraphrases are quite similar to the original text,
@@
       \hline
-      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakesperean language model. a\\
+      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakespearean language model. a\\
       \hline
@@
   \end{center}
-  \caption{Descriptions of various systems for Shakesperean Paraphrase.  Romeo and Juliet is held out for testing.}
+  \caption{Descriptions of various systems for Shakespearean Paraphrase.  Romeo and Juliet is held out for testing.}
   \label{systems}
@@
   \end{center}
-  \caption{Various Shakesperean Paraphrase systems compared using BLEU and PINC.  A brief description of each system is presented in table \ref{systems}.}
+  \caption{Various Shakespearean Paraphrase systems compared using BLEU and PINC.  A brief description of each system is presented in table \ref{systems}.}
   \label{bleupinc}
@@
   \end{center}
-  \caption{Example Shakesperean paraphrases generated by the best overall system.}
+  \caption{Example Shakespearean paraphrases generated by the best overall system.}
   \label{examples}
@@
 \label{human_evaluation}
-Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is innitially unclear how well the BLEU and PINC
+Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is initially unclear how well the BLEU and PINC
 automatic evaluation metrics perform when applied to evaluating paraphrases targeting a specific style of writing.  BLEU and PINC have previously
-been shown to have high correlation with human judgements of semantic adequacy and lexical dissimilarity of paraphrase candidates, however no
+been shown to have high correlation with human judgments of semantic adequacy and lexical dissimilarity of paraphrase candidates, however no
 previous work has evaluated automatically generated paraphrases which target a specific style of writing \cite{chen11}.
@@
 are more likely to contain overlapping ngrams if they are both semantically and stylistically similar.  What BLEU doesn't tell us, however
-is what portion of it's improvements are due to stylistic similarity or semantic equivelance.  For this reason, we were motivated perform
-an evaluation based on human judgements of semantic adequacy, lexical dissimilarity and stylistic similarity.
+is what portion of it's improvements are due to stylistic similarity or semantic equivalence.  For this reason, we were motivated perform
+an evaluation based on human judgments of semantic adequacy, lexical dissimilarity and stylistic similarity.
 
-For this purpose, we randomly sampled 100 lines from Romeo and Juliet, then two of the authors annotated each sentence and it's Shakesperean
-translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overal quality.
+For this purpose, we randomly sampled 100 lines from Romeo and Juliet, then two of the authors annotated each sentence and it's Shakespearean
+translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality.
 The aggregate results of the human evaluation are displayed in figure \ref{human_judgements}.  Agreement between annotators
@@
 
-Based on the human evaluation, it appears that the baseline combining paraphrases collected from mechanical turk \cite{chen11} with
-a Shakesperean language model has the highest semantic adequacy, however it is also fairly conservative making few changes to the input.
+Based on the human evaluation, it appears that the baseline combining paraphrases collected from mechanical Turk \cite{chen11} with
+a Shakespearean language model has the highest semantic adequacy, however it is also fairly conservative making few changes to the input.
 
@@
 
-These results are roughly in line with the automatic evalution metrics presented in figure \ref{bleupinc}, however we see several important
-trends which are not aparent based on the automatic evaluation metrics.
+These results are roughly in line with the automatic evaluation metrics presented in figure \ref{bleupinc}, however we see several important
+trends which are not apparent based on the automatic evaluation metrics.
 
@@
 to be slightly different in style.}
-It would appear that in this case BLEU is conflating semantic adequecy with writing style.  Although the paraphrases produced 
+It would appear that in this case BLEU is conflating semantic adequacy with writing style.  Although the paraphrases produced 
 by the video baseline have high semantic adequacy, their style tends to differ substantially from the reference translations resulting
@@
   \end{center}
-  \caption{Average human judgements evaluating semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality
-    of Shakesperean paraphrase systems} 
+  \caption{Average human judgments evaluating semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality
+    of Shakespearean paraphrase systems} 
   \label{human_judgements}
@@
 semantic adequacy with writing style.  When comparing various systems using automatic metrics, it would seem useful
-to seperate effects based on these two critera.  We would like our automatic evaluation metrics to be able to distinguish
+to separate effects based on these two criteria.  We would like our automatic evaluation metrics to be able to distinguish
 between a system which generates perfect paraphrases which don't match the target style of writing and a system which
@@
 
-To help address this issue we propse two new automatic evaluation metrics whose goal is to measure the degree to which
-autoamtic paraphrases match the target style.  Both metrics assume existence of large corpora in both the source and
-target style, but do not require access to any parallel text, or human judgements.
+To help address this issue we propose two new automatic evaluation metrics whose goal is to measure the degree to which
+automatic paraphrases match the target style.  Both metrics assume existence of large corpora in both the source and
+target style, but do not require access to any parallel text, or human judgments.
 
-We present a preliminary evalutation of these metrics by measuring their correlation with human judgements, however
+We present a preliminary evaluation of these metrics by measuring their correlation with human judgments, however
 we emphasize that we are only evaluating these metrics with respect to one specific style of writing.  We
-are cautionsly optimistic that our results will generalize across writing styles, however, as they are based entirely
+are cautiously optimistic that our results will generalize across writing styles, however, as they are based entirely
 on ngram statistics.
@@
 We trained both Logistic Regression and Cosine Similarity evaluation metrics using the original Shakespeare plays and modern translations as
-the source and target corpus respectively (holding out Romeo and Juliet), then measured Pearson's Correlation Coefficent between the automatic
-evaluation metrics and human judgements reported in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.
+the source and target corpus respectively (holding out Romeo and Juliet), then measured Pearson's Correlation Coefficient between the automatic
+evaluation metrics and human judgments reported in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.
 
@@
   \end{center}
-  \caption{Correlation between various human judgements and automatic evaluation metrics}
+  \caption{Correlation between various human judgments and automatic evaluation metrics}
   \label{correlation}
@@
 due to the conflation of stylistic differences and semantic adequacy discussed discussed in section \ref{human_evaluation}, however it also appears 
-that the correlation between BLEU and human style judgements is too low to be of practical use for evaluating style.
+that the correlation between BLEU and human style judgments is too low to be of practical use for evaluating style.
 
 PINC, on the other hand has high correlation with judgments on dissimilarity, and is also moderately correlated with human style
-judgements.  We believe PINC has some correlation with writing style, because the systems we are evaluating all target Shakesperean English, 
+judgments.  We believe PINC has some correlation with writing style, because the systems we are evaluating all target Shakespearean English, 
 so whenever changes are made to the input, they are likely to make it similar to the target style.
-Although PINC has relatively high correlation with human judgements, it is likely not a very useful measure of writing style in practice.
+Although PINC has relatively high correlation with human judgments, it is likely not a very useful measure of writing style in practice.
 For example, consider a paraphrase system which makes many changes to the input and thus gets a high PINC score, but targets a completely different writing style.
 
-Both the Cosine and Maximum Entropy style metrics achieve the highest overall correlation with human writing style judgements, with the Maximum Entropy style score performing significantly better.
+Both the Cosine and Maximum Entropy style metrics achieve the highest overall correlation with human writing style judgments, with the Maximum Entropy style score performing significantly better.
 
-Finally we note that overall the automatc metrics tend to agree with agree with human judgements as displayed in figure \ref{style_metrics}.
+Finally we note that overall the automatic metrics tend to agree with agree with human judgments as displayed in figure \ref{style_metrics}.
 
@@
     \end{center}
-    \caption{Overall results from comparing automatic style metrics.  Note that the automatic metrics agree with results from human judgements in figure \ref{human_judgements}.}
+    \caption{Overall results from comparing automatic style metrics.  Note that the automatic metrics agree with results from human judgments in figure \ref{human_judgements}.}
     \label{style_metrics}
@@
 \section{Related Work}
-Although no previous work has investigated paraphrasing modern text into Shakesperean English, or the more general task of paraphrasing while targeting a specific writing
+Although no previous work has investigated paraphrasing modern text into Shakespearean English, or the more general task of paraphrasing while targeting a specific writing
 style, we highlight several strands of related work.
@@
 Perhaps most relevant is recent work generating and translating rhythmic poetry \cite{Greene10}.  This work focuses on automatically generating text in an appropriate
-meter (e.g. iambic pentameter) using finate-state transducers, however doesn't address the issue of paraphrase.  
+meter (e.g. iambic pentameter) using finite-state transducers, however doesn't address the issue of paraphrase.  
 While our work does not address the issue of meter, it should be possible to combine our translation
-models with their weighted Finate State Transducers to produce Shakesperean paraphrase models which produce output in an appropriate meter.
+models with their weighted Finite State Transducers to produce Shakespearean paraphrase models which produce output in an appropriate meter.
 
@@
 \section{Conclusions}
-We have presented initial investigation into the task of automatic paraphrasing while targeting a specific style of writing.  We proposed Shakespere's plays and their
-modern translations as a tesbed for this task, and developed a series of paraphrase systems targeting Shakesperean English.  We showed that while existing evaluation
-metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivelance with writing style giving an incomplete picture of which systems
-perform better according to each of these critera.
+We have presented initial investigation into the task of automatic paraphrasing while targeting a specific style of writing.  We proposed Shakespeare's plays and their
+modern translations as a tesbed for this task, and developed a series of paraphrase systems targeting Shakespearean English.  We showed that while existing evaluation
+metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivalence with writing style giving an incomplete picture of which systems
+perform better according to each of these criteria.
 
 To address the problems we have demonstrated with previous evaluation metrics applied to this task, we have introduced two new metrics for evaluating writing style.
-We measured correlation between automatic metrics and human judgements in the context of paraphrasing writing style, and showed
-that our new metrics have better correlation with human judgements than existing metrics in the context of our data.
+We measured correlation between automatic metrics and human judgments in the context of paraphrasing writing style, and showed
+that our new metrics have better correlation with human judgments than existing metrics in the context of our data.
 While this evaluation is limited to one specific style of writing, we are optimistic that these or similar metrics will also perform well when
@@
 
-Future work could include automatically translating the remaining 20 of Shakespeare's plays into modern English, which could be benefical to students
-of Shakespere's plays and also to future human translators.
+Future work could include automatically translating the remaining 20 of Shakespeare's plays into modern English, which could be beneficial to students
+of Shakespeare's plays and also to future human translators.
 

### 2012-08-28 python/style_metric.py
added output from systems translating to modern english

@@ -105,7 +105,18 @@ class StyleMetric:
 
 if __name__ == "__main__":
     sm = StyleMetric(sys.argv[1], sys.argv[2])
-    print sm.ScoreSim("Give yourself to the dark side")
-    print sm.ScoreMaxEnt("Give yourself to the dark side")
-    print sm.ScoreSim("Give thee to the dark side")
-    print sm.ScoreMaxEnt("Give thee to the dark side")
+
+    simSum = 0.0
+    meSum  = 0.0
+    nLines = 0.0
+    for line in open(sys.argv[3]):
+        line = line.strip()
+        simScore    = sm.ScoreSim(line)
+        maxEntScore = sm.ScoreMaxEnt(line)
+        print "%s\t%s\t%s" % (line, simScore, maxEntScore)
+        simSum += simScore
+        meSum  += maxEntScore
+        nLines += 1.0
+
+print "average simScore = %s" % simSum / nLines 
+print "average meScore  = %s" % meSum  / nLines 

### 2012-08-29 paper/paper.tex
minor gramatical fix
minor change..
added shakespeare -> modern section

@@
 
-Systems capable of paraphrasing text targeting to a specific writing style could be useful for a variety of applications.  For example, they could:
+Systems capable of paraphrasing text targeting a specific writing style could be useful for a variety of applications.  For example, they could:
 \begin{enumerate}
@@
 \subsection{Logistic Regression Style Metric}
-We also consider a Logistic Regression based approach as an alternative to the Cosine-Similarity based style metric.  Here the idea is to estimate the probability that each
+We also consider a Logistic Regression based approach as an alternative to cosine similarity.  Here the idea is to estimate the probability that each
 sentence belongs to the target style based on the ngrams it contains, using large corpora of in and out-of domain sentences to learn  parameters of a logistic regression model.
@@
 
+\section{Translating Shakespeare's Plays to Modern English}
+Finally we preform a preliminary evaluation of the task of automatically translating Shakespeare's plays into modern English.  Success at this task could have immediate
+benefits to students, as well as translators of Shakespeare's plays into modern English.
+
+For the purposes of this evaluation, 
+we make use of the same paraphrase systems previously described, but swap the source and target languages.
+Additionally, each system makes use of a language model constructed from the 16 modern translations, and again Romeo and Juliet are held out for testing.  
+510 lines from Romeo and Juliet were automatically translated into modern English using each system, and the aligned modern 
+translations were used as a reference when computing BLEU.  The results of evaluating each of the automatic evaluation metrics on this
+data are presented in figure \ref{shakespeare_to_modern_automatic}.
+
+The results suggest that modern translations generates more diverse paraphrases which better match the target style.  Note that the paraphrase system
+based on the out-of-domain video corpus makes very few changes to the input, and thus achieves a very low PINC score.  This is due to the many out of
+vocabulary words in Shakespeare's plays which result in very few matching source phrases in the video baseline's phrase table.
+
+While we have yet to perform a human evaluation on the task of paraphrasing Shakespeare's plays into modern English, 
+informal inspection of the resulting translations is encouraging.  Several automatic paraphrases into modern English are presented in Table \ref{modern_examples}.
+
+\begin{figure}
+  \includegraphics[width=5in]{figures/shakespeare_to_modern.pdf}
+  \caption{Automatic evaluation of paraphrasing Shakespeare's plays into modern english comparing a system based on parallel text (16plays\_16LM), 
+  a Dictionary baseline, and a system trained on out of domain parallel monolingual text.  Note that the video corpus baseline achieves low overal
+  PINC score, as few phrases in the input match phrases found in it's phrase table, resulting in a small number of changes to the input.}
+  \label{shakespeare_to_modern_automatic}
+\end{figure}
+
+\begin{table}
+  \begin{center}
+  \begin{tabular}{|l|p{1.8in}|p{1.8in}|}
+    \hline
+    Speaker & Input & Output \\
+    \hline
+    \hline
+    MERCUTIO & i will bite thee by the ear for that jest . & i ’ ll bite you by the ear for that joke . \\
+    \hline
+    MONTAGUE & what further woe conspires against mine age ? & what ’ s true despair conspires against my old age ? \\
+    \hline
+    ROMEO & how doth my lady ? & how is my lady ? \\
+    \hline
+    FRIAR LAURENCE & hast thou slain tybalt ? & have you killed tybalt ? \\
+    \hline
+    NURSE & an i might live to see thee married once , i have my wish . & if i could live to see you married , i ’ ve my wish . \\
+    \hline
+    PRINCE & benvolio , who began this bloody fray ? & benvolio , who started this bloody fight itself ? \\
+    \hline
+    JULIET & what is your will ? & what do you want ? \\
+    \hline
+    LADY CAPULET & call her forth to me . & bring her out to me . \\
+    \hline
+  \end{tabular}
+  \end{center}
+  \caption{Example modern paraphrases of lines from Romeo and Juliet generated using our system.}
+  \label{modern_examples}
+\end{table}
+
 \section{Related Work}

### 2012-08-29 python/style_metric.py

@@ -78,7 +78,7 @@ class StyleMetric:
                 sentence_vector[ngram] = sentence_vector.get(ngram, 0.0) + 1.0
         source_sim = self.CosineSim(sentence_vector, self.source_vector)
         target_sim = self.CosineSim(sentence_vector, self.target_vector)
-        return target_sim / (target_sim + source_sim)
+        return target_sim / (target_sim + source_sim + 0.001)
 
     def ScoreMaxEnt(self, sentence):
         sentence_vector = {}
@@ -109,14 +109,16 @@ if __name__ == "__main__":
     simSum = 0.0
     meSum  = 0.0
     nLines = 0.0
-    for line in open(sys.argv[3]):
-        line = line.strip()
-        simScore    = sm.ScoreSim(line)
-        maxEntScore = sm.ScoreMaxEnt(line)
-        print "%s\t%s\t%s" % (line, simScore, maxEntScore)
-        simSum += simScore
-        meSum  += maxEntScore
-        nLines += 1.0
 
-print "average simScore = %s" % simSum / nLines 
-print "average meScore  = %s" % meSum  / nLines 
+    for f in sys.argv[3].split(':'):
+        print f
+        for line in open(f):
+            line = line.strip()
+            simScore    = sm.ScoreSim(line)
+            maxEntScore = sm.ScoreMaxEnt(line)
+            print "%s\t%s\t%s" % (line, simScore, maxEntScore)
+            simSum += simScore
+            meSum  += maxEntScore
+            nLines += 1.0
+        print "average %s simScore = %s" % (f, str(simSum / nLines))
+        print "average %s meScore  = %s" % (f, str(meSum  / nLines))

### 2012-08-29 paper/paper.tex
some polishing..

@@
 a Shakespearean English could help students to experiment with writing literature in this style.
-In addition, out of the 37 surviving plays written by William Shakespeare modern translations are currently only available for 17.  Though we have not yet formally evaluated
-paraphrasing Shakespeare's plays into modern English, we believe it should be possible to help make the other 20 plays more accessible to students of Shakespeare by automatically 
-generating modern translations.
+In addition, out of the 37 surviving plays written by William Shakespeare, modern translations are currently only available for 17.  
+We therefore present initial investigation into the task of automatically translating Shakespeare's plays into modern English, using our automatic evaluation metrics.
+By automatically paraphrasing the remaining 20 plays into modern English, 
+we believe it should be possible to help make these plays more accessible to students of Shakespeare.
 
@@
 \subsection{Baselines}
-Phrase-based translation has been demonstrated to be an effective approach to generating paraphrases \cite{chen11,quirk04}, however this approach does require the existence of
-parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches.
+Phrase-based translation has been demonstrated as an effective approach to paraphrasing \cite{chen11,quirk04}, however this approach does require the existence of
+parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches in order to help
+quantify the benefit of access to parallel text in the source and target styles.
 
@@
 \label{dictionary_baseline}
-Several dictionaries of stylistically representative words of Shakespearean English and their modern equivalents are available on the web.  These dictionaries can be used 
-to define a translation model which is used in combination with a language model as in standard phrase-based MT \cite{Koehn00}.
+Several dictionaries of stylistically representative words of Shakespearean English and their modern equivalents are available on the web.  
+These dictionaries can be used to define a translation model which can be used in combination with a language model as in standard phrase-based Machine
+Translation.
 
@@
 
-We scraped a set of 68,709 phrase/word pairs from \url{http://www.shakespeareswords.com/}.  
-Example dictionary entries are presented in table \ref{dictionary_example}.
-
-%As described in \cite{Koehn00}, we estimate phrase translation probabilities based on the frequencies of the translation words/phrases in the target language - the Shakespearean English. 
-As described in \cite{Koehn00}, we estimate phrase translation probabilities based on the frequencies of the translation words/phrases in the target language (Shakespearean English).
+To build a phrase table, we scraped a set of 68,709 phrase/word pairs from \url{http://www.shakespeareswords.com/}; 
+example dictionary entries are presented in table \ref{dictionary_example}. 
+As described in \cite{Koehn00}, we estimate phrase translation probabilities
+based on the frequencies of the translation words/phrases in the target language (Shakespearean English).
 For instance, if we look at the modern English word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations. 
@@
 
-Finally we note that overall the automatic metrics tend to agree with agree with human judgments as displayed in figure \ref{style_metrics}.
+Finally we note that overall the automatic metrics tend to agree with agree with human judgments as displayed in figure \ref{style_metrics}.\footnote{
+  Although the automatic style metrics rate the dictionary system higher than the video corpus baseline, both systems have very comparable
+  style scores in both the automatic and human evaluations.
+}
 
@@
     \end{center}
-    \caption{Overall results from comparing automatic style metrics.  Note that the automatic metrics agree with results from human judgments in figure \ref{human_judgements}.}
+    \caption{Results comparing the 3 systems using the automatic style metrics.}
     \label{style_metrics}
@@
 
-Future work could include automatically translating the remaining 20 of Shakespeare's plays into modern English, which could be beneficial to students
-of Shakespeare's plays and also to future human translators.
+Finally, we applied these automatic evaluation metrics to an initial investigation into the task of translating Shakespeare's plays into modern English.
+We plan to translate the remaining 20 of Shakespeare's plays into modern English, which could be beneficial to students
+of Shakespeare's plays and also to human translators.
 

### 2012-08-29 paper/paper.tex
some proofreading

@@
 
-We evaluate these models both through human judgments and standard evaluation metrics from the Machine Translation and paraphrase literature, however no previous work has investigated the ability of automatic
+We evaluate these models both through human judgments and standard evaluation metrics from the Machine Translation and Paraphrase literature, however no previous work has investigated the ability of automatic
 evaluation metrics to capture the notion of writing style.  
-We show that previously proposed automatic evaluation metrics do not give us a complete picture of a system's performance when the task is to generate paraphrases
-targeting a specific style of writing.  We propose several new metrics for evaluating paraphrases targeting a specific style, and measure correlation with human judgments showing promising
+We show that previously proposed metrics do not provide the complete picture of a system's performance when the task is to generate paraphrases
+targeting a specific style of writing.  We propose two new metrics for evaluating paraphrases targeting a specific style, and measure correlation with human judgments showing promising
 preliminary results.
@@
 For example, our systems which generate paraphrases targeting
-a Shakespearean English could help students to experiment with writing literature in this style.
+Shakespearean English could help students to experiment with writing literature in this style.
 In addition, out of the 37 surviving plays written by William Shakespeare, modern translations are currently only available for 17.  
@@
 We compare 3 different stylistic paraphrase systems targeting Shakespearean English.  One which leverages parallel corpora of modern translations, another which makes use
-of dictionaries of stylistically representative expressions, and another which leverages out-of-domain monolingual parallel data.
+of dictionaries of stylistically representative expressions, and another which utilizes out-of-domain monolingual parallel data.
 
@@
 of not making any changes to the modern translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making a significant number of changes to the 
-input, it's BLEU is lower than the \emph{no changes} baseline.  Secondly, it seems apparent that the systems whose parameters are learned using Minimum Error Rate Training \cite{MERT}
+input, it's BLEU is lower than the \emph{no changes} baseline.  Secondly, it seems apparent that the systems whose parameters are tuned using Minimum Error Rate Training \cite{MERT}
 tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, however also not seeing any BLEU improvements on the test data.  Finally
@@
 
-\subsection{Examples}
-Several example paraphrases of lines from Romeo and Juliet and a few Hollywood movies, generated by the top performing system according to BLEU and PINC, are presented in table \ref{examples}.
-
-\begin{table}[ht]
+\begin{table}
   \begin{center}
@@
 \end{figure}
+
+\subsection{Examples}
+Several example paraphrases of lines from Romeo and Juliet and a few Hollywood movies, generated by the top performing system according to BLEU and PINC, are presented in table \ref{examples}.
 
@@
 been shown to have high correlation with human judgments of semantic adequacy and lexical dissimilarity of paraphrase candidates, however no
-previous work has evaluated automatically generated paraphrases which target a specific style of writing \cite{chen11}.
+previous work has evaluated automatically generated paraphrases which target a specific style of writing.
 
@@
 trends which are not apparent based on the automatic evaluation metrics.
-
 Although the video baseline achieves the highest semantic adequacy in the human evaluation, it's BLEU score
@@
 \subsection{Cosine Similarity Style Metric}
-As a first approach automatic evaluation of writing style, we propose a vector-space model of similarity between the system
+As a first approach to automatic evaluation of writing style, we propose a vector-space model of similarity between the system
 output and a large corpus of text in both the source and target style.  The intuition is that if there is a large ngram

### 2012-08-29 paper/paper.tex
a bit of proofreading, and added a few more examples

@@
 
-\subsubsection{Out of Domain Monolingual Parallel Data}
+\subsubsection{Out of Domain Monolingual Parallel Text}
 As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
@@
 the in-domain language model does bias the system's output towards Shakespeare's style of writing.
+We found that performing Minimum Error Rate Training using a small set of held out parallel text from Romeo and Juliet was necessary in order to tune the
+video corpus baseline to generate reasonable paraphrases.
 
@@
       \hline
+      Terminator 2 & Terminator & My mission is to protect you. & my affair is to keep you . \\
+      %\hline
+      %Terminator 2 & Terminator & Negative.
+The T-1000's highest probability for success now would be to copy Sarah Connor and to wait for you to make contact with her.
+& negative.
+the t-1000 's most exalted probability for success now would be to have sarah connor and to stay for you to make contact with her .
+\\
+      \hline
+      Terminator 2 & Terminator & Skynet begins to learn at a geometric rate.
+...
+In a panic, they try to pull the plug.
+& skynet begins to learn at a geometric rate.
+...
+in a fearful sails , they would pluck the stop .
+\\
+      \hline
     \end{tabular}
@@
 
-\begin{table}[ht]
+\begin{table}
   \begin{center}
@@
 semantic adequacy with writing style.  When comparing various systems using automatic metrics, it would seem useful
-to separate effects based on these two criteria.  We would like our automatic evaluation metrics to be able to distinguish
+to separate effects caused by these two distinct criteria.  We would like our automatic evaluation metrics to be able to distinguish
 between a system which generates perfect paraphrases which don't match the target style of writing and a system which
@@
 \subsection{Logistic Regression Style Metric}
-We also consider a Logistic Regression based approach as an alternative to cosine similarity.  Here the idea is to estimate the probability that each
+We also consider an approach to measuring style which is based on logistic regression as opposed to cosine similarity.
+%We also consider a logistic Regression based approach as an alternative to cosine similarity.
+Here the idea is to estimate the probability that each
 sentence belongs to the target style based on the ngrams it contains, using large corpora of in and out-of domain sentences to learn  parameters of a logistic regression model.
 
-The probability a sentence belongs to the target style is estimated as follows:
+The probability that a sentence belongs to the target style is estimated as follows:
 \[
@@
 \subsection{Evaluation}
-We trained both Logistic Regression and Cosine Similarity evaluation metrics using the original Shakespeare plays and modern translations as
+We trained both logistic regression and cosine similarity evaluation metrics using the original Shakespeare plays and modern translations as
 the source and target corpus respectively (holding out Romeo and Juliet), then measured Pearson's Correlation Coefficient between the automatic

### 2012-08-29 paper/paper.tex
more proofreading

@@
 In addition, out of the 37 surviving plays written by William Shakespeare, modern translations are currently only available for 17.  
-We therefore present initial investigation into the task of automatically translating Shakespeare's plays into modern English, using our automatic evaluation metrics.
-By automatically paraphrasing the remaining 20 plays into modern English, 
+We therefore present a preliminary investigation into the task of automatically translating Shakespeare's plays into modern English, using our newly developed
+automatic evaluation metrics.  By automatically paraphrasing the remaining 20 plays into modern English, 
 we believe it should be possible to help make these plays more accessible to students of Shakespeare.
@@
 \subsection{Modern Translations}
-Having access to parallel text in the target style allows us to train statistical models for generating paraphrases, and also perform automatic evaluation of semantic adequacy using BLEU, which requires access to a set of reference translations.
+Access to parallel text in the target style allows us to train statistical models to generate paraphrases, and also perform automatic evaluation of semantic adequacy using BLEU, which requires availability of reference translations.
 For this purpose we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}, and an additional 8 translations of overlapping plays from \url{http://enotes.com}, giving us two reference translations for 8 out of the 17 plays.
@@
 \subsection{Baselines}
-Phrase-based translation has been demonstrated as an effective approach to paraphrasing \cite{chen11,quirk04}, however this approach does require the existence of
+Phrase-based translation has been demonstrated as an effective approach to paraphrasing \cite{quirk04chen11}, however this approach does require the existence of
 parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches in order to help
@@
       \hline
-      Romeo \& Juliet & Benvolio & he killed your relative , brave mercutio , and then young romeo killed him . & he slew thy kinsman , brave mercutio , and then young romeo kill him . \\
+      Romeo \& Juliet & Benvolio & He killed your relative, brave Mercutio, and then young Romeo killed him. & he slew thy kinsman , brave mercutio , and then young romeo kill him . \\
       \hline
-      Romeo \& Juliet & Romeo & i can read my own fortune in my misery . & i can read mine own fortune in my woes . \\
+      Romeo \& Juliet & Romeo & I can read my own fortune in my misery. & i can read mine own fortune in my woes . \\
       \hline
@@
 
-These results are roughly in line with the automatic evaluation metrics presented in figure \ref{bleupinc}, however we see several important
-trends which are not apparent based on the automatic evaluation metrics.
+These results are roughly in line with the automatic evaluation metrics presented in figure \ref{bleupinc}, however we also see several important
+trends which are not apparent from the automatic evaluation metrics.
 Although the video baseline achieves the highest semantic adequacy in the human evaluation, it's BLEU score
@@
 As a first approach to automatic evaluation of writing style, we propose a vector-space model of similarity between the system
-output and a large corpus of text in both the source and target style.  The intuition is that if there is a large ngram
-overlap between the system's output and a large corpus of text in the target style, then the output is more likely to be
-stylistically appropriate.
+output and a large corpus of text in both the source and target style.  The intuition behind this metric is that  a large ngram
+overlap between the system's output and a corpus of text in the target style should indicate that the
+output is likely to be stylistically appropriate.
 
-More concretely, we extract ngrams from both the source and target corpus which are then represented as binary
+More concretely, we extract ngrams from both the source and target corpus which are represented as binary
 vectors $\vec{s}$, and $\vec{t}$; similarly the output sentence is represented using a vector of
@@
 Here the idea is to estimate the probability that each
-sentence belongs to the target style based on the ngrams it contains, using large corpora of in and out-of domain sentences to learn  parameters of a logistic regression model.
+sentence belongs to the target style based on the ngrams it contains, using large corpora of \emph{in domain} and \emph{out-of domain} sentences to learn  parameters of a logistic regression model.
 
@@
 \]
-Where $\vec{f(\text{sentence})}$ is a vector of ngrams, and $\vec{\theta}$ is a vector of weights.
+Where $\vec{f(\text{sentence})}$ is a vector of ngrams contained by the sentence, and $\vec{\theta}$ is a vector of weights corresponding to each possible ngram.
 
-The parameters, $\vec{\theta}$, are optimized on the source and target corpus, where the assumption is that the target corpus
+The parameters, $\vec{\theta}$, are optimized to maximize conditional likelihood on the source and target corpus, where the assumption is that the target corpus
 is in the target style, whereas the source corpus is not.\footnote{
@@
 \subsection{Evaluation}
-We trained both logistic regression and cosine similarity evaluation metrics using the original Shakespeare plays and modern translations as
+We trained both the logistic regression and cosine similarity evaluation metrics using the original Shakespeare plays and modern translations as
 the source and target corpus respectively (holding out Romeo and Juliet), then measured Pearson's Correlation Coefficient between the automatic
@@
   Although the automatic style metrics rate the dictionary system higher than the video corpus baseline, both systems have very comparable
-  style scores in both the automatic and human evaluations.
+  style scores in the automatic and human evaluations.
 }
@@
 
-The results suggest that modern translations generates more diverse paraphrases which better match the target style.  Note that the paraphrase system
+The results suggest that in comparison to the dictionary and video corpus baselines, 
+our system trained on modern translations generates diverse paraphrases which match the target style.
+Note that the paraphrase system 
 based on the out-of-domain video corpus makes very few changes to the input, and thus achieves a very low PINC score.  This is due to the many out of
@@
 
-Perhaps most relevant is recent work generating and translating rhythmic poetry \cite{Greene10}.  This work focuses on automatically generating text in an appropriate
-meter (e.g. iambic pentameter) using finite-state transducers, however doesn't address the issue of paraphrase.  
-While our work does not address the issue of meter, it should be possible to combine our translation
-models with their weighted Finite State Transducers to produce Shakespearean paraphrase models which produce output in an appropriate meter.
-
 Much previous work has addressed the task of automatically generating paraphrases \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05,Callison-Burch08,Kok10}.  
 In addition several authors have previously proposed 
-automatic paraphrase evaluation metrics \cite{chen11,Callison-Burch08b,Bangalore00,liu10} for paraphrase.
+automatic metrics specifically for evaluating paraphrases \cite{chen11,Callison-Burch08b,liu10}.
 We are not aware, however, of any previous work that has addressed the task of generating or evaluating
@@
 
+Perhaps most relevant, however, is recent work autoatic generation of rhythmic poetry \cite{Greene10}.  This work focuses on automatically generating and translating
+poetry in an appropriate meter (e.g. iambic pentameter) using finite-state transducers, however doesn't address the issue of paraphrase.  Their generation system
+is trained on Shakespeare's sonnets, and they investigate the task of automatically translating Dante's Divine Comedy from Italian to English.
+While our work does not address the issue of meter, it should be possible to combine our translation
+models with their weighted finite state transducers to produce Shakespearean paraphrase models which produce output in an appropriate meter.
+
 Finally we highlight related work on authorship classification which can be seen as detecting a specific style of writing \cite{Gamon04,Raghavan10}.
-This work has not specifically addressed the task of automatically generating or evaluating paraphrases in a specific style.
+This work has not specifically addressed the task of automatically generating or evaluating paraphrases in a specific style, however.
 
@@
 
-To address the problems we have demonstrated with previous evaluation metrics applied to this task, we have introduced two new metrics for evaluating writing style.
+To address this problem, we have introduced two new metrics for evaluating writing style.
 We measured correlation between automatic metrics and human judgments in the context of paraphrasing writing style, and showed
@@
 While this evaluation is limited to one specific style of writing, we are optimistic that these or similar metrics will also perform well when
-evaluating other writing styles.
+evaluating paraphrase systems targeting other writing styles.
 

### 2012-08-29 paper/paper.tex
some fixes

--- 2012-08-29 paper/paper.tex
@@
 
-Systems capable of paraphrasing text targeting a specific writing style could be useful for a variety of applications.  For example, they could:
+Systems capable of paraphrasing text targeting to a specific writing style could be useful for a variety of applications.  For example, they could:
 \begin{enumerate}
@@
 
-We evaluate these models both through human judgments and standard evaluation metrics from the Machine Translation and Paraphrase literature, however no previous work has investigated the ability of automatic
+We evaluate these models both through human judgments and standard evaluation metrics from the Machine Translation and paraphrase literature, however no previous work has investigated the ability of automatic
 evaluation metrics to capture the notion of writing style.  
-We show that previously proposed metrics do not provide the complete picture of a system's performance when the task is to generate paraphrases
-targeting a specific style of writing.  We propose two new metrics for evaluating paraphrases targeting a specific style, and measure correlation with human judgments showing promising
+We show that previously proposed automatic evaluation metrics do not give us a complete picture of a system's performance when the task is to generate paraphrases
+targeting a specific style of writing.  We propose several new metrics for evaluating paraphrases targeting a specific style, and measure correlation with human judgments showing promising
 preliminary results.
@@
 For example, our systems which generate paraphrases targeting
-Shakespearean English could help students to experiment with writing literature in this style.
-In addition, out of the 37 surviving plays written by William Shakespeare, modern translations are currently only available for 17.  
-We therefore present initial investigation into the task of automatically translating Shakespeare's plays into modern English, using our automatic evaluation metrics.
-By automatically paraphrasing the remaining 20 plays into modern English, 
-we believe it should be possible to help make these plays more accessible to students of Shakespeare.
+a Shakespearean English could help students to experiment with writing literature in this style.
+In addition, out of the 37 surviving plays written by William Shakespeare modern translations are currently only available for 17.  Though we have not yet formally evaluated
+paraphrasing Shakespeare's plays into modern English, we believe it should be possible to help make the other 20 plays more accessible to students of Shakespeare by automatically 
+generating modern translations.
 
@@
 We compare 3 different stylistic paraphrase systems targeting Shakespearean English.  One which leverages parallel corpora of modern translations, another which makes use
-of dictionaries of stylistically representative expressions, and another which utilizes out-of-domain monolingual parallel data.
+of dictionaries of stylistically representative expressions, and another which leverages out-of-domain monolingual parallel data.
 
@@
 \subsection{Baselines}
-Phrase-based translation has been demonstrated as an effective approach to paraphrasing \cite{chen11,quirk04}, however this approach does require the existence of
-parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches in order to help
-quantify the benefit of access to parallel text in the source and target styles.
+Phrase-based translation has been demonstrated to be an effective approach to generating paraphrases \cite{chen11,quirk04}, however this approach does require the existence of
+parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches.
 
@@
 \label{dictionary_baseline}
-Several dictionaries of stylistically representative words of Shakespearean English and their modern equivalents are available on the web.  
-These dictionaries can be used to define a translation model which can be used in combination with a language model as in standard phrase-based Machine
-Translation.
+Several dictionaries of stylistically representative words of Shakespearean English and their modern equivalents are available on the web.  These dictionaries can be used 
+to define a translation model which is used in combination with a language model as in standard phrase-based MT \cite{Koehn00}.
 
@@
 
-To build a phrase table, we scraped a set of 68,709 phrase/word pairs from \url{http://www.shakespeareswords.com/}; 
-example dictionary entries are presented in table \ref{dictionary_example}. 
-As described in \cite{Koehn00}, we estimate phrase translation probabilities
-based on the frequencies of the translation words/phrases in the target language (Shakespearean English).
+We scraped a set of 68,709 phrase/word pairs from \url{http://www.shakespeareswords.com/}.  
+Example dictionary entries are presented in table \ref{dictionary_example}.
+
+%As described in \cite{Koehn00}, we estimate phrase translation probabilities based on the frequencies of the translation words/phrases in the target language - the Shakespearean English. 
+As described in \cite{Koehn00}, we estimate phrase translation probabilities based on the frequencies of the translation words/phrases in the target language (Shakespearean English).
 For instance, if we look at the modern English word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations. 
@@
 This method allows us to estimate reasonable translation probabilities for use in a phrase table, which is used in combination 
-with a language model consisting of Shakespeare's 36 plays (holding out Romeo and Juliet), which are then fed into the Moses decoder
+with a language model consisting of Shakespeare's 36 plays (holding out {\em Romeo and Juliet}), which are then fed into the Moses decoder
 \cite{Koehn07}.
@@
 \subsubsection{Out of Domain Monolingual Parallel Data}
+\label{video_baseline}
 As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
 \cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of domain parallel text, with an in-domain
-language model consisting of Shakespeare's 36 plays (holding out Romeo and Juliet for testing), applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
+language model consisting of Shakespeare's 36 plays (holding out {\em Romeo and Juliet} for testing), applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
 Although this monolingual parallel data does not include text in the target writing style,
@@
 of not making any changes to the modern translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making a significant number of changes to the 
-input, it's BLEU is lower than the \emph{no changes} baseline.  Secondly, it seems apparent that the systems whose parameters are tuned using Minimum Error Rate Training \cite{MERT}
+input, it's BLEU is lower than the \emph{no changes} baseline.  Secondly, it seems apparent that the systems whose parameters are learned using Minimum Error Rate Training \cite{MERT}
 tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, however also not seeing any BLEU improvements on the test data.  Finally
@@
 
-\begin{table}
+\subsection{Examples}
+Several example paraphrases of lines from {\em Romeo and Juliet} and a few Hollywood movies, generated by the top performing system according to BLEU and PINC, are presented in table \ref{examples}.
+
+\begin{table}[ht]
   \begin{center}
@@
       \hline
-      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakespearean language model. a\\
+      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakespearean language model.\\
       \hline
       16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
+      \hline
+      video\_corpus\_baseline & Paraphrase system combining out of domain parallel text \cite{chen11} with an in-domain language model.  Described
+      in detail in section \ref{video_baseline}. \\
       \hline
@@
   \end{center}
-  \caption{Descriptions of various systems for Shakespearean Paraphrase.  Romeo and Juliet is held out for testing.}
+  \caption{Descriptions of various systems for Shakespearean Paraphrase.  {\em Romeo and Juliet} is held out for testing.}
   \label{systems}
@@
 \end{figure}
-
-\subsection{Examples}
-Several example paraphrases of lines from Romeo and Juliet and a few Hollywood movies, generated by the top performing system according to BLEU and PINC, are presented in table \ref{examples}.
 
@@
 been shown to have high correlation with human judgments of semantic adequacy and lexical dissimilarity of paraphrase candidates, however no
-previous work has evaluated automatically generated paraphrases which target a specific style of writing.
+previous work has evaluated automatically generated paraphrases which target a specific style of writing \cite{chen11}.
 
@@
 
-For this purpose, we randomly sampled 100 lines from Romeo and Juliet, then two of the authors annotated each sentence and it's Shakespearean
+For this purpose, we randomly sampled 100 lines from {\em Romeo and Juliet}, then two of the authors annotated each sentence and it's Shakespearean
 translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality.
@@
 trends which are not apparent based on the automatic evaluation metrics.
+
 Although the video baseline achieves the highest semantic adequacy in the human evaluation, it's BLEU score
@@
 \subsection{Cosine Similarity Style Metric}
-As a first approach to automatic evaluation of writing style, we propose a vector-space model of similarity between the system
+As a first approach automatic evaluation of writing style, we propose a vector-space model of similarity between the system
 output and a large corpus of text in both the source and target style.  The intuition is that if there is a large ngram
@@
 \subsection{Logistic Regression Style Metric}
-We also consider a Logistic Regression based approach as an alternative to cosine similarity.  Here the idea is to estimate the probability that each
+We also consider a Logistic Regression based approach as an alternative to the Cosine-Similarity based style metric.  Here the idea is to estimate the probability that each
 sentence belongs to the target style based on the ngrams it contains, using large corpora of in and out-of domain sentences to learn  parameters of a logistic regression model.
@@
 We trained both Logistic Regression and Cosine Similarity evaluation metrics using the original Shakespeare plays and modern translations as
-the source and target corpus respectively (holding out Romeo and Juliet), then measured Pearson's Correlation Coefficient between the automatic
+the source and target corpus respectively (holding out {\em Romeo and Juliet}), then measured Pearson's Correlation Coefficient between the automatic
 evaluation metrics and human judgments reported in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.
@@
 
-Finally we note that overall the automatic metrics tend to agree with agree with human judgments as displayed in figure \ref{style_metrics}.\footnote{
-  Although the automatic style metrics rate the dictionary system higher than the video corpus baseline, both systems have very comparable
-  style scores in both the automatic and human evaluations.
-}
+Finally we note that overall the automatic metrics tend to agree with agree with human judgments as displayed in figure \ref{style_metrics}.
 
@@
     \end{center}
-    \caption{Results comparing the 3 systems using the automatic style metrics.}
+    \caption{Overall results from comparing automatic style metrics.  Note that the automatic metrics agree with results from human judgments in figure \ref{human_judgements}.}
     \label{style_metrics}
 \end{figure}
-
-\section{Translating Shakespeare's Plays to Modern English}
-Finally we preform a preliminary evaluation of the task of automatically translating Shakespeare's plays into modern English.  Success at this task could have immediate
-benefits to students, as well as translators of Shakespeare's plays into modern English.
-
-For the purposes of this evaluation, 
-we make use of the same paraphrase systems previously described, but swap the source and target languages.
-Additionally, each system makes use of a language model constructed from the 16 modern translations, and again Romeo and Juliet are held out for testing.  
-510 lines from Romeo and Juliet were automatically translated into modern English using each system, and the aligned modern 
-translations were used as a reference when computing BLEU.  The results of evaluating each of the automatic evaluation metrics on this
-data are presented in figure \ref{shakespeare_to_modern_automatic}.
-
-The results suggest that modern translations generates more diverse paraphrases which better match the target style.  Note that the paraphrase system
-based on the out-of-domain video corpus makes very few changes to the input, and thus achieves a very low PINC score.  This is due to the many out of
-vocabulary words in Shakespeare's plays which result in very few matching source phrases in the video baseline's phrase table.
-
-While we have yet to perform a human evaluation on the task of paraphrasing Shakespeare's plays into modern English, 
-informal inspection of the resulting translations is encouraging.  Several automatic paraphrases into modern English are presented in Table \ref{modern_examples}.
-
-\begin{figure}
-  \includegraphics[width=5in]{figures/shakespeare_to_modern.pdf}
-  \caption{Automatic evaluation of paraphrasing Shakespeare's plays into modern english comparing a system based on parallel text (16plays\_16LM), 
-  a Dictionary baseline, and a system trained on out of domain parallel monolingual text.  Note that the video corpus baseline achieves low overal
-  PINC score, as few phrases in the input match phrases found in it's phrase table, resulting in a small number of changes to the input.}
-  \label{shakespeare_to_modern_automatic}
-\end{figure}
-
-\begin{table}
-  \begin{center}
-  \begin{tabular}{|l|p{1.8in}|p{1.8in}|}
-    \hline
-    Speaker & Input & Output \\
-    \hline
-    \hline
-    MERCUTIO & i will bite thee by the ear for that jest . & i ’ ll bite you by the ear for that joke . \\
-    \hline
-    MONTAGUE & what further woe conspires against mine age ? & what ’ s true despair conspires against my old age ? \\
-    \hline
-    ROMEO & how doth my lady ? & how is my lady ? \\
-    \hline
-    FRIAR LAURENCE & hast thou slain tybalt ? & have you killed tybalt ? \\
-    \hline
-    NURSE & an i might live to see thee married once , i have my wish . & if i could live to see you married , i ’ ve my wish . \\
-    \hline
-    PRINCE & benvolio , who began this bloody fray ? & benvolio , who started this bloody fight itself ? \\
-    \hline
-    JULIET & what is your will ? & what do you want ? \\
-    \hline
-    LADY CAPULET & call her forth to me . & bring her out to me . \\
-    \hline
-  \end{tabular}
-  \end{center}
-  \caption{Example modern paraphrases of lines from Romeo and Juliet generated using our system.}
-  \label{modern_examples}
-\end{table}
 
@@
 
-Finally, we applied these automatic evaluation metrics to an initial investigation into the task of translating Shakespeare's plays into modern English.
-We plan to translate the remaining 20 of Shakespeare's plays into modern English, which could be beneficial to students
-of Shakespeare's plays and also to human translators.
+Future work could include automatically translating the remaining 20 of Shakespeare's plays into modern English, which could be beneficial to students
+of Shakespeare's plays and also to future human translators.
 
 \bibliographystyle{apa}
-
 \bibliography{paper.bib}

### 2012-08-29 paper/paper.tex
incorporated wei's feedback

--- 2012-08-29 paper/paper.tex
@@
 
+\newpage
 \section{Introduction}
@@
 \subsection{Baselines}
-Phrase-based translation has been demonstrated as an effective approach to paraphrasing \cite{quirk04chen11}, however this approach does require the existence of
+Phrase-based translation has been demonstrated as an effective approach to paraphrasing \cite{quirk04,chen11}, however this approach does require the existence of
 parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches in order to help
@@
 
-\subsubsection{Out of Domain Monolingual Parallel Text}
+\subsubsection{Out of Domain Monolingual Parallel Data}
+\label{video_baseline}
 As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
 \cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of domain parallel text, with an in-domain
-language model consisting of Shakespeare's 36 plays (holding out Romeo and Juliet for testing), applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
+language model consisting of Shakespeare's 36 plays (holding out {\em Romeo and Juliet} for testing), applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
 Although this monolingual parallel data does not include text in the target writing style,
@@
 
+\subsection{Examples}
+Several example paraphrases of lines from {\em Romeo and Juliet} and several Hollywood movies, generated by the top performing system according to BLEU and PINC, are presented in table \ref{examples}.
+
 \begin{table}
@@
 \bibliographystyle{apa}
-
-\bibliography{paper.bib}
+\bibliography{paper}
 

### 2012-08-29 paper/paper.tex
more proofreading...

@@
 
-Although two utterances might be semantically equivalent, they can still be stylistically quite different.  For example, the same information
+Although two utterances may be semantically equivalent, they can still be stylistically quite different.  For example, the same information
 is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.
@@
     \begin{enumerate}
-    \item Students studying a specific style of writing may benefit from access to \emph{modern English} versions of works by authors they are studying.
-    \item Automatic paraphrases could help students to experiment with writing in the style of the authors whose works they are reading.
+    \item Students studying a specific literary style may benefit from access to \emph{modern English} versions of works by authors they are studying.
+    \item Automatic paraphrases could help students to experiment with writing in the style of the authors they are studying.
     \end{enumerate}
@@
 We show that previously proposed metrics do not provide the complete picture of a system's performance when the task is to generate paraphrases
-targeting a specific style of writing.  We propose two new metrics for evaluating paraphrases targeting a specific style, and measure correlation with human judgments showing promising
+targeting a specific style of writing.  We therefore propose two new metrics for evaluating paraphrases targeting a specific style, and measure correlation with human judgments showing promising
 preliminary results.
@@
 
-We compare 3 different stylistic paraphrase systems targeting Shakespearean English.  One which leverages parallel corpora of modern translations, another which makes use
+We compare 3 different stylistic paraphrase systems targeting Shakespearean English which vary in the resources they assume access to.
+One which leverages parallel corpora of modern translations, another which makes use
 of dictionaries of stylistically representative expressions, and another which utilizes out-of-domain monolingual parallel data.
@@
 of not making any changes to the modern translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making a significant number of changes to the 
-input, it's BLEU is lower than the \emph{no changes} baseline.  Secondly, it seems apparent that the systems whose parameters are tuned using Minimum Error Rate Training \cite{MERT}
+input, its BLEU is lower than the \emph{no changes} baseline.  Secondly, it seems apparent that the systems whose parameters are tuned using Minimum Error Rate Training \cite{MERT}
 tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, however also not seeing any BLEU improvements on the test data.  Finally
@@
       \hline
-      16and7plays\_36LM & Phrase table learned from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, excluding R\&J.
+      16and7plays\_36LM & Phrase table extracted from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, again excluding R\&J.
       Uses default Moses parameters. \\
       \hline
-      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT} instead of using the default Moses parameters.\\
+      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT}. \\
       \hline
-      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 with modern translations\\
+      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 plays with modern translations\\
       \hline
@@
 are more likely to contain overlapping ngrams if they are both semantically and stylistically similar.  What BLEU doesn't tell us, however
-is what portion of it's improvements are due to stylistic similarity or semantic equivalence.  For this reason, we were motivated perform
+is what portion of its improvements are due to stylistic similarity or semantic equivalence.  For this reason, we were motivated perform
 an evaluation based on human judgments of semantic adequacy, lexical dissimilarity and stylistic similarity.
 
-For this purpose, we randomly sampled 100 lines from {\em Romeo and Juliet}, then two of the authors annotated each sentence and it's Shakespearean
+For this purpose, we randomly sampled 100 lines from {\em Romeo and Juliet}, then two of the authors annotated each sentence and its Shakespearean
 translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality.
@@
 These results are roughly in line with the automatic evaluation metrics presented in figure \ref{bleupinc}, however we also see several important
-trends which are not apparent from the automatic evaluation metrics.
-Although the video baseline achieves the highest semantic adequacy in the human evaluation, it's BLEU score
+trends which are not apparent from the automatic metrics.
+Although the video baseline achieves the highest semantic adequacy in the human evaluation, its BLEU score
 is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
@@
   a Dictionary baseline, and a system trained on out of domain parallel monolingual text.  Note that the video corpus baseline achieves low overal
-  PINC score, as few phrases in the input match phrases found in it's phrase table, resulting in a small number of changes to the input.}
+  PINC score, as few phrases in the input match phrases found in its phrase table, resulting in a small number of changes to the input.}
   \label{shakespeare_to_modern_automatic}

### 2012-08-30 paper/paper.tex
more proofreading

@@
 
-We evaluate these models both through human judgments and standard evaluation metrics from the Machine Translation and Paraphrase literature, however no previous work has investigated the ability of automatic
+We evaluate these models both through human judgments and standard evaluation metrics from the machine translation and paraphrase literature, however no previous work has investigated the ability of automatic
 evaluation metrics to capture the notion of writing style.  
@@
 
-To generate paraphrases, we apply a typical phrase-based Statistical Machine Translation pipeline, performing
+To generate paraphrases, we apply a typical phrase-based statistical machine translation pipeline, performing
 word alignment on the data described in table \ref{corpus_stats} using GIZA++ \cite{Och03}, then extracting phrase pairs and performing decoding using Moses \cite{Koehn07}.
@@
 Several dictionaries of stylistically representative words of Shakespearean English and their modern equivalents are available on the web.  
-These dictionaries can be used to define a translation model which can be used in combination with a language model as in standard phrase-based Machine
-Translation.
+These dictionaries can be used to define a translation model which can be used in combination with a language model as in standard phrase-based machine
+translation.
 
@@
   \end{center}
-  \caption{Descriptions of various systems for Shakespearean Paraphrase.  {\em Romeo and Juliet} is held out for testing.}
+  \caption{Descriptions of various systems for Shakespearean paraphrase.  {\em Romeo and Juliet} is held out for testing.}
   \label{systems}
@@
   \end{center}
-  \caption{Various Shakespearean Paraphrase systems compared using BLEU and PINC.  A brief description of each system is presented in table \ref{systems}.}
+  \caption{Various Shakespearean paraphrase systems compared using BLEU and PINC.  A brief description of each system is presented in table \ref{systems}.}
   \label{bleupinc}
@@
       \hline
-      Terminator 2 & Terminator & My mission is to protect you. & my affair is to keep you . \\
+      %Terminator 2 & Terminator & My mission is to protect you. & my affair is to keep you . \\
       %\hline
@@
 \\
-      \hline
-      Terminator 2 & Terminator & Skynet begins to learn at a geometric rate.
+      %\hline
+      %Terminator 2 & Terminator & Skynet begins to learn at a geometric rate.
 ...
@@
 \\
-      \hline
+      %\hline
     \end{tabular}
@@
 These results are roughly in line with the automatic evaluation metrics presented in figure \ref{bleupinc}, however we also see several important
-trends which are not apparent from the automatic metrics.
+trends which are not apparent from the automatic evaluation.
 Although the video baseline achieves the highest semantic adequacy in the human evaluation, its BLEU score
@@
 We trained both the logistic regression and cosine similarity evaluation metrics using the original Shakespeare plays and modern translations as
-the source and target corpus respectively (holding out Romeo and Juliet), then measured Pearson's Correlation Coefficient between the automatic
-evaluation metrics and human judgments reported in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.
+the source and target corpus respectively (holding out {\em Romeo and Juliet}), then measured Pearson's Correlation Coefficient between the automatic
+evaluation metrics and human judgments described in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.
 
@@
     \hline
-    style & Maximum Entropy & 0.47 \\
+    style & Logistic regression & 0.47 \\
     \hline
@@
 
-Both the Cosine and Maximum Entropy style metrics achieve the highest overall correlation with human writing style judgments, with the Maximum Entropy style score performing significantly better.
+Both the cosine and logistic regression style metrics achieve the highest overall correlation with human writing style judgments, with the logistic regression style score performing best.
 
-Finally we note that overall the automatic metrics tend to agree with agree with human judgments as displayed in figure \ref{style_metrics}.\footnote{
+We note that overall the automatic metrics tend to agree with agree with human judgments as displayed in figure \ref{style_metrics}.\footnote{
   Although the automatic style metrics rate the dictionary system higher than the video corpus baseline, both systems have very comparable
@@
 \section{Translating Shakespeare's Plays to Modern English}
-Finally we preform a preliminary evaluation of the task of automatically translating Shakespeare's plays into modern English.  Success at this task could have immediate
+Finally we preform a preliminary evaluation on the task of automatically translating Shakespeare's plays into modern English.  Success at this task could have immediate
 benefits to students, as well as translators of Shakespeare's plays into modern English.
@@
 
-The results suggest that in comparison to the dictionary and video corpus baselines, 
-our system trained on modern translations generates diverse paraphrases which match the target style.
+These results suggest that in comparison to the dictionary and video corpus baselines, 
+our system trained on modern translations generates a large number of paraphrases which match the target style.
 Note that the paraphrase system 
@@
 \section{Related Work}
-Although no previous work has investigated paraphrasing modern text into Shakespearean English, or the more general task of paraphrasing while targeting a specific writing
-style, we highlight several strands of related work.
-
 Much previous work has addressed the task of automatically generating paraphrases \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05,Callison-Burch08,Kok10}.  
@@
 automatic metrics specifically for evaluating paraphrases \cite{chen11,Callison-Burch08b,liu10}.
-We are not aware, however, of any previous work that has addressed the task of generating or evaluating
+We are not aware, however, of any work that has addressed the task of generating or evaluating
 paraphrases targeting a specific style of writing.
@@
 Perhaps most relevant, however, is recent work autoatic generation of rhythmic poetry \cite{Greene10}.  This work focuses on automatically generating and translating
-poetry in an appropriate meter (e.g. iambic pentameter) using finite-state transducers, however doesn't address the issue of paraphrase.  Their generation system
+poetry in an appropriate meter (e.g. iambic pentameter) using finite-state transducers, however does not investigate the task of paraphrase.  Their generation system
 is trained on Shakespeare's sonnets, and they investigate the task of automatically translating Dante's Divine Comedy from Italian to English.
@@
 metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivalence with writing style giving an incomplete picture of which systems
-perform better according to each of these criteria.
+perform better according to each criteria.
 
 To address this problem, we have introduced two new metrics for evaluating writing style.
-We measured correlation between automatic metrics and human judgments in the context of paraphrasing writing style, and showed
-that our new metrics have better correlation with human judgments than existing metrics in the context of our data.
+We measured correlation between automatic metrics and human judgments, and showed
+that our new metrics have better correlation with human judgments than existing metrics in the context of our task.
 While this evaluation is limited to one specific style of writing, we are optimistic that these or similar metrics will also perform well when
@@
 
-Finally, we applied these automatic evaluation metrics to an initial investigation into the task of translating Shakespeare's plays into modern English.
-We plan to translate the remaining 20 of Shakespeare's plays into modern English, which could be beneficial to students
-of Shakespeare's plays and also to human translators.
+Finally, we applied these automatic evaluation metrics in an initial investigation into the task of translating Shakespeare's plays into modern English.
+We plan to translate the remaining 20 of Shakespeare's plays, which could be beneficial to students
+of Shakespeare and also to human translators.
 

### 2012-08-30 paper/figures/plot_style.R
changed figure

@@ -11,7 +11,7 @@
 pdf('style_metrics.pdf', width=8, height=5)
 
 systems = c('16plays36LM', 'Dictionary', 'Video Baseline')
-metrics = c('Cosine Similarity', 'Maximum Entropy')
+metrics = c('Cosine Similarity', 'Logistic Regression')
 
 barplot(t(rbind(
 	 c(0.512979241631, 0.491599098577, 0.480059827357),

### 2012-08-31 paper/paper.tex

@@
 %\title{Translating to Shakespeare: A Case Study in Paraphrasing Writing Styles}
-\title{You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles}
+%\title{You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles}
+%\title{A rose would smell just as good even if it had a different name (``A rose by any other name would smell as sweet'') \\ A Case Study in Paraphrase Targeting Writing Styles}
+%\title{“Be super careful on March 15” (“Beware the ides of March”) \\ A Case Study in Paraphrase Targeting Writing Styles}
+\title{``A rose by any other name would smell as sweet'': \\ A Case Study in Paraphrase Targeting Writing Styles}
 %for authors: in case of more than four author names ref. to commented line below 
@@
 
-Identical meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
+The same meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
 fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.
 
-Although two utterances may be semantically equivalent, they can still be stylistically quite different.  For example, the same information
-is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.
+Paraphrases can differ along many dimensions, including utterance length, diction level, and speech register. 
+There is a significant literature in sentence compression aimed at modeling the first of these, length: 
+producing meaning-preserving alternations that preserve the meaning of the input string. [citations] 
+However, we know of no previous work aimed at modeling meaning-preserving transformations that systematically transform the register or style of an input string. 
+Can we learn to reliably map from one form of language to another, transforming formal prose into a more colloquial form, or a casual email into a more formal equivalent?
+
+%Although two utterances may be semantically equivalent, they can still be stylistically quite different.  For example, the same information
+%is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.
 
@@
 \begin{enumerate}
-  \item Help authors of technical documents to adhere to appropriate stylistic guidelines.  
-  \item Enable average people to better understand information in legal documents by translating ``legalese'' into ordinary English.  
+  \item Help authors of technical documents to adhere to appropriate stylistic guidelines, or allow writers to automatically “upscale” an email before sending it
+  \item Enable non-specialists to better understand information in legal or medical documents by translating ``legalese'' or medical jargon into ordinary English.  
   \item Benefit educational applications:
     \begin{enumerate}
-    \item Students studying a specific literary style may benefit from access to \emph{modern English} versions of works by authors they are studying.
-    \item Automatic paraphrases could help students to experiment with writing in the style of the authors they are studying.
+    \item Students studying a specific literary style could benefit from access to \emph{modern English} versions of works by authors they are studying.
+    \item Automatic register transformations could help students to experiment with writing in the style of the authors they are studying.
     \end{enumerate}
@@
 
-We evaluate these models both through human judgments and standard evaluation metrics from the machine translation and paraphrase literature, however no previous work has investigated the ability of automatic
+We evaluate these models both through human judgments and standard evaluation metrics from the machine translation and paraphrase literature.  
+However, no previous work has investigated the ability of automatic
 evaluation metrics to capture the notion of writing style.  
 We show that previously proposed metrics do not provide the complete picture of a system's performance when the task is to generate paraphrases
-targeting a specific style of writing.  We therefore propose two new metrics for evaluating paraphrases targeting a specific style, and measure correlation with human judgments showing promising
-preliminary results.
+targeting a specific style of writing.  We therefore propose two new metrics for evaluating paraphrases targeting a specific style, and 
+show that these metrics correlate well with human judgments.
 
+\begin{comment}
 Systems which are capable of automatically paraphrasing literary writing styles could be directly beneficial for educational applications.
@@
 we believe it should be possible to help make these plays more accessible to students of Shakespeare.
+\end{comment}
 
 \section{Shakespearean Paraphrasing}
-We propose to use Shakespeare's plays as a testbed for the task of paraphrasing while targeting a specific writing style.  Because these plays are some of the
-highest regarded examples of English literature and are also very unique in style, many linguistic resources are available such as parallel corpora
-of modern translations and dictionaries of stylistically representative words and their modern equivalents.
+We use Shakespeare's plays as a testbed for the task of paraphrasing while targeting a specific writing style.  Because these plays are some of 
+the most highly-regarded examples of English literature and 
+are written in a style that is now 400 years out of date, many linguistic resources are available to help modern readers pick their way through 
+these Elizabethan texts. Among these are “translations” of the plays into colloquial English, and dictionaries that provide modern equivalents for specific words and phrases.
 
-We compare 3 different stylistic paraphrase systems targeting Shakespearean English which vary in the resources they assume access to.
-One which leverages parallel corpora of modern translations, another which makes use
-of dictionaries of stylistically representative expressions, and another which utilizes out-of-domain monolingual parallel data.
+We compare 3 different stylistic paraphrase systems targeting Shakespearean English which rely on different types of linguistic resources. 
+One leverages parallel “translations”, another exploits dictionary resources, and a third relies on modern, out-of-domain monolingual parallel data and an in-domain corpus.
 

### 2012-08-31 python_wei/add_scores_wei_lm.py
LM metric that succeeds

@@ -116,19 +116,22 @@ def corelation_auto_human (filename):
     _16plays36_cmaxent_list = []
     _16plays36_lmdiff_list = []
     _16plays36_lmdiff2_list = []
+    _16plays36_lmdiff3_list = []
     phrase_bleu_list = []
     phrase_pinc_list = []
     phrase_csim_list = []
     phrase_cmaxent_list = []
     phrase_lmdiff_list = []
     phrase_lmdiff2_list = []
+    phrase_lmdiff3_list = []
     video_bleu_list = []
     video_pinc_list = []
     video_csim_list = []
     video_cmaxent_list = []
     video_lmdiff_list = []
     video_lmdiff2_list = []
-
+    video_lmdiff3_list = []
+    
     _16plays36_semantic_list = []
     _16plays36_dissim_list = []
     _16plays36_style_list = []
@@ -166,6 +169,7 @@ def corelation_auto_human (filename):
         _16plays36_cmaxent_list.append(sm.ScoreMaxEnt(_16plays36))
         _16plays36_lmdiff_list.append(LMdiff(_16plays36))
         _16plays36_lmdiff2_list.append(LMdiff2(_16plays36, modern))
+        _16plays36_lmdiff3_list.append(LMdiff3(_16plays36))
 
         phrase_bleu_list.append(simple_bleu(phrase, original))
         phrase_pinc_list.append(pinc(phrase, modern))
@@ -173,6 +177,7 @@ def corelation_auto_human (filename):
         phrase_cmaxent_list.append(sm.ScoreMaxEnt(phrase))
         phrase_lmdiff_list.append(LMdiff(phrase))
         phrase_lmdiff2_list.append(LMdiff2(phrase, modern))
+        phrase_lmdiff3_list.append(LMdiff3(phrase))
 
         video_bleu_list.append(simple_bleu(video, original))
         video_pinc_list.append(pinc(video, modern))
@@ -180,6 +185,7 @@ def corelation_auto_human (filename):
         video_cmaxent_list.append(sm.ScoreMaxEnt(video))
         video_lmdiff_list.append(LMdiff(video))
         video_lmdiff2_list.append(LMdiff2(video, modern))
+        video_lmdiff3_list.append(LMdiff3(video))
        
         i += 1
 
@@ -193,6 +199,7 @@ def corelation_auto_human (filename):
[…]

### 2012-08-31 python_wei/lm_score.py

@@ -1,9 +1,11 @@
 import subprocess
 import re
+from math import log10
 
-
-lmoriginal = "/Users/weixu/Work/Shakespere/Shakespere/models/LMs/36plays_tokenized_lowercased.original.lm"    
+#lmoriginal = "/Users/weixu/Work/Shakespere/Shakespere/models/LMs/36plays_tokenized_lowercased.original.lm"    
+lmoriginal = "/Users/weixu/Work/Shakespere/Shakespere/models/LMs/16plays_tokenized_lowercased.original.lm"    
 lmmodern = "/Users/weixu/Work/Shakespere/Shakespere/models2/LM/16plays_tokenized_lowercased.modern.lm"    
+
 
 def sent_logprob (sent, lmfile) :
     f = open('tmp_sent', 'w')
@@ -27,10 +29,19 @@ def LMdiff2 (osent, msent) :
     logprob_lmoriginal_m = sent_logprob (msent, lmoriginal) ['logprob']
     diff = logprob_lmoriginal_o - logprob_lmoriginal_m
     return diff
+    
+    
+def LMdiff3 (sent) :
+    logprob_lmoriginal = sent_logprob (sent, lmoriginal) ['logprob']
+    logprob_lmmodern   = sent_logprob (sent, lmmodern) ['logprob']
+    #diff = log10 ( 1 / (1 + pow(10,logprob_lmoriginal - logprob_lmmodern)) )
+    diff = pow(10, logprob_lmoriginal) / (pow(10, logprob_lmoriginal) + pow(10,logprob_lmmodern))
+    return diff
+
 
 #sentence = "wilt thou take them ?"
-#sentence = "do you need my help ?"
+sentence = "do you need my help ?"
 #print sent_logprob (sentence, lmoriginal)
 #print sent_logprob (sentence, lmmodern)
 
-#print LMdiff(sentence)
+print LMdiff3(sentence)

### 2012-08-31 paper/paper.tex
incorporated the rest of Bill's feedback

@@
 \subsection{Modern Translations}
-Access to parallel text in the target style allows us to train statistical models to generate paraphrases, and also perform automatic evaluation of semantic adequacy using BLEU, which requires availability of reference translations.
-For this purpose we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}, and an additional 8 translations of overlapping plays from \url{http://enotes.com}, giving us two reference translations for 8 out of the 17 plays.
+\label{modern_translations}
+Access to parallel text in the target style allows us to train statistical models that generate paraphrases, and also perform automatic evaluation of semantic adequacy using BLEU, which requires availability of reference translations.
+For this purpose we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}, and
+additional translations of 8 of these plays from from \url{http://enotes.com}.
 
-After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence aligner \cite{Moore02}, which produced about 21,079 alignments out of 31,718 sentences in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the Enotes data.
-The modern translations from each source are qualitatively quite
+After tokenizing and lowercasing, the plays were sentence aligned \cite{Moore02}, producing 21,079 alignments from the 31,718 sentence pairs in the Sparknotes data, and 10,365 sentence pairs from the 13,640 original
+pairs in the Enotes data.  The modern translations from the two sources are qualitatively quite
 different.  The Sparknotes paraphrases tend to differ significantly from the original text, whereas the Enotes translations are much more conservative, making fewer changes.
-To illustrate these differences empirically and provide an initial paraphrase baseline, we computed BLEU scores of the unchanged modern translations against Shakespeare's 
-original text; the Sparknotes paraphrases result in a BLEU score of 24.67, whereas the Enotes paraphrases produce a much higher BLEU of 52.30 indicating their strong similarity to the original plays.
-These corpus statistics are summarized in table \ref{corpus_stats}.
+To illustrate these differences empirically and provide an initial paraphrase baseline, we computed BLEU scores of the modern translations against Shakespeare's 
+original text; the Sparknotes paraphrases yield a BLEU score of 24.67, whereas the Enotes paraphrases produce a much higher BLEU of 52.30 reflecting their strong similarity to the original texts.
+These results are summarized in table \ref{corpus_stats}.
 
@@
 \subsection{Baselines}
-Phrase-based translation has been demonstrated as an effective approach to paraphrasing \cite{quirk04,chen11}, however this approach does require the existence of
-parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches in order to help
+Phrase-based translation has been demonstrated as an effective approach to paraphrasing \cite{quirk04,chen11}.  However, this approach does require the existence of
+parallel corpora, resources which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches in order to help
 quantify the benefit of access to parallel text in the source and target styles.
@@
 For instance, if we look at the modern English word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations. 
-We obtained the conditional probabilities for each translation according to the n-gram back off model built on Shakespeare's 
-36 plays by SRILM toolkit \cite{Stolcke02} \ref{word_frequency}, 
+We obtained the conditional probabilities for each translation according to the n-gram back-off model built from 36 of Shakespeare's 
+plays ({\em Romeo and Juliet} was held out for testing) using the SRILM toolkit \cite{Stolcke02}, 
 normalizing the probabilities for each source phrase, for example $p(\text{PERCHANGE}|\text{maybe}) = \frac{0.0000790755}{0.00026264791} = 0.30107035689$.
+An example is presented in Table \ref{word_frequency}.
 This method allows us to estimate reasonable translation probabilities for use in a phrase table, which is used in combination 
-with a language model consisting of Shakespeare's 36 plays (holding out {\em Romeo and Juliet}), which are then fed into the Moses decoder
-\cite{Koehn07}.
+with a language model built from the 36 plays, which are then fed into the Moses decoder \cite{Koehn07}.
 
@@
 As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
-\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of domain parallel text, with an in-domain
-language model consisting of Shakespeare's 36 plays (holding out {\em Romeo and Juliet} for testing), applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
+\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this modern, out of domain parallel text, with an in-domain
+language model consisting of Shakespeare's 36 plays (again, holding out {\em Romeo and Juliet} for testing), applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
 Although this monolingual parallel data does not include text in the target writing style,
 the in-domain language model does bias the system's output towards Shakespeare's style of writing.
-We found that performing Minimum Error Rate Training using a small set of held out parallel text from Romeo and Juliet was necessary in order to tune the
+We found that performing Minimum Error Rate Training \cite{MERT} using a small set of held out parallel text from Romeo and Juliet was necessary in order to tune the
 video corpus baseline to generate reasonable paraphrases.
@@
 have been demonstrated to correlate with human judgments on semantic adequacy and lexical dissimilarity with the input.
-A description of each of the systems compared in this experiment is presented in table \ref{systems}.  Notice that the Enotes paraphrases are quite similar to the original text,
-obtaining a BLEU score of 52.3 when compared directly to the original lines from Shakespeare's plays.
+A description of each of the systems compared in this experiment is presented in Table \ref{systems}.
+As mentioned in \S \ref{modern_translations}, the Enotes paraphrases diverge little from the original text,
+resulting in a BLEU score of 52.3 when compared directly to the original lines from Shakespeare's plays.
 Because our goal is to produce paraphrases which make more dramatic stylistic changes to the input,
@@
 \subsubsection{Discussion}
-Two main trends emerge from Figure \ref{bleupinc}.  First, notice that all of the systems which are trained using parallel text achieve higher BLEU scores than the baseline
-of not making any changes to the modern translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making a significant number of changes to the 
-input, its BLEU is lower than the \emph{no changes} baseline.  Secondly, it seems apparent that the systems whose parameters are tuned using Minimum Error Rate Training \cite{MERT}
-tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, however also not seeing any BLEU improvements on the test data.  Finally
-we note that using the larger language model seems to yield a slight improvement in BLEU score.
+Two main trends are evident in Figure \ref{bleupinc}.  First, notice that all of the systems trained using parallel text achieve higher BLEU scores than the unmodified modern
+translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making a significant number of changes to the 
+input, its BLEU is lower than that of the modern translations.  Secondly, it seems apparent that the systems whose parameters are tuned using Minimum Error Rate Training
+tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, while not improving BLEU scores on the test data.  Finally
+we note that using the larger target language model seems to yield a slight improvement in BLEU score.
 
@@
       video\_corpus\_baseline & Paraphrase system combining out of domain parallel text \cite{chen11} with an in-domain language model.  Described
-      in detail in section \ref{video_baseline}. \\
+      in detail in \S \ref{video_baseline}. \\
       \hline
@@
       \hline
-      Dictionary & Dictionary baseline described in section \ref{dictionary_baseline}\\
+      Dictionary & Dictionary baseline described in \S \ref{dictionary_baseline}\\
       \hline
@@
 Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is initially unclear how well the BLEU and PINC
-automatic evaluation metrics perform when applied to evaluating paraphrases targeting a specific style of writing.  BLEU and PINC have previously
-been shown to have high correlation with human judgments of semantic adequacy and lexical dissimilarity of paraphrase candidates, however no
-previous work has evaluated automatically generated paraphrases which target a specific style of writing.
+automatic evaluation metrics perform when applied to evaluating paraphrases that target a specific style of writing.  BLEU and PINC have previously
+been shown to have high correlation with human judgments of semantic adequacy and lexical dissimilarity of paraphrase candidates, 
+but no corresponding work exists for paraphrasing models that target a specific style of writing.
 
-While BLEU is typically used to measure semantic adequacy, it seems reasonable to assume that it may also depend on style, since utterances
-are more likely to contain overlapping ngrams if they are both semantically and stylistically similar.  What BLEU doesn't tell us, however
+While BLEU is typically used to measure semantic adequacy, it seems reasonable to assume that it 
+could also be useful for measuring stylistic alternations, since utterances
+are more likely to contain overlapping ngrams if they are both semantically and stylistically similar.  What BLEU cannot tell us, however
 is what portion of its improvements are due to stylistic similarity or semantic equivalence.  For this reason, we were motivated perform
@@
 For this purpose, we randomly sampled 100 lines from {\em Romeo and Juliet}, then two of the authors annotated each sentence and its Shakespearean
-translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality.
-The aggregate results of the human evaluation are displayed in figure \ref{human_judgements}.  Agreement between annotators
-measured using Pearson's $\rho$ is displayed in table \ref{annotator_agreement}.
+translation to indicate semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality.
+The aggregate results of the human evaluation are displayed in Figure \ref{human_judgements}.  Agreement between annotators
+measured using Pearson's $\rho$ is displayed in Table \ref{annotator_agreement}.
 
-Based on the human evaluation, it appears that the baseline combining paraphrases collected from mechanical Turk \cite{chen11} with
-a Shakespearean language model has the highest semantic adequacy, however it is also fairly conservative making few changes to the input.
+Based on the human evaluation, it appears that the baseline combining paraphrases collected from Mechanical Turk \cite{chen11} with
+a Shakespearean language model has the highest semantic adequacy, yet this approach is also fairly conservative in that it makes few changes to the input.
 
-The dictionary baseline, and paraphrase system trained on parallel modern translations are roughly comparable when it comes to 
-the number of changes made to the input, however the system trained on modern translations achieves higher semantic adequacy, while also being rated higher on style and overall.
+The dictionary baseline, and the paraphrase system trained on parallel modern translations are roughly comparable in terms of 
+the number of changes made to the input, but the system trained on modern translations achieves higher semantic adequacy, while also being rated higher on style and overall.
 
-These results are roughly in line with the automatic evaluation metrics presented in figure \ref{bleupinc}, however we also see several important
+These results are roughly in line with the automatic evaluation metrics presented in Figure \ref{bleupinc}.  However we also see several important
 trends which are not apparent from the automatic evaluation.
@@
 \section{Automatic Metrics Evaluating Writing Style}
-While PINC and BLEU do seem useful for automatically evaluating paraphrases targeting a  writing style, BLEU tends to conflate the notions of
+While PINC and BLEU do seem useful for automatically evaluating stylistic paraphrases, BLEU tends to conflate the notions of
 semantic adequacy with writing style.  When comparing various systems using automatic metrics, it would seem useful
-to separate effects caused by these two distinct criteria.  We would like our automatic evaluation metrics to be able to distinguish
-between a system which generates perfect paraphrases which don't match the target style of writing and a system which
+to separate the effects caused by these two distinct criteria.  We would like our automatic evaluation metrics to be able to distinguish
+between a system which generates perfect paraphrases which do not match the target style of writing versus a system which
 generates sentences in the correct style, but which convey different meaning.
@@
 
-We present a preliminary evaluation of these metrics by measuring their correlation with human judgments, however
-we emphasize that we are only evaluating these metrics with respect to one specific style of writing.  We
-are cautiously optimistic that our results will generalize across writing styles, however, as they are based entirely
+We present a preliminary evaluation of these metrics by measuring their correlation with human judgments, but
+it should be emphasized that we are only evaluating these metrics with respect to one specific style of writing.  We
+are optimistic that these results will generalize across writing styles, however, since they are based entirely
 on ngram statistics.
@@
 the source and target corpus respectively (holding out {\em Romeo and Juliet}), then measured Pearson's Correlation Coefficient between the automatic
-evaluation metrics and human judgments described in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.
+evaluation metrics and human judgments described in \S \ref{human_evaluation}.  These results are reported in table \ref{correlation}.
 
@@
 As can be seen in table \ref{correlation}, the correlation between semantic adequacy and BLEU appears smaller than that reported in previous work \cite{chen11}.  Presumably this is
-due to the conflation of stylistic differences and semantic adequacy discussed discussed in section \ref{human_evaluation}, however it also appears 
+due to the conflation of stylistic differences and semantic adequacy discussed discussed in \S \ref{human_evaluation}.  However it also appears 
 that the correlation between BLEU and human style judgments is too low to be of practical use for evaluating style.
@@
 \section{Translating Shakespeare's Plays to Modern English}
-Finally we preform a preliminary evaluation on the task of automatically translating Shakespeare's plays into modern English.  Success at this task could have immediate
-benefits to students, as well as translators of Shakespeare's plays into modern English.
+Finally we perform a preliminary evaluation on the task of automatically translating Shakespeare's plays into modern English.  
+%Success at this task could have immediate benefits to students, as well as translators of Shakespeare's plays into modern English.
 
@@
 we make use of the same paraphrase systems previously described, but swap the source and target languages.
-Additionally, each system makes use of a language model constructed from the 16 modern translations, and again Romeo and Juliet are held out for testing.  
-510 lines from Romeo and Juliet were automatically translated into modern English using each system, and the aligned modern 
+Additionally, each system makes use of a language model constructed from the 16 modern translations, with {\em Romeo and Juliet} held out for testing.  
+510 lines from {\em Romeo and Juliet} were automatically translated into modern English using each system, and the aligned modern 
 translations were used as a reference when computing BLEU.  The results of evaluating each of the automatic evaluation metrics on this
-data are presented in figure \ref{shakespeare_to_modern_automatic}.
+data are presented in Figure \ref{shakespeare_to_modern_automatic}.
 
@@
   \includegraphics[width=5in]{figures/shakespeare_to_modern.pdf}
-  \caption{Automatic evaluation of paraphrasing Shakespeare's plays into modern english comparing a system based on parallel text (16plays\_16LM), 
-  a Dictionary baseline, and a system trained on out of domain parallel monolingual text.  Note that the video corpus baseline achieves low overal
+  \caption{Automatic evaluation of paraphrasing Shakespeare's plays into modern English comparing a system based on parallel text (16plays\_16LM), 
+  a Dictionary baseline, and a system trained on out of domain parallel monolingual text.  Note that the video corpus baseline achieves low overall
   PINC score, as few phrases in the input match phrases found in its phrase table, resulting in a small number of changes to the input.}
@@
 
-Perhaps most relevant, however, is recent work autoatic generation of rhythmic poetry \cite{Greene10}.  This work focuses on automatically generating and translating
-poetry in an appropriate meter (e.g. iambic pentameter) using finite-state transducers, however does not investigate the task of paraphrase.  Their generation system
+Perhaps most relevant, however, is recent work automatic generation of rhythmic poetry \cite{Greene10}.  This work focuses on automatically generating and translating
+poetry in an appropriate meter (e.g. iambic pentameter) using finite-state transducers, but does not investigate the task of paraphrase.  Their generation system
 is trained on Shakespeare's sonnets, and they investigate the task of automatically translating Dante's Divine Comedy from Italian to English.
@@
 \section{Conclusions}
-We have presented initial investigation into the task of automatic paraphrasing while targeting a specific style of writing.  We proposed Shakespeare's plays and their
+We have presented the first investigation into the task of automatic paraphrasing while targeting a specific writing style.  We proposed Shakespeare's plays and their
 modern translations as a tesbed for this task, and developed a series of paraphrase systems targeting Shakespearean English.  We showed that while existing evaluation
@@
 
-To address this problem, we have introduced two new metrics for evaluating writing style.
+To address this problem, we introduced two new metrics for evaluating writing style, one of which is based on cosine similarity and another based on logistic regression.
 We measured correlation between automatic metrics and human judgments, and showed
@@
 Finally, we applied these automatic evaluation metrics in an initial investigation into the task of translating Shakespeare's plays into modern English.
-We plan to translate the remaining 20 of Shakespeare's plays, which could be beneficial to students
-of Shakespeare and also to human translators.
+%We plan to translate the remaining 20 of Shakespeare's plays, which could be beneficial to students
+%of Shakespeare and also to human translators.
 

### 2012-08-31 python_wei/add_scores_wei_lm.py
LM-based metric beat MaxEnt

@@ -117,6 +117,10 @@ def corelation_auto_human (filename):
     _16plays36_lmdiff_list = []
     _16plays36_lmdiff2_list = []
     _16plays36_lmdiff3_list = []
+    _16plays36_lmdiff4_list = []
+    _16plays36_lmdiff5_list = []
+    _16plays36_lmdiff6_list = []
+    _16plays36_lmdiff7_list = []
     phrase_bleu_list = []
     phrase_pinc_list = []
     phrase_csim_list = []
@@ -124,6 +128,10 @@ def corelation_auto_human (filename):
     phrase_lmdiff_list = []
     phrase_lmdiff2_list = []
     phrase_lmdiff3_list = []
+    phrase_lmdiff4_list = []
+    phrase_lmdiff5_list = []
+    phrase_lmdiff6_list = []
+    phrase_lmdiff7_list = []
     video_bleu_list = []
     video_pinc_list = []
     video_csim_list = []
@@ -131,6 +139,10 @@ def corelation_auto_human (filename):
     video_lmdiff_list = []
     video_lmdiff2_list = []
     video_lmdiff3_list = []
+    video_lmdiff4_list = []
+    video_lmdiff5_list = []
+    video_lmdiff6_list = []
+    video_lmdiff7_list = []
     
     _16plays36_semantic_list = []
     _16plays36_dissim_list = []
@@ -170,6 +182,10 @@ def corelation_auto_human (filename):
         _16plays36_lmdiff_list.append(LMdiff(_16plays36))
         _16plays36_lmdiff2_list.append(LMdiff2(_16plays36, modern))
         _16plays36_lmdiff3_list.append(LMdiff3(_16plays36))
+        _16plays36_lmdiff4_list.append(LMdiff4(_16plays36))
+        _16plays36_lmdiff5_list.append(LMdiff5(_16plays36))
+        _16plays36_lmdiff6_list.append(LMdiff6(_16plays36))
+        _16plays36_lmdiff7_list.append(LMdiff7(_16plays36))
 
         phrase_bleu_list.append(simple_bleu(phrase, original))
         phrase_pinc_list.append(pinc(phrase, modern))
@@ -178,6 +194,10 @@ def corelation_auto_human (filename):
         phrase_lmdiff_list.append(LMdiff(phrase))
         phrase_lmdiff2_list.append(LMdiff2(phrase, modern))
         phrase_lmdiff3_list.append(LMdiff3(phrase))
[…]

### 2012-08-31 python_wei/lm_score.py

@@ -1,11 +1,14 @@
 import subprocess
 import re
-from math import log10
+import math
 
-#lmoriginal = "/Users/weixu/Work/Shakespere/Shakespere/models/LMs/36plays_tokenized_lowercased.original.lm"    
+lmoriginal2 = "/Users/weixu/Work/Shakespere/Shakespere/models/LMs/36plays_tokenized_lowercased.original.lm"    
 lmoriginal = "/Users/weixu/Work/Shakespere/Shakespere/models/LMs/16plays_tokenized_lowercased.original.lm"    
 lmmodern = "/Users/weixu/Work/Shakespere/Shakespere/models2/LM/16plays_tokenized_lowercased.modern.lm"    
 
+def logexpsum(logprobs):
+    m = max(logprobs)
+    return(m + math.log(sum([math.exp(x - m) for x in logprobs])))
 
 def sent_logprob (sent, lmfile) :
     f = open('tmp_sent', 'w')
@@ -38,10 +41,38 @@ def LMdiff3 (sent) :
     diff = pow(10, logprob_lmoriginal) / (pow(10, logprob_lmoriginal) + pow(10,logprob_lmmodern))
     return diff
 
+def LMdiff4 (sent) :
+    logprob_lmoriginal = sent_logprob (sent, lmoriginal) ['logprob']
+    logprob_lmmodern   = sent_logprob (sent, lmmodern) ['logprob']
+    diff = logprob_lmoriginal - logexpsum([logprob_lmoriginal, logprob_lmmodern])
+    return diff
 
+def LMdiff5 (sent) :
+    logprob_lmoriginal = sent_logprob (sent, lmoriginal) ['logprob']
+    logprob_lmmodern   = sent_logprob (sent, lmmodern) ['logprob']
+    diff = logprob_lmoriginal - logexpsum([logprob_lmoriginal, logprob_lmmodern])
+    diff = pow(10, diff)
+    return diff
+    
+def LMdiff6 (sent) :
+    logprob_lmoriginal = sent_logprob (sent, lmoriginal2) ['logprob']
+    logprob_lmmodern   = sent_logprob (sent, lmmodern) ['logprob']
+    diff = logprob_lmoriginal - logexpsum([logprob_lmoriginal, logprob_lmmodern])
+    return diff
+
+def LMdiff7 (sent) :
+    logprob_lmoriginal = sent_logprob (sent, lmoriginal2) ['logprob']
[…]

### 2012-08-31 paper/paper.tex

@@
 There is a significant literature in sentence compression aimed at modeling the first of these, length: 
-producing meaning-preserving alternations that preserve the meaning of the input string. [citations] 
+producing meaning-preserving alternations that reduce the length of the input string {\bf TODO:} [citations].
 However, we know of no previous work aimed at modeling meaning-preserving transformations that systematically transform the register or style of an input string. 
@@
 \begin{enumerate}
-  \item Help authors of technical documents to adhere to appropriate stylistic guidelines, or allow writers to automatically “upscale” an email before sending it
-  \item Enable non-specialists to better understand information in legal or medical documents by translating ``legalese'' or medical jargon into ordinary English.  
+  \item Help authors of technical documents to adhere to appropriate stylistic guidelines, or allow writers to automatically “upscale” an email before sending it.
+  \item Enable non-specialists to better understand information in legal or medical documents by translating ``legalese'' and medical jargon into ordinary English.  
   \item Benefit educational applications:

### 2012-08-31 paper/paper.tex
incorporated more of bill's feedback

--- 2012-08-31 paper/paper.tex
@@
 %\title{Translating to Shakespeare: A Case Study in Paraphrasing Writing Styles}
-%\title{You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles}
-%\title{A rose would smell just as good even if it had a different name (``A rose by any other name would smell as sweet'') \\ A Case Study in Paraphrase Targeting Writing Styles}
-%\title{“Be super careful on March 15” (“Beware the ides of March”) \\ A Case Study in Paraphrase Targeting Writing Styles}
-\title{``A rose by any other name would smell as sweet'': \\ A Case Study in Paraphrase Targeting Writing Styles}
+\title{You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles}
 %for authors: in case of more than four author names ref. to commented line below 
@@
 
-The same meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
+Identical meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
 fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.
 
-Paraphrases can differ along many dimensions, including utterance length, diction level, and speech register. 
-There is a significant literature in sentence compression aimed at modeling the first of these, length: 
-producing meaning-preserving alternations that preserve the meaning of the input string. [citations] 
-However, we know of no previous work aimed at modeling meaning-preserving transformations that systematically transform the register or style of an input string. 
-Can we learn to reliably map from one form of language to another, transforming formal prose into a more colloquial form, or a casual email into a more formal equivalent?
-
-%Although two utterances may be semantically equivalent, they can still be stylistically quite different.  For example, the same information
-%is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.
+Although two utterances may be semantically equivalent, they can still be stylistically quite different.  For example, the same information
+is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.
 
@@
 \begin{enumerate}
-  \item Help authors of technical documents to adhere to appropriate stylistic guidelines, or allow writers to automatically “upscale” an email before sending it
-  \item Enable non-specialists to better understand information in legal or medical documents by translating ``legalese'' or medical jargon into ordinary English.  
-  \item Benefit educational applications:
+  \item Help authors of technical documents to adhere to appropriate stylistic guidelines.  
+  \item Enable average people to better consume information by translating legalese or medical jargon into nontechnical English.  
+  \item Benefit educational applications, allowing students to:
     \begin{enumerate}
-    \item Students studying a specific literary style could benefit from access to \emph{modern English} versions of works by authors they are studying.
-    \item Automatic register transformations could help students to experiment with writing in the style of the authors they are studying.
+    \item Access \emph{modern English} versions of works by authors they are studying.
+    \item Experiment with writing in the style of an author they are studying.
     \end{enumerate}
@@
 
-In this paper, we investigate the task of automatic paraphrasing when targeting a writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
-We exploit modern translations of 17 plays written to help students better understand Shakespeare's work.  A parallel corpus is extracted from these modern translations,
-which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakespearean English.  In addition we develop several
-baseline systems which do not make use of this source of parallel text and instead rely on manually compiled dictionaries of expressions commonly found in Shakespearean English, or out of
-domain parallel monolingual text gathered through Amazon's Mechanical Turk \cite{chen11}.
+In this paper, we investigate the task of automatic paraphrasing techniques that target a particular writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
+We explored several different methods, all of which rely on techniques from phrase-based MT, but which were trained on different types of parallel monolingual data.
+The first engine was trained on the text of Shakespeare’s plays, along with parallel modern English “translations” that were written to help students better understand Shakespeare's work.
+%A parallel corpus is extracted from these modern translations,
+%which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakespearean English.  
+We also developed several
+baseline systems which do not make use of this parallel text and instead rely on manually compiled dictionaries of expressions commonly found in Shakespearean English, or existing
+corpora of out-of-domain parallel monolingual text.
 
-We evaluate these models both through human judgments and standard evaluation metrics from the machine translation and paraphrase literature.  
-However, no previous work has investigated the ability of automatic
+We evaluate these models both through human judgments and standard evaluation metrics from the Machine Translation (MT) and Paraphrase literature, however no previous work has investigated the ability of automatic
 evaluation metrics to capture the notion of writing style.  
 We show that previously proposed metrics do not provide the complete picture of a system's performance when the task is to generate paraphrases
-targeting a specific style of writing.  We therefore propose two new metrics for evaluating paraphrases targeting a specific style, and 
-show that these metrics correlate well with human judgments.
+targeting a specific style of writing.  We therefore propose two new metrics for evaluating paraphrases targeting a specific style, and measure correlation with human judgments showing promising
+preliminary results.
 
-\begin{comment}
 Systems which are capable of automatically paraphrasing literary writing styles could be directly beneficial for educational applications.
@@
 we believe it should be possible to help make these plays more accessible to students of Shakespeare.
-\end{comment}
 
 \section{Shakespearean Paraphrasing}
-We use Shakespeare's plays as a testbed for the task of paraphrasing while targeting a specific writing style.  Because these plays are some of 
-the most highly-regarded examples of English literature and 
-are written in a style that is now 400 years out of date, many linguistic resources are available to help modern readers pick their way through 
-these Elizabethan texts. Among these are “translations” of the plays into colloquial English, and dictionaries that provide modern equivalents for specific words and phrases.
+We propose to use Shakespeare's plays as a testbed for the task of paraphrasing while targeting a specific writing style.  Because these plays are some of the
+highest regarded examples of English literature and are also very unique in style, many linguistic resources are available such as parallel corpora
+of modern translations and dictionaries of stylistically representative words and their modern equivalents.
 
-We compare 3 different stylistic paraphrase systems targeting Shakespearean English which rely on different types of linguistic resources. 
-One leverages parallel “translations”, another exploits dictionary resources, and a third relies on modern, out-of-domain monolingual parallel data and an in-domain corpus.
+We compare 3 different stylistic paraphrase systems targeting Shakespearean English which vary in the resources they assume access to.
+One which leverages parallel corpora of modern translations, another which makes use
+of dictionaries of stylistically representative expressions, and another which utilizes out-of-domain monolingual parallel data.
 
@@
 
-To generate paraphrases, we apply a typical phrase-based statistical machine translation pipeline, performing
+To generate paraphrases, we apply a typical phrase-based Statistical Machine Translation pipeline, performing
 word alignment on the data described in table \ref{corpus_stats} using GIZA++ \cite{Och03}, then extracting phrase pairs and performing decoding using Moses \cite{Koehn07}.
@@
 Several dictionaries of stylistically representative words of Shakespearean English and their modern equivalents are available on the web.  
-These dictionaries can be used to define a translation model which can be used in combination with a language model as in standard phrase-based machine
-translation.
+These dictionaries can be used to define a translation model which can be used in combination with a language model as in standard phrase-based Machine
+Translation.
 
@@
   \end{center}
-  \caption{Descriptions of various systems for Shakespearean paraphrase.  {\em Romeo and Juliet} is held out for testing.}
+  \caption{Descriptions of various systems for Shakespearean Paraphrase.  {\em Romeo and Juliet} is held out for testing.}
   \label{systems}
@@
   \end{center}
-  \caption{Various Shakespearean paraphrase systems compared using BLEU and PINC.  A brief description of each system is presented in table \ref{systems}.}
+  \caption{Various Shakespearean Paraphrase systems compared using BLEU and PINC.  A brief description of each system is presented in table \ref{systems}.}
   \label{bleupinc}
@@
       \hline
-      %Terminator 2 & Terminator & My mission is to protect you. & my affair is to keep you . \\
+      Terminator 2 & Terminator & My mission is to protect you. & my affair is to keep you . \\
       %\hline
@@
 \\
-      %\hline
-      %Terminator 2 & Terminator & Skynet begins to learn at a geometric rate.
+      \hline
+      Terminator 2 & Terminator & Skynet begins to learn at a geometric rate.
 ...
@@
 \\
-      %\hline
+      \hline
     \end{tabular}
@@
 These results are roughly in line with the automatic evaluation metrics presented in figure \ref{bleupinc}, however we also see several important
-trends which are not apparent from the automatic evaluation.
+trends which are not apparent from the automatic metrics.
 Although the video baseline achieves the highest semantic adequacy in the human evaluation, its BLEU score
@@
 We trained both the logistic regression and cosine similarity evaluation metrics using the original Shakespeare plays and modern translations as
-the source and target corpus respectively (holding out {\em Romeo and Juliet}), then measured Pearson's Correlation Coefficient between the automatic
-evaluation metrics and human judgments described in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.
+the source and target corpus respectively (holding out Romeo and Juliet), then measured Pearson's Correlation Coefficient between the automatic
+evaluation metrics and human judgments reported in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.
 
@@
     \hline
-    style & Logistic regression & 0.47 \\
+    style & Maximum Entropy & 0.47 \\
     \hline
@@
 
-Both the cosine and logistic regression style metrics achieve the highest overall correlation with human writing style judgments, with the logistic regression style score performing best.
+Both the Cosine and Maximum Entropy style metrics achieve the highest overall correlation with human writing style judgments, with the Maximum Entropy style score performing significantly better.
 
-We note that overall the automatic metrics tend to agree with agree with human judgments as displayed in figure \ref{style_metrics}.\footnote{
+Finally we note that overall the automatic metrics tend to agree with agree with human judgments as displayed in figure \ref{style_metrics}.\footnote{
   Although the automatic style metrics rate the dictionary system higher than the video corpus baseline, both systems have very comparable
@@
 \section{Translating Shakespeare's Plays to Modern English}
-Finally we preform a preliminary evaluation on the task of automatically translating Shakespeare's plays into modern English.  Success at this task could have immediate
+Finally we preform a preliminary evaluation of the task of automatically translating Shakespeare's plays into modern English.  Success at this task could have immediate
 benefits to students, as well as translators of Shakespeare's plays into modern English.
@@
 
-These results suggest that in comparison to the dictionary and video corpus baselines, 
-our system trained on modern translations generates a large number of paraphrases which match the target style.
+The results suggest that in comparison to the dictionary and video corpus baselines, 
+our system trained on modern translations generates diverse paraphrases which match the target style.
 Note that the paraphrase system 
@@
 \section{Related Work}
+Although no previous work has investigated paraphrasing modern text into Shakespearean English, or the more general task of paraphrasing while targeting a specific writing
+style, we highlight several strands of related work.
+
 Much previous work has addressed the task of automatically generating paraphrases \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05,Callison-Burch08,Kok10}.  
@@
 automatic metrics specifically for evaluating paraphrases \cite{chen11,Callison-Burch08b,liu10}.
-We are not aware, however, of any work that has addressed the task of generating or evaluating
+We are not aware, however, of any previous work that has addressed the task of generating or evaluating
 paraphrases targeting a specific style of writing.
@@
 Perhaps most relevant, however, is recent work autoatic generation of rhythmic poetry \cite{Greene10}.  This work focuses on automatically generating and translating
-poetry in an appropriate meter (e.g. iambic pentameter) using finite-state transducers, however does not investigate the task of paraphrase.  Their generation system
+poetry in an appropriate meter (e.g. iambic pentameter) using finite-state transducers, however doesn't address the issue of paraphrase.  Their generation system
 is trained on Shakespeare's sonnets, and they investigate the task of automatically translating Dante's Divine Comedy from Italian to English.
@@
 metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivalence with writing style giving an incomplete picture of which systems
-perform better according to each criteria.
+perform better according to each of these criteria.
 
 To address this problem, we have introduced two new metrics for evaluating writing style.
-We measured correlation between automatic metrics and human judgments, and showed
-that our new metrics have better correlation with human judgments than existing metrics in the context of our task.
+We measured correlation between automatic metrics and human judgments in the context of paraphrasing writing style, and showed
+that our new metrics have better correlation with human judgments than existing metrics in the context of our data.
 While this evaluation is limited to one specific style of writing, we are optimistic that these or similar metrics will also perform well when
@@
 
-Finally, we applied these automatic evaluation metrics in an initial investigation into the task of translating Shakespeare's plays into modern English.
-We plan to translate the remaining 20 of Shakespeare's plays, which could be beneficial to students
-of Shakespeare and also to human translators.
+Finally, we applied these automatic evaluation metrics to an initial investigation into the task of translating Shakespeare's plays into modern English.
+We plan to translate the remaining 20 of Shakespeare's plays into modern English, which could be beneficial to students
+of Shakespeare's plays and also to human translators.
 

### 2012-08-31 paper/paper.tex

--- 2012-08-31 paper/paper.tex
@@
 \begin{enumerate}
-  \item Help authors of technical documents to adhere to appropriate stylistic guidelines, or allow writers to automatically “upscale” an email before sending it.
-  \item Enable non-specialists to better understand information in legal or medical documents by translating ``legalese'' and medical jargon into ordinary English.  
-  \item Benefit educational applications:
+  \item Help authors of technical documents to adhere to appropriate stylistic guidelines.  
+  \item Enable average people to better consume information by translating legalese or medical jargon into nontechnical English.  
+  \item Benefit educational applications, allowing students to:
     \begin{enumerate}
-    \item Students studying a specific literary style could benefit from access to \emph{modern English} versions of works by authors they are studying.
-    \item Automatic register transformations could help students to experiment with writing in the style of the authors they are studying.
+    \item Access \emph{modern English} versions of works by authors they are studying.
+    \item Experiment with writing in the style of an author they are studying.
     \end{enumerate}
@@
 
-In this paper, we investigate the task of automatic paraphrasing when targeting a writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
-We exploit modern translations of 17 plays written to help students better understand Shakespeare's work.  A parallel corpus is extracted from these modern translations,
-which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakespearean English.  In addition we develop several
-baseline systems which do not make use of this source of parallel text and instead rely on manually compiled dictionaries of expressions commonly found in Shakespearean English, or out of
-domain parallel monolingual text gathered through Amazon's Mechanical Turk \cite{chen11}.
+In this paper, we investigate the task of automatic paraphrasing techniques that target a particular writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
+We explored several different methods, all of which rely on techniques from phrase-based MT, but which were trained on different types of parallel monolingual data.
+The first engine was trained on the text of Shakespeare’s plays, along with parallel modern English “translations” that were written to help students better understand Shakespeare's work.
+%A parallel corpus is extracted from these modern translations,
+%which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakespearean English.  
+We also developed several
+baseline systems which do not make use of this parallel text and instead rely on manually compiled dictionaries of expressions commonly found in Shakespearean English, or existing
+corpora of out-of-domain parallel monolingual text.
 
-We evaluate these models both through human judgments and standard evaluation metrics from the machine translation and paraphrase literature.  
-However, no previous work has investigated the ability of automatic
+We evaluate these models both through human judgments and standard evaluation metrics from the Machine Translation (MT) and Paraphrase literature, however no previous work has investigated the ability of automatic
 evaluation metrics to capture the notion of writing style.  

### 2012-08-31 paper/paper.tex
more of bill's feedback

@@
 are written in a style that is now 400 years out of date, many linguistic resources are available to help modern readers pick their way through 
-these Elizabethan texts. Among these are “translations” of the plays into colloquial English, and dictionaries that provide modern equivalents for specific words and phrases.
+these Elizabethan texts. Among these are “translations” of the plays into colloquial English, as well as dictionaries that provide modern equivalents for archaic words and phrases.
 
@@
 For this purpose we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}, and
-additional translations of 8 of these plays from from \url{http://enotes.com}.
+additional translations of 8 of these plays from \url{http://enotes.com}.
 
@@
 original text; the Sparknotes paraphrases yield a BLEU score of 24.67, whereas the Enotes paraphrases produce a much higher BLEU of 52.30 reflecting their strong similarity to the original texts.
-These results are summarized in table \ref{corpus_stats}.
+These results are summarized in Table \ref{corpus_stats}.
 
@@
 
-To generate paraphrases, we apply a typical phrase-based statistical machine translation pipeline, performing
+To generate paraphrases, we applied a typical phrase-based statistical MT pipeline, performing
 word alignment on the data described in table \ref{corpus_stats} using GIZA++ \cite{Och03}, then extracting phrase pairs and performing decoding using Moses \cite{Koehn07}.
+
+For evaluation purposes, the parallel text of one play, Romeo and Juliet, was held out of the training corpus for this system and the baseline systems described in the following section.
 
@@
 Phrase-based translation has been demonstrated as an effective approach to paraphrasing \cite{quirk04,chen11}.  However, this approach does require the existence of
-parallel corpora, resources which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches in order to help
-quantify the benefit of access to parallel text in the source and target styles.
+parallel corpora of aligned phrases and sentences, resources which may not be available for many writing styles that we might wish to target.
+For this reason we were motivated to investigate alternative approaches in order to help
+quantify how critical this type of parallel data is for the task of stylistic paraphrasing.
 
@@
 Several dictionaries of stylistically representative words of Shakespearean English and their modern equivalents are available on the web.  
-These dictionaries can be used to define a translation model which can be used in combination with a language model as in standard phrase-based machine
-translation.
+These dictionaries can be used to define a translation model which can be used in combination with a language model as in standard phrase-based MT.
 
@@
 We obtained the conditional probabilities for each translation according to the n-gram back-off model built from 36 of Shakespeare's 
-plays ({\em Romeo and Juliet} was held out for testing) using the SRILM toolkit \cite{Stolcke02}, 
+plays using the SRILM toolkit \cite{Stolcke02}, 
 normalizing the probabilities for each source phrase, for example $p(\text{PERCHANGE}|\text{maybe}) = \frac{0.0000790755}{0.00026264791} = 0.30107035689$.
@@
 As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
-\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this modern, out of domain parallel text, with an in-domain
-language model consisting of Shakespeare's 36 plays (again, holding out {\em Romeo and Juliet} for testing), applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
+\cite{Snow08} to caption the action in short video segements \cite{chen11}.  We combined a phrase table extracted from this modern, out of domain parallel text, with an in-domain
+language model consisting of Shakespeare's 36 plays, applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
 Although this monolingual parallel data does not include text in the target writing style,
@@
 \label{human_evaluation}
-Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is initially unclear how well the BLEU and PINC
+Figure \ref{bleupinc} provides some insight into the performance of the various systems, but it is initially unclear how well the BLEU and PINC
 automatic evaluation metrics perform when applied to evaluating paraphrases that target a specific style of writing.  BLEU and PINC have previously
 been shown to have high correlation with human judgments of semantic adequacy and lexical dissimilarity of paraphrase candidates, 
-but no corresponding work exists for paraphrasing models that target a specific style of writing.
+but the implications of this for the more specialized task of stylistic paraphrasing are unclear.
 
@@
 We trained both the logistic regression and cosine similarity evaluation metrics using the original Shakespeare plays and modern translations as
-the source and target corpus respectively (holding out {\em Romeo and Juliet}), then measured Pearson's Correlation Coefficient between the automatic
+the source and target corpus respectively, then measured Pearson's Correlation Coefficient between the automatic
 evaluation metrics and human judgments described in \S \ref{human_evaluation}.  These results are reported in table \ref{correlation}.
@@
 As can be seen in table \ref{correlation}, the correlation between semantic adequacy and BLEU appears smaller than that reported in previous work \cite{chen11}.  Presumably this is
-due to the conflation of stylistic differences and semantic adequacy discussed discussed in \S \ref{human_evaluation}.  However it also appears 
+due to the conflation of stylistic differences and semantic adequacy discussed in \S \ref{human_evaluation}.  However it also appears 
 that the correlation between BLEU and human style judgments is too low to be of practical use for evaluating style.
@@
 
-We note that overall the automatic metrics tend to agree with agree with human judgments as displayed in figure \ref{style_metrics}.\footnote{
+We note that overall the automatic metrics tend to agree with agree with human judgments as displayed in Figure \ref{style_metrics}.\footnote{
   Although the automatic style metrics rate the dictionary system higher than the video corpus baseline, both systems have very comparable
@@
 \section{Conclusions}
-We have presented the first investigation into the task of automatic paraphrasing while targeting a specific writing style.  We proposed Shakespeare's plays and their
-modern translations as a tesbed for this task, and developed a series of paraphrase systems targeting Shakespearean English.  We showed that while existing evaluation
-metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivalence with writing style giving an incomplete picture of which systems
-perform better according to each criteria.
+We have presented the first investigation into the task of automatic paraphrasing while targeting a specific writing style.  Using Shakespeare's plays and their
+modern translations as a tesbed for this task, we developed a series of paraphrase systems targeting Shakespearean English.  We showed that while existing evaluation
+metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivalence with writing style and thus gives an incomplete picture of 
+system performance on these different dimensions.
 
-To address this problem, we introduced two new metrics for evaluating writing style, one of which is based on cosine similarity and another based on logistic regression.
+To address this problem, we introduced two new metrics for evaluating writing style, one based on cosine similarity and the other based on logistic regression.
 We measured correlation between automatic metrics and human judgments, and showed

### 2012-08-31 paper/paper.tex
added section on LM style metric.  still need to incorporate in other sections, and compute aggregate scores.

@@
 
+\subsection{Language Model Style Metric}
+Another approach is to build seperate language models for text in the target style and outside the style, and apply Bayes' rule to estimate
+the probability that a particular sentence was generated based on the style or not:
+\begin{eqnarray*}
+P(\text{style}=\text{target}|\text{sentence}) 
+& = & \frac{P_\text{LM}(\text{sentence}|\text{target}) P(\text{target})}{P(\text{sentence})} \\
+& = & \frac{P_\text{LM}(\text{sentence}|\text{target}) \times 0.5}{P_\text{LM}(\text{sentence}|\text{target}) \times 0.5 + P_\text{LM}(\text{sentence}|\text{source}) \times 0.5} \\
+& = & \frac{P_\text{LM}(\text{sentence}|\text{target})}{P_\text{LM}(\text{sentence}|\text{target}) + P_\text{LM}(\text{sentence}|\text{source})} \\
+\end{eqnarray*}
+
+That is the probability that a sentence was generated according to the target style is simply it's probability according to the target language model divided by the sum of it's
+probability according to the source and target language models.
+
 \subsection{Logistic Regression Style Metric}
@@
   \begin{center}
-  \begin{tabular}{|l|l|r|}
+  \begin{tabular}{|l|l|r|r|}
     \hline
-    & & Pearson's $\rho$ \\
+    & & $\rho$ (Annotator 1) & $\rho$ (Annotator 2) \\
     \hline
     \hline
-    semantic adequacy & BLEU & 0.35 \\
+    semantic adequacy & BLEU & 0.35 & 0.31 \\
     \hline
-    dissimilarity & PINC & 0.78 \\
+    dissimilarity & PINC & 0.78 & 0.82 \\
     \hline
-    style & BLEU & 0.07 \\
+    style & BLEU & 0.07 & 0.06 \\
     \hline
-    style & PINC & 0.20 \\
+    style & PINC & 0.20 & 0.45 \\
     \hline
-    style & Cosine & 0.37 \\
+    style & Cosine & 0.37 & 0.41 \\
     \hline
-    style & Logistic regression & 0.47 \\
+    style & LM & 0.45 & 0.48 \\
+    \hline
+    style & Logistic regression & 0.47 & 0.48 \\
     \hline
@@
   \end{center}
-  \caption{Correlation between various human judgments and automatic evaluation metrics}
+  \caption{Correlation between various human judgments and automatic evaluation metrics.  Pearson's correlation coefficient is displayed
+  between the automatic metrics and human judgements from each annotator.}
   \label{correlation}

### 2012-09-01 paper/paper.tex
minor changes
Changed the title, added to the conclusions, and incorporated some of bill's changes to the abstract

@@
 %\title{“Be super careful on March 15” (“Beware the ides of March”) \\ A Case Study in Paraphrase Targeting Writing Styles}
-\title{``A rose by any other name would smell as sweet'': \\ A Case Study in Paraphrase Targeting Writing Styles}
+%\title{``A rose by any other name would smell as sweet'': \\ A Case Study in Paraphrase Targeting Writing Styles}
 %for authors: in case of more than four author names ref. to commented line below 
 %\author{$Annie~SMITH^{1, 2}~~~LI~Xiao Dong^{1, 3}$\\$~~~Third~Author^{1, 2}~~~Fourth~Author^{1, 3}~~~ Fifth~Author^{2, 3}$\\
+\title{Paraphrasing for Style}
 \author{$Author1^{1, 2}~~~Author2^{1, 3}$\\
@@
 %style.  
-We show that even with a relatively small amount of parallel training data available, it is
-possible to learn paraphrase models which capture stylistic phenomenon, and these models outperform
+We show that even with a relatively small amount of parallel training data, it is
+possible to learn paraphrase models which capture stylistic phenomena, and these models outperform
 baselines based on dictionaries and out-of-domain parallel text.
@@
     \hline
-    style & Logistic regression & 0.47 & 0.48 \\
+    style & Logistic regression & 0.47 & 0.47 \\
     \hline
@@
 Finally, we applied these automatic evaluation metrics in an initial investigation into the task of translating Shakespeare's plays into modern English.
+
+We have shown that access to even a small amount of parallel text produces paraphrase systems 
+capable of generating a large number of stylistically appropriate paraphrases which preserving the meaning of the input text.  
+Our paraphrase systems targeting Shakesperean English could be benefical for educational applications, for example helping to
+make Shakespeare's work accessable to a broader audience.
+Future work could investigate stylistic paraphrasing in other domains, such as paraphrasing emails into formal documents, or
+translating legal documents into nontechnical English. 
 %We plan to translate the remaining 20 of Shakespeare's plays, which could be beneficial to students

### 2012-09-01 paper/paper.tex
added citations

@@
 There is a significant literature in sentence compression aimed at modeling the first of these, length: 
-producing meaning-preserving alternations that reduce the length of the input string {\bf TODO:} [citations].
+producing meaning-preserving alternations that reduce the length of the input string \cite{Chandrasekar96,Vanderwende07,Yatskar10}.
 However, we know of no previous work aimed at modeling meaning-preserving transformations that systematically transform the register or style of an input string. 

### 2012-09-01 paper/paper_weichange.tex

--- 2012-08-31 paper/paper.tex
@@
 %\title{“Be super careful on March 15” (“Beware the ides of March”) \\ A Case Study in Paraphrase Targeting Writing Styles}
-\title{``A rose by any other name would smell as sweet'': \\ A Case Study in Paraphrase Targeting Writing Styles}
+%\title{``A rose by any other name would smell as sweet'': \\ A Case Study in Paraphrase Targeting Writing Styles}
+\title{A Case Study in Paraphrase Targeting Writing Styles}
 %for authors: in case of more than four author names ref. to commented line below 
@@
 %style.  
-We show that even with a relatively small amount of parallel training data available, it is
-possible to learn paraphrase models which capture stylistic phenomenon, and these models outperform
-baselines based on dictionaries and out-of-domain parallel text.
+We show that even with a relatively small amount of parallel training data, it is
+possible to learn paraphrase models which capture stylistic phenomea, and these models outperform
+baselines based on dictionaries and monolingual corpora.
 In addition we present an initial investigation into automatic evaluation metrics for paraphrasing writing style.
@@
 The same meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
-fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.
+fundamental to many natural language understanding tasks \cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.
 
@@
 There is a significant literature in sentence compression aimed at modeling the first of these, length: 
-producing meaning-preserving alternations that reduce the length of the input string {\bf TODO:} [citations].
-However, we know of no previous work aimed at modeling meaning-preserving transformations that systematically transform the register or style of an input string. 
+producing meaning-preserving alternations that reduce the length of the input string \cite{Knight02}.
+However, no previous work aimed at modeling meaning-preserving transformations that systematically transform the register or style of an input string. 
 Can we learn to reliably map from one form of language to another, transforming formal prose into a more colloquial form, or a casual email into a more formal equivalent?
@@
   \item Help authors of technical documents to adhere to appropriate stylistic guidelines.
-  \item Enable average people to better consume information by translating legalese or medical jargon into nontechnical English.  
+  \item Enable non-specialists to better consume information by translating legalese or medical jargon into nontechnical English.  
   \item Benefit educational applications, allowing students to:
@@
 
-We evaluate these models both through human judgments and standard evaluation metrics from the Machine Translation (MT) and Paraphrase literature, however no previous work has investigated the ability of automatic
-evaluation metrics to capture the notion of writing style.  
-We show that previously proposed metrics do not provide the complete picture of a system's performance when the task is to generate paraphrases
-targeting a specific style of writing.  We therefore propose two new metrics for evaluating paraphrases targeting a specific style, and 
+We evaluate these models both by human judges and by standard automated metrics from the Machine Translation (MT) and Paraphrase literature.
+However, we show that these previously proposed automatic metrics do not provide the complete picture of a system's performance when the task is to generate paraphrases
+targeting a specific style of writing.  No previous work has investigated the ability of automatic
+evaluation metrics to capture the notion of writing style.  We therefore propose three new automated metrics for evaluating paraphrases targeting a specific style, and 
 show that these metrics correlate well with human judgments.
@@
   \begin{center}
-    \begin{tabular}{|l|p{3in}|}
+    \begin{tabular}{|l|p{3.5in}|}
       \hline
@@
       \hline
-      16and7plays\_36LM & Phrase table extracted from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, again excluding R\&J.
-      Uses default Moses parameters. \\
+      16and7plays\_36LM & Phrase table is extracted from the parallel texts of 16 plays from Sparknotes plus 7 plays from Enotes.
+Language model is built from all 36 of Shakespeare's plays except R\&J.
+Uses default Moses parameters.
+\\
       \hline
@@
 
-\subsection{Language Model Style Metric}
-Another approach is to build seperate language models for text in the target style and outside the style, and apply Bayes' rule to estimate
-the probability that a particular sentence was generated based on the style or not:
-\begin{eqnarray*}
-P(\text{style}=\text{target}|\text{sentence}) 
-& = & \frac{P_\text{LM}(\text{sentence}|\text{target}) P(\text{target})}{P(\text{sentence})} \\
-& = & \frac{P_\text{LM}(\text{sentence}|\text{target}) \times 0.5}{P_\text{LM}(\text{sentence}|\text{target}) \times 0.5 + P_\text{LM}(\text{sentence}|\text{source}) \times 0.5} \\
-& = & \frac{P_\text{LM}(\text{sentence}|\text{target})}{P_\text{LM}(\text{sentence}|\text{target}) + P_\text{LM}(\text{sentence}|\text{source})} \\
-\end{eqnarray*}
-
-That is the probability that a sentence was generated according to the target style is simply it's probability according to the target language model divided by the sum of it's
-probability according to the source and target language models.
-
 \subsection{Logistic Regression Style Metric}
@@
 
+\subsection{Language Model Style Metric}
+\emph{TO ADD}
+
 \subsection{Evaluation}
@@
   \begin{center}
-  \begin{tabular}{|l|l|r|r|}
+  \begin{tabular}{|l|l|r|}
     \hline
-    & & $\rho$ (Annotator 1) & $\rho$ (Annotator 2) \\
+    & & Pearson's $\rho$ \\
     \hline
     \hline
-    semantic adequacy & BLEU & 0.35 & 0.31 \\
+    semantic adequacy & BLEU & 0.35 \\
     \hline
-    dissimilarity & PINC & 0.78 & 0.82 \\
+    dissimilarity & PINC & 0.78 \\
     \hline
-    style & BLEU & 0.07 & 0.06 \\
+    style & BLEU & 0.07 \\
     \hline
-    style & PINC & 0.20 & 0.45 \\
+    style & PINC & 0.20 \\
     \hline
-    style & Cosine & 0.37 & 0.41 \\
+    style & Cosine & 0.37 \\
     \hline
-    style & LM & 0.45 & 0.48 \\
-    \hline
-    style & Logistic regression & 0.47 & 0.48 \\
+    style & Logistic regression & 0.47 \\
     \hline
@@
   \end{center}
-  \caption{Correlation between various human judgments and automatic evaluation metrics.  Pearson's correlation coefficient is displayed
-  between the automatic metrics and human judgements from each annotator.}
+  \caption{Correlation between various human judgments and automatic evaluation metrics}
   \label{correlation}

### 2012-09-01 paper/paper.tex
switched to lmdiff5
Added wei's new numbers

@@
 We show that previously proposed metrics do not provide the complete picture of a system's performance when the task is to generate paraphrases
-targeting a specific style of writing.  We therefore propose two new metrics for evaluating paraphrases targeting a specific style, and 
+targeting a specific style of writing.  We therefore propose three new metrics for evaluating paraphrases targeting a specific style, and 
 show that these metrics correlate well with human judgments.
@@
 We compare 3 different stylistic paraphrase systems targeting Shakespearean English which rely on different types of linguistic resources. 
-One leverages parallel “translations”, another exploits dictionary resources, and a third relies on modern, out-of-domain monolingual parallel data and an in-domain corpus.
+One leverages parallel “translations”, another exploits dictionary resources, and a third relies on modern, out-of-domain monolingual parallel data and an in-domain language model.
 
@@
     \begin{tabular}{cc}
-      \includegraphics[width=2.4in]{figures/bleupinc1.pdf} & \includegraphics[width=2.4in]{figures/bleupinc2.pdf} \\
+      \includegraphics[width=2.4in]{figures/bleupinc1-crop.pdf} & \includegraphics[width=2.4in]{figures/bleupinc2-crop.pdf} \\
     \end{tabular}
@@
   \begin{center}
-    \includegraphics[width=5in]{figures/human_judgements.pdf}
+    \includegraphics[width=5in]{figures/human_judgements-crop.pdf}
   \end{center}
@@
 
-To help address this issue we propose two new automatic evaluation metrics whose goal is to measure the degree to which
-automatic paraphrases match the target style.  Both metrics assume existence of large corpora in both the source and
+To help address this issue we propose three new automatic evaluation metrics whose goal is to measure the degree to which
+automatic paraphrases match the target style.  These metrics assume existence of large corpora in both the source and
 target style, but do not require access to any parallel text, or human judgments.
 
-We present a preliminary evaluation of these metrics by measuring their correlation with human judgments, but
+We present a preliminary evaluation of the proposed metrics by measuring their correlation with human judgments, but
 it should be emphasized that we are only evaluating these metrics with respect to one specific style of writing.  We
@@
 \subsection{Cosine Similarity Style Metric}
-As a first approach to automatic evaluation of writing style, we propose a vector-space model of similarity between the system
+As a first approach to automatic evaluation of writing style, we present a vector-space model of similarity between the system
 output and a large corpus of text in both the source and target style.  The intuition behind this metric is that  a large ngram
@@
 \subsection{Language Model Style Metric}
-Another approach is to build seperate language models for text in the target style and outside the style, and apply Bayes' rule to estimate
+Another approach is to build a language model for text in the target style and a background language model from text outside the style, then apply Bayes' rule to estimate
 the probability that a particular sentence was generated based on the style or not:
@@
 \end{eqnarray*}
-
-That is the probability that a sentence was generated according to the target style is simply it's probability according to the target language model divided by the sum of it's
-probability according to the source and target language models.
 
@@
     \hline
-    style & LM & 0.45 & 0.48 \\
+    style & LM & 0.46 & 0.51 \\
     \hline
@@
   \begin{center}
-    \includegraphics[width=5in]{figures/style_metrics.pdf}
+    \includegraphics[width=5in]{figures/style_metrics-crop.pdf}
     \end{center}
@@
 \section{Translating Shakespeare's Plays to Modern English}
-Finally we perform a preliminary evaluation on the task of automatically translating Shakespeare's plays into modern English.  
+Finally we perform an evaluation on the task of automatically translating Shakespeare's plays into modern English.  
 %Success at this task could have immediate benefits to students, as well as translators of Shakespeare's plays into modern English.
@@
 Additionally, each system makes use of a language model constructed from the 16 modern translations, with {\em Romeo and Juliet} held out for testing.  
-510 lines from {\em Romeo and Juliet} were automatically translated into modern English using each system, and the aligned modern 
+100 lines from {\em Romeo and Juliet} were automatically translated into modern English using each system, and the aligned modern 
 translations were used as a reference when computing BLEU.  The results of evaluating each of the automatic evaluation metrics on this
-data are presented in Figure \ref{shakespeare_to_modern_automatic}.
+data are presented in Figure \ref{shakespeare_to_modern_automatic}, correlation of the automatic metrics with with human judgements are presented in 
+Figure \ref{correlation_s2m} and overall average human judgements are presented in Figure \ref{human_judgements}.
+
+\begin{table}
+  \begin{center}
+  \begin{tabular}{|l|l|r|}
+    \hline
+    & & $\rho$ (Annotator 1) \\
+    \hline
+    \hline
+    semantic adequacy & BLEU & 0.27 \\
+    \hline
+    dissimilarity & PINC & 0.79 \\
+    \hline
+    style & BLEU & 0.12 \\
+    \hline
+    style & PINC & 0.41 \\
+    \hline
+    style & Cosine & 0.37 \\
+    \hline
+    style & LM & 0.45 \\
+    \hline
+    style & Logistic regression & 0.46 \\
+    \hline
+  \end{tabular}
+  \end{center}
+  \caption{Correlation between human judgments and automatic evaluation metrics when paraphrasing Shakespeare's plays into modern prose.}
+  \label{correlation_s2m}
+\end{table}
+
+\begin{figure}[ht]
+  \begin{center}
+    \includegraphics[width=5in]{figures/human_judgements_s2m-crop.pdf}
+  \end{center}
+  \caption{Average human judgments translating Shakespeare's plays into modern English.} 
+  \label{human_judgements_s2m}
+\end{figure}
 
@@
 \begin{figure}
-  \includegraphics[width=5in]{figures/shakespeare_to_modern.pdf}
+  \includegraphics[width=5in]{figures/shakespeare_to_modern-crop.pdf}
   \caption{Automatic evaluation of paraphrasing Shakespeare's plays into modern English comparing a system based on parallel text (16plays\_16LM), 
@@
 
-To address this problem, we introduced two new metrics for evaluating writing style, one based on cosine similarity and the other based on logistic regression.
+To address this problem, we introduced three new metrics for evaluating writing style, one based on cosine similarity one based on
+language models, and the third based on logistic regression.
 We measured correlation between automatic metrics and human judgments, and showed
@@
 
-Finally, we applied these automatic evaluation metrics in an initial investigation into the task of translating Shakespeare's plays into modern English.
+Finally, we applied these automatic evaluation metrics in an investigation into the task of translating Shakespeare's plays into modern English.
 

### 2012-09-01 paper/figures/plot_style.R

@@ -11,15 +11,16 @@
 pdf('style_metrics.pdf', width=8, height=5)
 
 systems = c('16plays36LM', 'Dictionary', 'Video Baseline')
-metrics = c('Cosine Similarity', 'Logistic Regression')
+metrics = c('Cosine Similarity', 'Language Model', 'Logistic Regression')
 
 barplot(t(rbind(
 	 c(0.512979241631, 0.491599098577, 0.480059827357),
+	 c(0.50886, 0.30984, 0.21186),
 	 c(0.701862536235, 0.50375691204, 0.456308085791))),
 	names.arg=metrics, beside=TRUE)
 
 title("Average Style Metrics")
 
-legend("topright", legend=systems, fill=(gray.colors(n=3)))
+legend("topleft", legend=systems, fill=(gray.colors(n=3)))
 
 dev.off()

### 2012-09-01 paper/figures/shakespere_to_modern.R

@@ -1,14 +1,15 @@
 systems = c('16plays_16LM', 'Dictionary', 'Video Baseline')
-metrics = c('BLEU', 'PINC', 'Style-MaxEnt', 'Style-Cosine')
+metrics = c('BLEU', 'PINC', 'Style-MaxEnt', 'Style-LM', 'Style-Cosine')
 BLEU = c(27.79, 19.79, 24.23)
 PINC = c(48.70, 39.94, 4.09)
 sMaxEnt = c(71.99, 54.92, 44.02)
 sCosine = c(48.30, 46.11, 44.04)
+sLM = c(64.96, 33.59, 10.25)
 
 pdf('shakespeare_to_modern.pdf', width=8, height=5)
 
 barplot(
-	t(rbind(BLEU, PINC, sMaxEnt, sCosine)),
+	t(rbind(BLEU, PINC, sMaxEnt, sLM, sCosine)),
 	names.arg=metrics, beside=TRUE)
 title("Automatic Evaluation of Paraphrasing Shakespeare's plays to Modern English")
 

### 2012-09-01 python_wei_2/PINC_document.py
-> modern

@@ -1,0 +1,98 @@
+from __future__ import division
+from collections import *
+
+import io
+import sys
+
+def intersect (list1, list2) :
+    cnt1 = Counter()
+    cnt2 = Counter()
+    for tk1 in list1:
+        cnt1[tk1] += 1
+    for tk2 in list2:
+        cnt2[tk2] += 1    
+    inter = cnt1 & cnt2
+    return len(list(inter.elements()))
+
+def pinc ( ssent, csent) :
+    s1grams = ssent.split(" ")
+    c1grams = cline.split(" ")
+    
+    s2grams = []
+    c2grams = []
+    s3grams = []
+    c3grams = []
+    s4grams = []
+    c4grams = []
+        
+    for i in range(0, len(s1grams)-1) :
+        if i < len(s1grams) - 1:
+            s2gram = s1grams[i] + " " + s1grams[i+1]
+            s2grams.append(s2gram)
+        if i < len(s1grams)-2:
+            s3gram = s1grams[i] + " " + s1grams[i+1] + " " + s1grams[i+2]
+            s3grams.append(s3gram)
+        if i < len(s1grams)-3:
+            s4gram = s1grams[i] + " " + s1grams[i+1] + " " + s1grams[i+2] + " " + s1grams[i+3]
+            s4grams.append(s4gram)
+            
+    for i in range(0, len(c1grams)-1) :
+        if i < len(c1grams) - 1:
+            c2gram = c1grams[i] + " " + c1grams[i+1]
+            c2grams.append(c2gram)
+        if i < len(c1grams)-2:
+            c3gram = c1grams[i] + " " + c1grams[i+1] + " " + c1grams[i+2]
+            c3grams.append(c3gram)
+        if i < len(c1grams)-3:
+            c4gram = c1grams[i] + " " + c1grams[i+1] + " " + c1grams[i+2] + " " + c1grams[i+3]
+            c4grams.append(c4gram)
+
+    if len(c1grams) > 0 :
+        score  = 1 - intersect(s1grams, c1grams) / len(c1grams)
+        #print "score1", score
+    if len(c2grams) > 0 :
+        score += 1 - intersect(s2grams, c2grams) / len(c2grams)
+        #print "score2", score
+    if len(c3grams) > 0 :
+        score += 1 - intersect(s3grams, c3grams) / len(c3grams)
+        #print "score3", score   
+    if len(c4grams) > 0 :
[…]

### 2012-09-01 python_wei_2/add_scores_wei_lm.py

@@ -1,0 +1,493 @@
+#!/usr/bin/python
+
+import sys
+
+from scipy.stats.stats import pearsonr
+
+from PINC_BLEU import *
+from style_metric import *
+from lm_score import *
+
+def mean(values):
+    return sum(values, 0.0) / len(values)
+
+def corelation_human_human (filename1, filename2):
+
+    _16plays36_semantic_list_1 = []
+    _16plays36_dissim_list_1 = []
+    _16plays36_style_list_1 = []
+    _16plays36_overall_list_1 = []
+    phrase_semantic_list_1 = []
+    phrase_dissim_list_1 = []
+    phrase_style_list_1 = []
+    phrase_overall_list_1 = []
+    video_semantic_list_1 = []
+    video_dissim_list_1 = []
+    video_style_list_1 = []
+    video_overall_list_1 = []
+    
+    
+    _16plays36_semantic_list_2 = []
+    _16plays36_dissim_list_2 = []
+    _16plays36_style_list_2 = []
+    _16plays36_overall_list_2 = []
+    phrase_semantic_list_2 = []
+    phrase_dissim_list_2 = []
+    phrase_style_list_2 = []
+    phrase_overall_list_2 = []
+    video_semantic_list_2 = []
+    video_dissim_list_2 = []
+    video_style_list_2 = []
+    video_overall_list_2 = []
+
+    i = 0
+    for line in open(filename1):
+        line = line.strip()
+        if len(line.split('\t')) < 12 or i == 0:
+            i += 1
+            continue
+        (original, modern, _16plays36, phrase, video, _16plays36_semantic, _16plays36_dissim, _16plays36_style, _16plays36_overall, phrase_semantic, phrase_dissim, phrase_style, phrase_overall, video_semantic, video_dissim, video_style, video_overall) = line.split('\t')
+        _16plays36_semantic_list_1.append(float(_16plays36_semantic))
+        _16plays36_dissim_list_1.append(float(_16plays36_dissim))
+        _16plays36_style_list_1.append(float(_16plays36_style))
+        _16plays36_overall_list_1.append(float(_16plays36_overall))
+        phrase_semantic_list_1.append(float(phrase_semantic))
+        phrase_dissim_list_1.append(float(phrase_dissim))
+        phrase_style_list_1.append(float(phrase_style))
+        phrase_overall_list_1.append(float(phrase_overall))
+        video_semantic_list_1.append(float(video_semantic))
[…]

### 2012-09-01 python_wei_2/crawl_dictionary.py

@@ -1,0 +1,19 @@
+import re
+import urllib
+import string
+import time
+
+urlhead = "http://www.william-shakespeare.info/william-shakespeare-dictionary-"
+urltail = ".htm"
+
+for c in string.lowercase:
+    url = urlhead + c + urltail
+    print url
+    urlobject = urllib.urlopen(url)
+    lines = urllib.urlopen(url).readlines()
+    
+    
+    fOut = open('../dictionary/word_%s.htm' % c , 'w')
+    fOut.write("\n".join(lines))
+    fOut.close()
+    time.sleep(1)    

### 2012-09-01 python_wei_2/lm_score.py

@@ -1,0 +1,84 @@
+import subprocess
+import re
+import math
+
+### Modern -> Original ###
+lmoriginal2 = "/Users/weixu/Work/Shakespere/Shakespere/models/LMs/36plays_tokenized_lowercased.original.lm"    
+#lmoriginal = "/Users/weixu/Work/Shakespere/Shakespere/models/LMs/16plays_tokenized_lowercased.original.lm"    
+#lmmodern = "/Users/weixu/Work/Shakespere/Shakespere/models2/LM/16plays_tokenized_lowercased.modern.lm"    
+
+### Original -> Modern ###
+lmmodern = "/Users/weixu/Work/Shakespere/Shakespere/models/LMs/16plays_tokenized_lowercased.original.lm"    
+lmoriginal = "/Users/weixu/Work/Shakespere/Shakespere/models2/LM/16plays_tokenized_lowercased.modern.lm"    
+
+
+def logexpsum(logprobs):
+    m = max(logprobs)
+    return(m + math.log(sum([math.exp(x - m) for x in logprobs])))
+
+def sent_logprob (sent, lmfile) :
+    f = open('tmp_sent', 'w')
+    f.write(sent)
+    f.close()
+    p = subprocess.Popen(["/Users/weixu/Work/Shakespere/tools/srilm/lm/bin/macosx/ngram", "-lm" , lmfile, "-ppl" ,"tmp_sent"], shell=False, stderr=subprocess.PIPE, stdout=subprocess.PIPE).communicate()
+    output = p[0]
+    sentlen = re.search(r', (.*)words', output).group(1)
+    logprob = re.search(r'logprob= (.*) ppl=', output).group(1)
+    return {'sentlen':float(sentlen), 'logprob':float(logprob)}    
+    
+    
+def LMdiff (sent) :
+    logprob_lmoriginal = sent_logprob (sent, lmoriginal) ['logprob']
+    logprob_lmmodern   = sent_logprob (sent, lmmodern) ['logprob']
+    diff = logprob_lmoriginal - logprob_lmmodern
+    return diff
+
+def LMdiff2 (osent, msent) :
+    logprob_lmoriginal_o = sent_logprob (osent, lmoriginal) ['logprob']
+    logprob_lmoriginal_m = sent_logprob (msent, lmoriginal) ['logprob']
+    diff = logprob_lmoriginal_o - logprob_lmoriginal_m
+    return diff
+    
+    
[…]

### 2012-09-01 python_wei_2/maxent.py

@@ -1,0 +1,1734 @@
+# Added two functions for 'Classifier Trainer: megam'
+# - save trained model to file
+# - read model from file
+# 
+# Usage: replace 'maxent.py' in the nltk package
+# e.g. 
+# for Mac OS '/Library/Frameworks/Python.framework/Versions/2.7/lib/python2.7/site-packages/nltk/classify/maxent.py'
+
+# Natural Language Toolkit: Maximum Entropy Classifiers
+#
+# Copyright (C) 2001-2012 NLTK Project
+# Author: Edward Loper <edloper@gradient.cis.upenn.edu>
+#         Dmitry Chichkov <dchichkov@gmail.com> (TypedMaxentFeatureEncoding)
+# URL: <http://www.nltk.org/>
+# For license information, see LICENSE.TXT
+
+"""
+A classifier model based on maximum entropy modeling framework.  This
+framework considers all of the probability distributions that are
+empirically consistent with the training data; and chooses the
+distribution with the highest entropy.  A probability distribution is
+"empirically consistent" with a set of training data if its estimated
+frequency with which a class and a feature vector value co-occur is
+equal to the actual frequency in the data.
+
+Terminology: 'feature'
+======================
+The term *feature* is usually used to refer to some property of an
+unlabeled token.  For example, when performing word sense
+disambiguation, we might define a ``'prevword'`` feature whose value is
+the word preceding the target word.  However, in the context of
+maxent modeling, the term *feature* is typically used to refer to a
+property of a "labeled" token.  In order to prevent confusion, we
+will introduce two distinct terms to disambiguate these two different
+concepts:
+
+  - An "input-feature" is a property of an unlabeled token.
+  - A "joint-feature" is a property of a labeled token.
+
+In the rest of the ``nltk.classify`` module, the term "features" is
+used to refer to what we will call "input-features" in this module.
+
+In literature that describes and discusses maximum entropy models,
+input-features are typically called "contexts", and joint-features
+are simply referred to as "features".
+
+Converting Input-Features to Joint-Features
+-------------------------------------------
+In maximum entropy models, joint-features are required to have numeric
+values.  Typically, each input-feature ``input_feat`` is mapped to a
+set of joint-features of the form:
+
+|   joint_feat(token, label) = { 1 if input_feat(token) == feat_val
+|                              {      and label == some_label
+|                              {
+|                              { 0 otherwise
+
+For all values of ``feat_val`` and ``some_label``.  This mapping is
[…]

### 2012-09-01 python_wei_2/startServers.py

@@ -1,0 +1,21 @@
+#!/usr/bin/python
+
+import sys
+import re
+import time
+from subprocess import Popen
+
+for line in open(sys.argv[1]):
+    line = line.rstrip('\n')
+    (old, name, iniFile, port) = re.split(r'\s+', line)
+    if old == "0":
+        #pid = Popen(["nohup", "/homes/gws/aritter/mt/moses-web/bin/daemon.pl", "milkhog.cs.washington.edu", port, iniFile]).pid
+        pid = Popen(["/homes/gws/aritter/mt/moses-web/bin/daemon.pl", "milkhog.cs.washington.edu", port, iniFile]).pid
+    elif old == "2":
+        #pid = Popen(["nohup", "/homes/gws/aritter/mt/moses-web/bin/daemon_n13.pl", "rv-n13.cs.washington.edu", port, iniFile]).pid
+        pid = Popen(["/homes/gws/aritter/mt/moses-web/bin/daemon_n13.pl", "rv-n13.cs.washington.edu", port, iniFile]).pid
+    else:
+        pid = Popen(["nohup", "/homes/gws/aritter/mt/moses-web/bin/daemon_old.pl", "milkhog.cs.washington.edu", port, iniFile]).pid
+        #pid = Popen(["/homes/gws/aritter/mt/moses-web/bin/daemon_old.pl", "milkhog.cs.washington.edu", port, iniFile]).pid
+    #Sleep for a minute between starting up each version of the decoder (it takes a while to load files into memory)
+    time.sleep(60 * 4)

### 2012-09-01 python_wei_2/style_metric.py

@@ -1,0 +1,116 @@
+#!/usr/bin/python
+
+import nltk
+#nltk.config_megam('/home/aritter/local/bin/megam')
+nltk.config_megam('/usr/local/bin/megam')
+
+import sys
+import math
+import random
+
+MAX_NGRAM=6
+
+class StyleMetric:
+    source_vector = {}
+    target_vector = {}
+
+    training = []
+
+    def __init__(self, corpus_source, corpus_target):
+        #Read in Source Corpus
+        nlines = 0
+        for line in open(corpus_source):
+            #TODO: can use more data for training maxent model if more memory is available
+            line = line.strip()
+            words = nltk.word_tokenize(line)
+            sentenceDict = {}
+            for gram in range(1,MAX_NGRAM):
+                for i in range(len(words)-gram+1):
+                    ngram = " ".join(words[i:i+gram])
+                    self.source_vector[ngram] = 1
+                    #self.source_vector[ngram] = self.source_vector.get(ngram, 0) + 1
+                    sentenceDict[ngram] = 1
+                    #sentenceDict[ngram] = sentenceDict.get(ngram, 0) + 1.0
+            self.training.append((sentenceDict, 'source'))
+            nlines += 1
+
+        #Read in Target Corpus
+        nlines = 0
+        for line in open(corpus_target):
+            line = line.strip()
+            words = nltk.word_tokenize(line)
+            sentenceDict = {}
+            for gram in range(1,MAX_NGRAM):
+                for i in range(len(words)-gram+1):
+                    ngram = " ".join(words[i:i+gram])
+                    self.target_vector[ngram] = 1
+                    #self.target_vector[ngram] = self.target_vector.get(ngram, 0) + 1
+                    sentenceDict[ngram] = 1
+                    #sentenceDict[ngram] = sentenceDict.get(ngram, 0) + 1
+            self.training.append((sentenceDict, 'target'))
+            nlines += 1
+
+        #self.training = random.sample(self.training, 100)
+            
+#        for i in range(len(self.training)):
+#            t = {}
+#            for k in self.source_vector.keys() + self.target_vector.keys():
+#                #t[k] = self.training[i][0].get(k, 0.0)
+#                if self.training[i][0].has_key(k):
+#                    t[k] = 1
[…]

### 2012-09-01 paper/paper.tex
spellchecked

@@
 As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
-\cite{Snow08} to caption the action in short video segements \cite{chen11}.  We combined a phrase table extracted from this modern, out of domain parallel text, with an in-domain
+\cite{Snow08} to caption the action in short video segments \cite{chen11}.  We combined a phrase table extracted from this modern, out of domain parallel text, with an in-domain
 language model consisting of Shakespeare's 36 plays, applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
@@
 Another approach is to build a language model for text in the target style and a background language model from text outside the style, then apply Bayes' rule to estimate
-the probability that a particular sentence was generated based on the style or not:
+the posterior probability that a sentence was generated from the target language model:
 \begin{eqnarray*}
@@
   \caption{Correlation between various human judgments and automatic evaluation metrics.  Pearson's correlation coefficient is displayed
-  between the automatic metrics and human judgements from each annotator.}
+  between the automatic metrics and human judgments from each annotator.}
   \label{correlation}
@@
 translations were used as a reference when computing BLEU.  The results of evaluating each of the automatic evaluation metrics on this
-data are presented in Figure \ref{shakespeare_to_modern_automatic}, correlation of the automatic metrics with with human judgements are presented in 
-Figure \ref{correlation_s2m} and overall average human judgements are presented in Figure \ref{human_judgements}.
+data are presented in Figure \ref{shakespeare_to_modern_automatic}, correlation of the automatic metrics with with human judgments are presented in 
+Figure \ref{correlation_s2m} and overall average human judgments are presented in Figure \ref{human_judgements}.
 
@@
 We have presented the first investigation into the task of automatic paraphrasing while targeting a specific writing style.  Using Shakespeare's plays and their
-modern translations as a tesbed for this task, we developed a series of paraphrase systems targeting Shakespearean English.  We showed that while existing evaluation
+modern translations as a testbed for this task, we developed a series of paraphrase systems targeting Shakespearean English.  We showed that while existing evaluation
 metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivalence with writing style and thus gives an incomplete picture of 
@@
 capable of generating a large number of stylistically appropriate paraphrases which preserving the meaning of the input text.  
-Our paraphrase systems targeting Shakesperean English could be benefical for educational applications, for example helping to
-make Shakespeare's work accessable to a broader audience.
+Our paraphrase systems targeting Shakespearean English could be beneficial for educational applications, for example helping to
+make Shakespeare's work accessible to a broader audience.
 Future work could investigate stylistic paraphrasing in other domains, such as paraphrasing emails into formal documents, or

### 2012-09-01 paper/paper.tex
removed the weird paragraph

@@
 \subsection{Language Model Style Metric}
-Another approach is to build a language model for text in the target style and a background language model from text outside the style, then apply Bayes' rule to estimate
+Another approach is to build a language model from a corpus of text in the target style and a background language model from text outside the style, then apply Bayes' rule to estimate
 the posterior probability that a sentence was generated from the target language model:
@@
 data are presented in Figure \ref{shakespeare_to_modern_automatic}, correlation of the automatic metrics with with human judgments are presented in 
-Figure \ref{correlation_s2m} and overall average human judgments are presented in Figure \ref{human_judgements}.
+Table \ref{correlation_s2m} and overall average human judgments are presented in Figure \ref{human_judgements_s2m}.
 
@@
 vocabulary words in Shakespeare's plays which result in very few matching source phrases in the video baseline's phrase table.
-
-While we have yet to perform a human evaluation on the task of paraphrasing Shakespeare's plays into modern English, 
-informal inspection of the resulting translations is encouraging.  Several automatic paraphrases into modern English are presented in Table \ref{modern_examples}.
+Several automatic paraphrases into modern English are presented in Table \ref{modern_examples}.
 

### 2012-09-01 paper/figures/shakespere_to_modern.R

@@ -1,5 +1,5 @@
 systems = c('16plays_16LM', 'Dictionary', 'Video Baseline')
-metrics = c('BLEU', 'PINC', 'Style-MaxEnt', 'Style-LM', 'Style-Cosine')
+metrics = c('BLEU', 'PINC', 'Style-LR', 'Style-LM', 'Style-Cosine')
 BLEU = c(27.79, 19.79, 24.23)
 PINC = c(48.70, 39.94, 4.09)
 sMaxEnt = c(71.99, 54.92, 44.02)

### 2012-09-02 paper/paper.tex
fixed a bunch of conflicting information...

@@
   \item Help authors of technical documents to adhere to appropriate stylistic guidelines.  
-  \item Enable average people to better consume information by translating legalese or medical jargon into nontechnical English.  
+  \item Enable non-experts to better consume technical information, for example by translating legalese or medical jargon into nontechnical English.  
   \item Benefit educational applications, allowing students to:
@@
 
-In this paper, we investigate the task of automatic paraphrasing techniques that target a particular writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
+In this paper, we investigate the task of automatic paraphrasing while targeting a particular writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
 We explored several different methods, all of which rely on techniques from phrase-based MT, but which were trained on different types of parallel monolingual data.
-The first engine was trained on the text of Shakespeare’s plays, along with parallel modern English “translations” that were written to help students better understand Shakespeare's work.
+The first system was trained on the text of Shakespeare’s plays, along with parallel modern English “translations” that were written to help students better understand Shakespeare's work.
 %A parallel corpus is extracted from these modern translations,
 %which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakespearean English.  
-We also developed several
-baseline systems which do not make use of this parallel text and instead rely on manually compiled dictionaries of expressions commonly found in Shakespearean English, or existing
+We also developed several baselines which do not make use of this parallel text and instead rely on manually compiled dictionaries of expressions commonly found in Shakespearean English, or existing
 corpora of out-of-domain parallel monolingual text.
@@
 For instance, if we look at the modern English word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations. 
-We obtained the conditional probabilities for each translation according to the n-gram back-off model built from 36 of Shakespeare's 
+We obtained the probabilities for each translation according to the n-gram back-off model built from 36 of Shakespeare's 
 plays using the SRILM toolkit \cite{Stolcke02}, 
@@
 input, its BLEU is lower than that of the modern translations.  Secondly, it seems apparent that the systems whose parameters are tuned using Minimum Error Rate Training
-tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, while not improving BLEU scores on the test data.  Finally
+tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, while not improving BLEU on the test data.  Finally
 we note that using the larger target language model seems to yield a slight improvement in BLEU score.
@@
 \subsection{Examples}
-Several example paraphrases of lines from {\em Romeo and Juliet} and several Hollywood movies, generated by the top performing system according to BLEU and PINC, are presented in table \ref{examples}.
+Example paraphrases of lines from {\em Romeo and Juliet} and several Hollywood movies, generated by the top performing system according to BLEU and PINC, are presented in table \ref{examples}.
 
@@
 Figure \ref{bleupinc} provides some insight into the performance of the various systems, but it is initially unclear how well the BLEU and PINC
-automatic evaluation metrics perform when applied to evaluating paraphrases that target a specific style of writing.  BLEU and PINC have previously
+automatic evaluation metrics perform when applied to paraphrases that target a specific style of writing.  BLEU and PINC have previously
 been shown to have high correlation with human judgments of semantic adequacy and lexical dissimilarity of paraphrase candidates, 
@@
 
-These results are roughly in line with the automatic evaluation metrics presented in Figure \ref{bleupinc}.  However we also see several important
+These results are roughly in line with the automatic metrics presented in Figure \ref{bleupinc}.  However we also see several important
 trends which are not apparent from the automatic evaluation.
@@
 semantic adequacy with writing style.  When comparing various systems using automatic metrics, it would seem useful
-to separate the effects caused by these two distinct criteria.  We would like our automatic evaluation metrics to be able to distinguish
+to separate the effects caused by these two distinct criteria.  We would like our automatic evaluation metrics to distinguish
 between a system which generates perfect paraphrases which do not match the target style of writing versus a system which
@@
 Another approach is to build a language model from a corpus of text in the target style and a background language model from text outside the style, then apply Bayes' rule to estimate
-the posterior probability that a sentence was generated from the target language model:
+the posterior probability that a sentence was generated from the target language model\footnote{
+Here we assume an uninformative prior, that is $P(\text{source}) = P(\text{target}) = 0.5$.
+}:
 \begin{eqnarray*}
@@
 \subsection{Logistic Regression Style Metric}
-We also consider an approach to measuring style which is based on logistic regression as opposed to cosine similarity.
+We also consider an approach to measuring style which is based on logistic regression.
 %We also consider a logistic Regression based approach as an alternative to cosine similarity.
@@
 \subsection{Evaluation}
-We trained both the logistic regression and cosine similarity evaluation metrics using the original Shakespeare plays and modern translations as
+We trained the logistic regression, language model and cosine similarity evaluation metrics using the original Shakespeare plays and modern translations as
 the source and target corpus respectively, then measured Pearson's Correlation Coefficient between the automatic
@@
 
-PINC, on the other hand has high correlation with judgments on dissimilarity, and is also moderately correlated with human style
-judgments.  We believe PINC has some correlation with writing style, because the systems we are evaluating all target Shakespearean English, 
+PINC, on the other hand has high correlation with judgments on dissimilarity, and is also correlated with human style
+judgments.  We believe PINC has correlation with writing style, because the systems we are evaluating all target Shakespearean English, 
 so whenever changes are made to the input, they are likely to make it similar to the target style.
@@
 
-Both the cosine and logistic regression style metrics achieve the highest overall correlation with human writing style judgments, with the logistic regression style score performing best.
+Both the language model and logistic regression style metrics achieve the highest overall correlation with human writing style judgments, achieving comparable performance.
 
@@
 data are presented in Figure \ref{shakespeare_to_modern_automatic}, correlation of the automatic metrics with with human judgments are presented in 
-Table \ref{correlation_s2m} and overall average human judgments are presented in Figure \ref{human_judgements_s2m}.
+Table \ref{correlation_s2m} and average human judgments are presented in Figure \ref{human_judgements_s2m}.
 
@@
 
-Finally, we applied these automatic evaluation metrics in an investigation into the task of translating Shakespeare's plays into modern English.
-
 We have shown that access to even a small amount of parallel text produces paraphrase systems 
-capable of generating a large number of stylistically appropriate paraphrases which preserving the meaning of the input text.  
+capable of generating a large number of stylistically appropriate paraphrases while preserving the meaning of the input text.  
 Our paraphrase systems targeting Shakespearean English could be beneficial for educational applications, for example helping to

### 2012-10-28 paper/paper.tex
updated for camera ready (and submitted)

@@
 \title{Paraphrasing for Style}
-\author{$Author1^{1, 2}~~~Author2^{1, 3}$\\
-{\small  	(1) INSTITUTE\_1, address 1\\ 
- 		(2) INSTITUTE\_2, address 2\\
-		(3) INSTITUTE\_3, address 3\\
-  \texttt{author1@institute1, author@institute2} \\ 
+\author{$Wei~Xu^{1}~~~Alan~Ritter^{2}~~~William~B.~Dolan^{3}~~~Ralph~Grishman^{1}~~~Colin~Cherry^{4}$\\
+{\small  	(1) New York University\\ 
+ 		(2) University of Washington\\
+		(3) Microsoft Research\\
+		(4) National Research Council, Canada\\
+  \texttt{xuwei@cims.nyu.edu, aritter@cs.washington.edu, billdol@microsoft.com, grishman@cs.nyu.edu, Colin.Cherry@nrc-cnrc.gc.ca} \\ 
 }}
@@
 
-The same meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
-fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.
+The same meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{madnani2010generating}.
 
@@
 There is a significant literature in sentence compression aimed at modeling the first of these, length: 
-producing meaning-preserving alternations that reduce the length of the input string \cite{Chandrasekar96,Vanderwende07,Yatskar10}.
+producing meaning-preserving alternations that reduce the length of the input string \cite{Chandrasekar96,Vanderwende07,clarke2008global,cohn2009sentence,Yatskar10}.
 However, we know of no previous work aimed at modeling meaning-preserving transformations that systematically transform the register or style of an input string. 
@@
 \section{Related Work}
+%Much previous work has addressed the task of automatically generating paraphrases \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05,Callison-Burch08,Kok10}.  
 Much previous work has addressed the task of automatically generating paraphrases \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05,Callison-Burch08,Kok10}.  

### 2012-11-19 paper/paper.tex
added video corpus

@@
       \hline
-      16and7plays\_36LM & Phrase table extracted from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, again excluding R\&J.
+      16and7plays\_36LM & Phrase table extracted from all 16 Sparknotes plays and 7 Enotes plays (holding out R\&J) and language model built from all 36 of Shakespeare's plays, again excluding R\&J.
       Uses default Moses parameters. \\
@@
 are more likely to contain overlapping ngrams if they are both semantically and stylistically similar.  What BLEU cannot tell us, however
-is what portion of its improvements are due to stylistic similarity or semantic equivalence.  For this reason, we were motivated perform
+is what portion of its improvements are due to stylistic similarity or semantic equivalence.  For this reason, we were motivated to perform
 an evaluation based on human judgments of semantic adequacy, lexical dissimilarity and stylistic similarity.
@@
 
-We note that overall the automatic metrics tend to agree with agree with human judgments as displayed in Figure \ref{style_metrics}.\footnote{
+We note that overall the automatic metrics tend to agree with human judgments as displayed in Figure \ref{style_metrics}.\footnote{
   Although the automatic style metrics rate the dictionary system higher than the video corpus baseline, both systems have very comparable
@@
 
-Perhaps most relevant, however, is recent work automatic generation of rhythmic poetry \cite{Greene10}.  This work focuses on automatically generating and translating
+Perhaps most relevant, however, is recent work on automatic generation of rhythmic poetry \cite{Greene10}.  This work focuses on automatically generating and translating
 poetry in an appropriate meter (e.g. iambic pentameter) using finite-state transducers, but does not investigate the task of paraphrase.  Their generation system
